---
title: "ABCD_other_data"
author: "An Nguyen"
date: "April 3, 2018"
output:
  pdf_document: default
  html_document: default
---

```{r, echo=FALSE,warning=FALSE,include=FALSE}
library(readr)
library(nortest)
library(PerformanceAnalytics)

#This script works on the big data ABCD file with everyone's information on IQ, Language measurements etc.
#Load the file: ABCD <- read_csv("~/ABCD.csv")
#calculate delta for rotary

#delta<-NULL
#for (i in seq(from=1,to=length(ABCD$Group),by=1)){delta <- append(delta, - mean(c(as.numeric(strsplit(ABCD$`Rotary Pursuit Trial 1: Sec on; Sec off`[i],split=';')[[1]][[1]]),as.numeric(strsplit(ABCD$`Rotary Pursuit Trial 2: Sec on; Sec off`[i],split=';')[[1]][[1]]))) + mean(c(as.numeric(strsplit(ABCD$`Rotary Pursuit Trial 16: Sec on; Sec off`[i],split=';')[[1]][[1]]),as.numeric(strsplit(ABCD$`Rotary Pursuit Trial 15: Sec on; Sec off`[i],split=';')[[1]][[1]]))))}

#delta mirror on

#mirror <- NULL
#for (i in seq(from=1,to=length(ABCD$Group),by=1)){mirror <- append(mirror, (- mean(c(as.numeric(strsplit(ABCD$`Mirror Tracing Trial 1: Completion time; Errors`[i],split=';')[[1]][[1]]),as.numeric(strsplit(ABCD$`Mirror Tracing Trial 2: Completion time; Errors`[i],split=';')[[1]][[1]]))) + mean(c(as.numeric(strsplit(ABCD$`Mirror Tracing Trial 9: Completion time; Errors`[i],split=';')[[1]][[1]]),as.numeric(strsplit(ABCD$`Mirror Tracing Trial 10: Completion time; Errors`[i],split=';')[[1]][[1]]))))/ as.numeric(strsplit(ABCD$`Mirror Tracing Trial 1: Completion time; Errors`[i],split=';')[[1]][[1]]))}

#delta mirror off

#mirror_off<-NULL
#for (i in seq(from=1,to=length(ABCD$Group),by=1)){
#  if(is.na(ABCD$`Mirror Tracing Trial 1: Completion time; Errors`[i])){mirror_off<-append(mirror_off,0)}
#  else {mirror_off <- append(mirror_off, - mean(c(as.numeric(strsplit(ABCD$`Mirror Tracing Trial 1: Completion time; Errors`[i],split=';')[[1]][[2]]),as.numeric(strsplit(ABCD$`Mirror Tracing Trial 2: Completion time; Errors`[i],split=';')[[1]][[2]]))) + mean(c(as.numeric(strsplit(ABCD$`Mirror Tracing Trial 9: Completion time; Errors`[i],split=';')[[1]][[2]]),as.numeric(strsplit(ABCD$`Mirror Tracing Trial 10: Completion time; Errors`[i],split=';')[[1]][[2]]))))}}

#Save this to a file: write.csv(ABCD, "ABCD.csv")

#then import the file again ABCD <- read_csv("~/ABCD.csv")

```

#Test for significant difference between the two groups on age, IQ, and gender ratio. There's no significant difference.
```{r,echo=FALSE,warning=FALSE}
ABCD <- read_csv("/Users/zhenghanqi/Dropbox (MIT)/UDel/projects/collaboration/abcd/raw/summary/ABCD_102818.csv")
#ABCD <- ABCD[ABCD$`ABCD ID`!="ABCD_1754",]
#ABCD <- ABCD[ABCD$`ABCD ID`!="ABCD_1742",]# remove two participants who had the highest IQ from the TYP group.
colnames(ABCD)[3]="subjid"
colnames(ABCD)[5]="age_month"
colnames(ABCD)[9]="kbit_nv"
colnames(ABCD)[10]="towre_sw"
colnames(ABCD)[11]="towre_pd"
colnames(ABCD)[12]="towre_total"
colnames(ABCD)[13]="wrmt_wi"
colnames(ABCD)[14]="wrmt_wa"
colnames(ABCD)[15]="wrmt_total"
ABCD_dys = subset(ABCD,Group == "DD")[,9:26]
ABCD_typ = subset(ABCD,Group =="TYP")[,9:26]
write.csv(ABCD_typ,"/Users/zhenghanqi/Dropbox (MIT)/UDel/projects/collaboration/abcd/raw/summary/typ.csv",sep=",")
write.csv(ABCD_dys,"/Users/zhenghanqi/Dropbox (MIT)/UDel/projects/collaboration/abcd/raw/summary/dd.csv",sep=",")

library(dplyr)
library(qwraps2)
options(qwraps2_markup = "markdown")
str(ABCD)
abcd_summary<-
  with(ABCD,
       list("Age" = tab_summary(age_month)[c(1,4,3)],
            "IQ" = tab_summary(kbit_nv)[c(1,4,3)],
            "Gender" = tab_summary(as.character(Sex)),
            "ASL_ACC"= tab_summary(TSL_ACC)[c(1,4,3)],
            "ASL_RT_slope"= tab_summary(TSL_RT_SLOPE)[c(1,4,3)],
            "VSL_ACC"= tab_summary(VSL_ACC)[c(1,4,3)],
            "VSL_RT_slope"= tab_summary(VSL_RT_SLOPE)[c(1,4,3)],
            "TOWRE_sw" = tab_summary(towre_sw)[c(1,4,3)],
            "TOWRE_pd" = tab_summary(towre_pd)[c(1,4,3)],
            "WRMT_wi" = tab_summary(wrmt_wi)[c(1,4,3)],
            "WRMT_wa" = tab_summary(wrmt_wa)[c(1,4,3)]
       ))
whole <- summary_table(ABCD,abcd_summary)
whole
```

### summarize the participant demographic info by groups
```{r results='asis',echo=FALSE}
grouped <- summary_table(dplyr::group_by(ABCD,Group),abcd_summary) 
grouped
```
# test whether groups
```{r results='asis',echo=FALSE}
wilcox.test(ABCD$age_month[ABCD$Group=="DD"],ABCD$age_month[ABCD$Group=="TYP"])
wilcox.test(ABCD$kbit_nv[ABCD$Group=="DD"],ABCD$kbit_nv[ABCD$Group=="TYP"])
library(reshape)
library(reshape2)
gender_table = cast(ABCD,Group~Sex,value = "age_month",length)
chisq.test(gender_table)
```

#Other measurements that are significantly different
###Mirror_delta_completion_time, CTOPP, TOWRE, WRMT, GORT
```{r,echo=FALSE,warning=FALSE}
#ad.test(ABCD$Rotary_Delta)
#ad.test(ABCD$CTOPP_TOTAL)
#ad.test(ABCD$`WAIS-4 DS Total: Standard Score`)
#ad.test(ABCD$`TOWRE-2 Total Word Reading Efficiency Index: Standard Score`)

#wilcox.test(ABCD$Mirror_delta_on[ABCD$Group=="DD"],ABCD$Mirror_delta_on[ABCD$Group=="TYP"])
wilcox.test(ABCD$CTOPP_TOTAL[ABCD$Group=="DD"],ABCD$CTOPP_TOTAL[ABCD$Group=="TYP"])
wilcox.test(ABCD$towre_total[ABCD$Group=="DD"],ABCD$towre_total[ABCD$Group=="TYP"])
wilcox.test(ABCD$wrmt_total[ABCD$Group=="DD"],ABCD$wrmt_total[ABCD$Group=="TYP"])
wilcox.test(ABCD$VSL_RT_SLOPE[ABCD$Group=="DD"],ABCD$VSL_RT_SLOPE[ABCD$Group=="TYP"])
wilcox.test(ABCD$TSL_RT_SLOPE[ABCD$Group=="DD"],ABCD$TSL_RT_SLOPE[ABCD$Group=="TYP"])
wilcox.test(ABCD$VSL_ACC[ABCD$Group=="DD"],ABCD$VSL_ACC[ABCD$Group=="TYP"])
wilcox.test(ABCD$TSL_ACC[ABCD$Group=="DD"],ABCD$TSL_ACC[ABCD$Group=="TYP"])
```


#Other measurements that are not significantly different 
###Rotary_delta, Mirror_delta_error,WAIS
```{r,echo=FALSE,warning=FALSE}
#wilcox.test(ABCD$Rotary_Delta[ABCD$Group=="DD"],ABCD$Rotary_Delta[ABCD$Group=="TYP"])
#wilcox.test(ABCD$Mirror_delta_off1[ABCD$Group=="DD"],ABCD$Mirror_delta_off1[ABCD$Group=="TYP"])
wilcox.test(ABCD$`WAIS-4 DS Total: Standard Score`[ABCD$Group=="DD"],ABCD$`WAIS-4 DS Total: Standard Score`[ABCD$Group=="TYP"])
```


# #Test for correlation
```{r, echo=FALSE,warning=FALSE}
# #Run cor test on vsl acc, rt slope and mirror:
# cor.test(ABCD$VSL_RT_SLOPE[ABCD$Group=="DD"],ABCD$Mirror_delta_on[ABCD$Group=="DD"],method="spearman", alternative = "greater")
# cor.test(ABCD$VSL_RT_SLOPE[ABCD$Group=="DD"],ABCD$Mirror_delta_off1[ABCD$Group=="DD"],method="spearman", alternative = "less")
# 
# cor.test(ABCD$VSL_ACC[ABCD$Group=="DD"],ABCD$Mirror_delta_on[ABCD$Group=="DD"],method="spearman", alternative = "greater")
# cor.test(ABCD$VSL_ACC[ABCD$Group=="DD"],ABCD$Mirror_delta_off1[ABCD$Group=="DD"],method="spearman", alternative = "less")
# cor.test(ABCD$TSL_ACC[ABCD$Group=="DD"],ABCD$Mirror_delta_on[ABCD$Group=="DD"],method="spearman", alternative = "greater")
# cor.test(ABCD$TSL_ACC[ABCD$Group=="DD"],ABCD$Mirror_delta_off1[ABCD$Group=="DD"],method="spearman", alternative = "less")
# 
# cor.test(ABCD$VSL_ACC[ABCD$Group=="TYP"],ABCD$Mirror_delta_on[ABCD$Group=="TYP"],method="spearman", alternative = "greater")
# cor.test(ABCD$VSL_ACC[ABCD$Group=="TYP"],ABCD$Mirror_delta_off1[ABCD$Group=="TYP"],method="spearman", alternative = "less")
# cor.test(ABCD$TSL_ACC[ABCD$Group=="TYP"],ABCD$Mirror_delta_on[ABCD$Group=="TYP"],method="spearman", alternative = "greater")
# cor.test(ABCD$TSL_ACC[ABCD$Group=="TYP"],ABCD$Mirror_delta_off1[ABCD$Group=="TYP"],method="spearman", alternative = "less")
source("~/Dropbox (MIT)/how-to/stats/R-related/a.pcor.test.R")
cor.test(ABCD$TSL_ACC[ABCD$Group=="TYP"],ABCD$VSL_ACC[ABCD$Group=="TYP"],method="spearman",alternative = "greater")
cor.test(ABCD$TSL_ACC[ABCD$Group=="TYP"],ABCD$towre_sw[ABCD$Group=="TYP"],method="spearman",alternative = "greater")
cor.test(ABCD$TSL_ACC[ABCD$Group=="TYP"],ABCD$towre_pd[ABCD$Group=="TYP"],method="spearman",alternative = "greater")
cor.test(ABCD$TSL_ACC[ABCD$Group=="TYP"],ABCD$wrmt_wi[ABCD$Group=="TYP"],method="spearman",alternative = "greater")
cor.test(ABCD$TSL_ACC[ABCD$Group=="TYP"],ABCD$wrmt_wa[ABCD$Group=="TYP"],method="spearman",alternative = "greater")
cor.test(ABCD$VSL_ACC[ABCD$Group=="TYP"],ABCD$towre_sw[ABCD$Group=="TYP"],method="spearman",alternative = "greater")
cor.test(ABCD$VSL_ACC[ABCD$Group=="TYP"],ABCD$towre_pd[ABCD$Group=="TYP"],method="spearman",alternative = "greater")
cor.test(ABCD$VSL_ACC[ABCD$Group=="TYP"],ABCD$wrmt_wi[ABCD$Group=="TYP"],method="spearman",alternative = "greater")
cor.test(ABCD$VSL_ACC[ABCD$Group=="TYP"],ABCD$wrmt_wa[ABCD$Group=="TYP"],method="spearman",alternative = "greater")

cor.test(ABCD$TSL_ACC[ABCD$Group=="DD"],ABCD$VSL_ACC[ABCD$Group=="DD"],method="spearman",alternative = "greater")
cor.test(ABCD$TSL_ACC[ABCD$Group=="DD"],ABCD$towre_sw[ABCD$Group=="DD"],method="spearman",alternative = "greater")
cor.test(ABCD$TSL_ACC[ABCD$Group=="DD"],ABCD$towre_pd[ABCD$Group=="DD"],method="spearman",alternative = "greater")
cor.test(ABCD$TSL_ACC[ABCD$Group=="DD"],ABCD$wrmt_wi[ABCD$Group=="DD"],method="spearman",alternative = "greater")
cor.test(ABCD$TSL_ACC[ABCD$Group=="DD"],ABCD$wrmt_wa[ABCD$Group=="DD"],method="spearman",alternative = "greater")

cor.test(ABCD$VSL_ACC[ABCD$Group=="DD"],ABCD$towre_sw[ABCD$Group=="DD"],method="spearman",alternative = "greater")
cor.test(ABCD$VSL_ACC[ABCD$Group=="DD"],ABCD$towre_pd[ABCD$Group=="DD"],method="spearman",alternative = "greater")
cor.test(ABCD$VSL_ACC[ABCD$Group=="DD"],ABCD$wrmt_wi[ABCD$Group=="DD"],method="spearman",alternative = "greater")
cor.test(ABCD$VSL_ACC[ABCD$Group=="DD"],ABCD$wrmt_wa[ABCD$Group=="DD"],method="spearman",alternative = "greater")

cor.test(ABCD$VSL_ACC[ABCD$Group=="DD"],ABCD$CTOPP_TOTAL[ABCD$Group=="DD"],method="spearman",alternative = "greater")


chart.Correlation(ABCD_dys,method="pearson")
chart.Correlation(ABCD_typ,method="pearson")
```
