---
title: "vsl_analysis"
author: "An Nguyen"
date: "November 9, 2017"
output: html_document
header-includes:
  - \usepackage{color}
---
\definecolor{coolblack}{rgb}{0.0, 0.18, 0.39}
\definecolor{violet}{rgb}{0.19, 0.55, 0.91}
```{r,echo=FALSE,warning=FALSE,include=FALSE}
#Loading library
library(ggplot2)
library(knitr)
library(readr)
library(psych)
library(ppcor)
library(nortest)

```


```{r,echo=FALSE}
#importing files
total_vsl_trial <- 24
language_1 = list(1,2,2,2,1,1,2,1,1,2,1,2,1,1,2,2,1,1,2,1,2,2,1,2,2,2,1,2,1,2,1,1)
language_2 = list(1,1,2,1,1,1,2,2,2,2,1,1,1,2,2,1,2,2,1,1,2,1,2,1,2,1,2,1,1,2,2,2)

vsl <- read_csv("Z:/projects/mturk/raw/cleaned_data/vsl2.csv")
wj3 <- read.csv("C:/Users/Qlab/Downloads/mturk/mturk_data/wj3_score.csv")
scf <-  read.csv("C:/Users/Qlab/Downloads/mturk/mturk_data/scf.csv")


#Clean data

vsl$stimulus<- gsub(".jpg","",vsl$stimulus)
vsl$stimulus<- gsub("../../images/","",vsl$stimulus)

```


```{r,echo=FALSE}
#analysis on RT

fam_block <- vsl[which(vsl$trial_index<=300 & vsl$trial_index>=13),]
fam_block <- fam_block[!(fam_block$stimulus=="../../vsl_audio/sound_instruct/vsl_instr7.wav" & fam_block$stimulus=="../../vsl_audio/vsl_instr_between.wav"),]
fam_block$targ <- paste(fam_block$targ)
fam_block$stimulus <- paste(fam_block$stimulus)

rt_col <- NULL
id <- NULL
trial <- NULL
target <- NULL

#Extract the row number in which the stimulus is the target
row_number <- which(fam_block$targ==fam_block$stimulus)

#Extract the response time and trial number when stimulus is the target
for (i in row_number){
        rt_col <- append(rt_col,fam_block[i,][,"rt"])
        trial <- append(trial,fam_block[i,][,"trial_index"])
        id <- append(id,paste(fam_block[i,]$par_id))
    if (fam_block[i-1,][,"rt"]!=-1){
        rt_col[(match(i,row_number))] <- -(1000-fam_block[i-1,][,"rt"])
        
    }}

fam_trial <- data.frame(unlist(trial),unlist(rt_col),id)
colnames(fam_trial) <- c("trial","rt_col","id")

#Re-index the trial number of the response so that it ranges from 1-24 (because there are 24 stimuli in total)
reindex <- rep(1:total_vsl_trial,length(fam_trial$trial)/24)
fam_trial$reindex <- reindex

hit_rate <- NULL
miss_rate <- NULL
correct_rejection <- NULL
false_alarm <- NULL
mean_rt <- NULL
rt_slope <- NULL
timeline <- c(rep("first half",total_vsl_trial/2),rep("second half",total_vsl_trial/2))
timeline <- rep(timeline,length(fam_trial$trial)/24)
fam_trial$timeline <- timeline
mean_table <- fam_trial[which(fam_trial$rt_col!=-1 & fam_trial$rt_col<1000 & fam_trial$rt_col>-1000), ] #only accept answers in range of -1000 < x < 1000

#exclude people who only have one rt point, so rtslope cannot be computed
mean_table <- mean_table[mean_table$id!="mtslAG1213",]

#vsl2
#mean_table <- mean_table[mean_table$id!="A1FDP7EMSL9T9F",]
#mean_table <- mean_table[mean_table$id!="mtslen0591",]
#mean_table <- mean_table[mean_table$id!="mtslmd1085",]

list_vsl_id <- unique(mean_table$id)

#Extract the mean response time, rt slope, hit rate, miss rat, correct rejection, and false alarm for each participant
for(id in list_vsl_id){
  mean_rt<-append(mean_rt,round(mean(mean_table$rt_col[mean_table$id==id]),digits=3))
 rt_slope <-append(rt_slope,round(summary(lm(mean_table$rt_col[mean_table$id==id]~mean_table$reindex[mean_table$id==id]))$coefficient[2,1],digits=3))
  hit_rate<-append(hit_rate,round(sum(!is.na(mean_table$rt_col[mean_table$id==id]))/total_vsl_trial,digits =2))
  miss_rate<-append(miss_rate,round(sum(fam_trial$rt_col[fam_trial$id==id]==-1)/total_vsl_trial,digits=2))
  correct_rejection <- append(correct_rejection, round(sum(fam_block$rt[fam_block$par_id==id]==-1 & fam_block$targ[fam_block$par_id==id]!=fam_block$stimulus[fam_block$par_id==id])/264,digits=2)) #264 is the total number of stimuli in the familiarization block
  false_alarm <- append(false_alarm, round(sum(fam_block$rt[fam_block$par_id==id]!=-1 & fam_block$targ[fam_block$par_id==id]!=fam_block$stimulus[fam_block$par_id==id])/264,digits=2))
}

subj_table <- data.frame(list_vsl_id,mean_rt, rt_slope,hit_rate, miss_rate,correct_rejection,false_alarm)
dprime<-NULL
for (i in seq(from=1,to=length(subj_table$list_vsl_id),by=1)){dprime<-append(dprime,qnorm(subj_table[i,]$hit_rate-0.00000001)-qnorm(subj_table[i,]$false_alarm+0.000000001))} #minus 0.000000001 to avoid perfect hit rate
subj_table$dprime <- round(dprime,3)

#Add Wj4 score into a column to look at SL performance and language skills
wj3$ID<-gsub("_wj3.csv","",wj3$ID)
for(id in wj3$ID){ subj_table$wj3_score[which(subj_table$list_vsl_id==id)]<-wj3$total[wj3$ID==id]}

for(id in scf$ID){ subj_table$gender[which(subj_table$list_vsl_id==id)]<-paste(scf$Gender[scf$ID==id])}
for(id in scf$ID){ subj_table$handedness[which(subj_table$list_vsl_id==id)]<-paste(scf$Hand[scf$ID==id])}
for(id in scf$ID){ subj_table$Language[which(subj_table$list_vsl_id==id)]<-paste(scf$Language[scf$ID==id])}
for(id in scf$ID){ subj_table$age[which(subj_table$list_vsl_id==id)]<-paste(scf$age[scf$ID==id])}
subj_table$Language <- as.numeric(subj_table$Language)
subj_table$age <- as.numeric(subj_table$age)

lowerbound <- mean(subj_table$rt_slope) - 2.5*sd(subj_table$rt_slope)
upperbound <- mean(subj_table$rt_slope) + 2.5*sd(subj_table$rt_slope)
subj_table <- subj_table[subj_table$rt_slope>=lowerbound,]
subj_table <- subj_table[subj_table$rt_slope<=upperbound,]

subset2<- subj_table[subj_table$Language>=20,]
subset1 <- subj_table[subj_table$gender!="Other",]
```



```{r,echo=FALSE}
#Extract the testing phase
#test block
 test_block <- vsl[which(vsl$trial_index<=532 & vsl$trial_index>=308),]
#test_block <- test_block[!(test_block$stimulus=="../../vsl_audio/sound_instruct/vsl_instr14.wav"),]
test_block <- test_block[!(test_block$stimulus=="" & test_block$key_press==-1),]

ans <- NULL
keyv <- NULL
subj <- NULL
cond<- NULL
#Extract rows in which the participant gives a response
 row_numberv <- which(test_block$key_press != -1 & is.na(test_block$stimulus)) #In older version of R - it would be test_block$stimulus==""   so if this line doesn't run correctly, you can try changing the latter part
  for (i in row_numberv){
    ans<-append(ans,test_block[i,]$key_press)
    subj <- append(subj,paste(test_block[i,]$par_id))
    cond <- append(cond,paste(test_block[i,]$cond))
  }
  
vsl_accuracy <- data.frame(ans,subj,cond)
vsl_accuracy <- vsl_accuracy[!(vsl_accuracy$ans==32),]
vsl_cond <- NULL
for (i in seq(from=1,to=length(vsl_accuracy$cond),by=32)){vsl_cond<-append(vsl_cond,as.character(vsl_accuracy[i,]$cond))}

keyv<- NULL

#Match the language condition with the correct answer key

for(cond in vsl_cond){
    if (cond=="lang1"){keyv<-append(keyv,language_1)}
    else if (cond=="lang2"){keyv<-append(keyv,language_2)}}



acc_id <- unique(vsl_accuracy$subj)

vsl_accuracy$key <- keyv

#Substitute the key press (49,50) with the answer (1,2)
vsl_accuracy$ans <- gsub(50,2,vsl_accuracy$ans)
vsl_accuracy$ans <- gsub(49,1,vsl_accuracy$ans)

#Loop through and count the correct answer
corr <- NULL
for (i in seq(from=1,to=length(vsl_accuracy$ans),by=1)) {corr<-append(corr,as.numeric(vsl_accuracy[i,]$ans==vsl_accuracy[i,]$key))}
vsl_accuracy$corr <- corr
subj_corr <- NULL
for (id in acc_id) {subj_corr <- append(subj_corr,round(sum(vsl_accuracy$corr[vsl_accuracy$subj==id])/32,digits=3))}
vsl_acc_table <- data.frame(acc_id,subj_corr,vsl_cond)

 for(id in scf$ID){ vsl_acc_table$age[which(vsl_acc_table$acc_id==id)]<-paste(scf$age[scf$ID==id])}

for(id in scf$ID){ vsl_acc_table$gender[which(vsl_acc_table$acc_id==id)]<-paste(scf$Gender[scf$ID==id])}
for(id in wj3$ID){ vsl_acc_table$wj3_score[which(vsl_acc_table$acc_id==id)]<-wj3$total[wj3$ID==id]}
for(id in scf$ID){ vsl_acc_table$hand[which(vsl_acc_table$acc_id==id)]<-paste(scf$Hand[scf$ID==id])}

 for(id in scf$ID){ vsl_acc_table$Language[which(vsl_acc_table$acc_id==id)]<-paste(scf$Language[scf$ID==id])}
vsl_acc_table$Language <- as.numeric(vsl_acc_table$Language)
vsl_acc_table$age <- as.numeric(vsl_acc_table$age)

```


### Cronbach's alpha score for the consistency of the vsl Accuracy task is 0.89. The consistency of the questions in this task is good.
```{r,echo=FALSE,warning=FALSE}
#d <- matrix(nrow=145,ncol=32)
#for(i in seq(from=1,to=145,by=1)){d[i,] <- rbind(vsl_accuracy$corr[((i-1)*32+1):(i*32)])}
#psych::alpha(d,check.keys = TRUE)$total$std.alpha

#Calculate cronbach's alpha for language 1
vsl_lang1 <- vsl_accuracy[vsl_accuracy$cond=='lang1',]
d1 <- matrix(nrow=74,ncol=32)
for(i in seq(from=1,to=74,by=1)){d1[i,] <- rbind(vsl_lang1$corr[((i-1)*32+1):(i*32)])}
a1 <- psych::alpha(d1,check.keys = TRUE)$total$std.alpha

#Calculate cronbach's alpha for language 2
vsl_lang2 <- vsl_accuracy[vsl_accuracy$cond=='lang2',]
d2 <- matrix(nrow=71,ncol=32)
for(i in seq(from=1,to=71,by=1)){d2[i,] <- rbind(vsl_lang2$corr[((i-1)*32+1):(i*32)])}
a2 <- psych::alpha(d2,check.keys = TRUE)$total$std.alpha

#Calculate the mean cronbach's alpha 
alpha <- mean(a1,a2)
print(alpha)

#ad.test(subj_table$rt_slope)
#ad.test(vsl_acc_table$subj_corr)
#ad.test(subj_table$wj3_score)
#ad.test(subj_table$age)


```


#Testing SL ability through the task:
###Looking at RT 

```{r,echo=FALSE,warning=FALSE}
t.test(subj_table$rt_slope,mu=0,alternative="less")

ggplot(mean_table,aes(y=rt_col,x=reindex))+geom_point(color='deepskyblue3') + geom_smooth(method='lm') + labs(x="Trial Index", y="Response time (ms)",title="Resposne time by trial index in VSL")

```

###Looking at Accuracy: the mean accuracy of this task is above chance (50%)
```{r,echo=FALSE}
t.test(vsl_acc_table$subj_corr,mu=0.5,alternative="greater")
```

```{r,echo=FALSE,warning=FALSE,include=FALSE}
#RT by WJ4 score
ggplot(subj_table[subj_table$wj3_score>25,],aes(y=mean_rt,x=wj3_score))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="WJ4 Score", y="Response time (ms)",title="Resposne time by WJ4 score in vsl") + ylim(c(100,700))

#RT Slope by WJ4
ggplot(subj_table[subj_table$wj3_score>25,],aes(y=rt_slope,x=wj3_score))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="WJ4 Score", y="Response time slope",title="Resposne time slope by WJ4 score in VSL")  + ylim(c(-15,15))

#RT slope  vs WJ4 score by gender
qplot(wj3_score,rt_slope,data=subset1[subset1$wj3_score>25,],facets=(. ~ gender),color= gender, main="vsl RT slope vs WJ4 scpre by gender", ylab="RT Slope", xlab="WJ4 score", ylim=c(-15,15)) + geom_smooth(method='lm') + scale_color_discrete(name="Gender")


#Mean rt vs WJ4 score by Handedness
qplot(wj3_score,mean_rt,data=subj_table[subj_table$wj3_score>25,],facets=(. ~ handedness),color= handedness, main="vsl RT by Handedness", ylab="Response time", xlab="Trial index", ylim=c(100,600)) + geom_smooth(method='lm') + scale_color_discrete(name="Handedness")
#RT Slope vs WJ4 score by Handedness
qplot(wj3_score,rt_slope,data=subj_table[subj_table$wj3_score>25,],facets=(. ~ handedness),color= handedness, main="vsl RT slope by Handedness", ylab="Response time", xlab="Trial index", ylim=c(-15,15)) + geom_smooth(method='lm') + scale_color_discrete(name="Handedness")



#RT by Language
ggplot(subset2,aes(y=mean_rt,x=Language))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="WJ4 Score", y="Response time (ms)",title="Resposne time by Language score in vsl") + ylim(c(100,700))
#RT Slope by Language
ggplot(subset2,aes(y=rt_slope,x=Language))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="WJ4 Score", y="Response time (ms)",title="Resposne time slope by Language score in vsl") + ylim(c(-15,15))





```


## A simple correlation test between WJ4 score and RT Slope, controlling for age
```{r,echo=FALSE}

#correlation test between rt slope and wj4 score
pcor.test(subj_table$rt_slope, subj_table$wj3_score,subj_table$age,method="spearman")
```

## A simple correlation test between WJ4 score and Accuracy, controlling for age
```{r,echo=FALSE}

#correlation test between rt slope and wj4 score
pcor.test(vsl_acc_table$subj_cor,vsl_acc_table$wj3_score,vsl_acc_table$age,method="spearman")
```

##RT slope and other factors
```{r,echo=FALSE}
a<-lm(formula = subj_corr ~ wj3_score * age + as.factor(hand) + as.factor(gender), data = vsl_acc_table)
summary(a)
```
##Accuracy and other factors
```{r,echo=FALSE}
a1<-lm(formula = rt_slope ~ wj3_score * age + as.factor(handedness) + as.factor(gender), data = subj_table)
summary(a1)
```




```{r,echo=FALSE}
#table_output <- subj_table[,c("list_vsl_id","mean_rt","rt_slope","dprime")]
#a <- seq(1,141,1)
#new_id <- sprintf("mtsl_%03d", a)
#table_output$list_vsl_id<-new_id
#colnames(table_output) <- c("ID","Mean RT","RT Slope","D'")
#kable(table_output)
```


```{r,echo=FALSE}
#table_output2 <- vsl_acc_table[,c("acc_id","subj_corr","vsl_cond")]
#a <- seq(1,145,1)
#new_id <- sprintf("mtsl_%03d", a)
#table_output2$acc_id<-new_id
#colnames(table_output2) <- c("ID","accuracy(%)","condition")
#kable(table_output2)
```

