---
title: "segment_parcel"
author: "Jojo Hu"
date: "9/28/2022"
output: html_document
---

# All commands below must be run in an R environment inside of terminal (system() commands below evoke FSL and AFNI commands in terminal) 
# Segmenting parcels for adults
# FSL must be installed for the following to work
```{r}
path <- "/Volumes/data-1/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/langloc_fitlins/group_constrained_mask/adult/6vox/"

dir.create(paste0(path, "seg_parcels"))

parcel <-
  read.csv(paste0(path, "LangLoc_adult_run_level_0001_6voxSpacing_parcel_report.csv"), stringsAsFactors = F)

mask_name <- paste0(path, "LangLoc_adult_run_level_0001_6voxSpacing_probability_map_thresh2subjs_smoothed_parcels_sig.nii.gz")

sig_parcel <- parcel[which(parcel$is_significant == 1), "parcel_numbers"]

length(sig_parcel)

for (i in sig_parcel) {
  parcel_seg <- paste0(path, "seg_parcels/langloc_gcp", i, ".nii.gz")
  
  fsl_command <- as.character(paste("fslmaths", mask_name, " -uthr", i, "-thr", i, parcel_seg))
 
  system(fsl_command)
}
```


# Segmenting parcels for children
```{r}
path <- "/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/langloc_fitlins/group_constrained_mask/child/6vox/"

dir.create(paste0(path, "seg_parcels"))

parcel <-
  read.csv(paste0(path, "LangLoc_child_run_level_0001_6voxSpacing_parcel_report.csv"), stringsAsFactors = F)

mask_name <- paste0(path, "LangLoc_child_run_level_0001_6voxSpacing_probability_map_thresh2subjs_smoothed_parcels_sig.nii.gz")

sig_parcel <- parcel[which(parcel$is_significant == 1), "parcel_numbers"]

length(sig_parcel)

for (i in sig_parcel) {
  parcel_seg <- paste0(path, "seg_parcels/langloc_gcp", i, ".nii.gz")
  
  fsl_command <- as.character(paste("fslmaths", mask_name, " -uthr", i, "-thr", i, parcel_seg))
 
  system(fsl_command)
}
```




# Extract individualized sub-voxels based on a parcel mask for children
# AFNI and FSL must be installed for the following to work
```{r}
library(stringr)
library(dplyr)
library(reshape2)

output_dir <- "/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/indiv_langloc_output/unresampled_mask/child/"

# Read in minimal of top 10% activation value
childMin <- 
  read.csv("/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/indiv_langloc_output/child_langloc_minimum_top_10_data_03_17.csv", stringsAsFactors = F)
# List langloc individual intact > degraded z-maps 
aliceFile <-
  list.files("/Volumes/data/projects/blast/data/derivatives/fitlins/analyzed/fitlins_alice", 
           pattern = "sub-blastc", 
           full.names = T, recursive = F)

aliceFile <-
  list.files(aliceFile, 
           pattern = "level-run_name-runlevel_sub-blastc\\d+_run-\\d+_contrast-intactGtDegraded_stat-z_statmap.nii.gz", 
           full.names = T, recursive = F)

aliceFile <- as.data.frame(aliceFile)

aliceFile$aliceFile <- as.character(aliceFile$aliceFile)

aliceFile$basename <- basename(as.character(aliceFile$aliceFile))

aliceFile$part_id <- str_extract(aliceFile$basename, "sub-blastc[[:digit:]]+")

aliceFile$bare_id <- str_extract(aliceFile$basename, "(?<=sub-blastc)[[:digit:]]+")

aliceFile$run <- str_extract(aliceFile$basename, "(?<=run-)[[:digit:]]")

aliceFile$bare_run <- paste0(aliceFile$bare_id, "_", aliceFile$run)

aliceFile <- 
  aliceFile %>%
  arrange(aliceFile)
# List all parcels in langloc group-constrained mask
langloc_parcels <- 
  list.files("/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/langloc_fitlins/group_constrained_mask/combined/td_adult/006_00001_final/seg_parcels",
            pattern = "\\S+.nii.gz", full.names = T)

# Repeat each individual's row so that each individual will have the number of rows that matches the total number of parcels in the group-constrained mask
file_rep <- rep(aliceFile$aliceFile, length(unique(langloc_parcels)))

file_rep <- as.data.frame(file_rep)

file_rep$part_id <- str_extract(file_rep$file_rep, "sub-blastc[[:digit:]]+")
file_rep$run <- str_extract(file_rep$file_rep, "(?<=run-)[[:digit:]]")

file_rep <-
  file_rep %>%
  arrange(file_rep)
 
# Repeat each parcel row so that each parcel will have the number of rows that matches the total number of individuals (N)
parcel_rep <- rep(langloc_parcels, times = c(nrow(file_rep)/length(langloc_parcels)))

length(parcel_rep) == nrow(file_rep)

file_rep <- cbind(file_rep, parcel_rep)

file_rep <- merge(file_rep, aliceFile, all.x = T)

file_rep$parcel <- str_extract(file_rep$parcel_rep, "(?<=seg_parcels/)\\S+(?=.nii.gz)")

# Check that merging did not create additional unwanted rows
length(parcel_rep) == nrow(file_rep)
# Check that each individual only has the set number of parcels
file_rep %>%
  arrange(file_rep) %>%
  group_by(part_id, run) %>%
  dplyr::summarise(n = n()) %>%
  filter(n != length(unique(langloc_parcels)))

library(reshape2)
childMin <- melt(childMin, id.vars = c("Row"))

colnames(childMin)[which(names(childMin) == "Row")] <- "bare_run"
colnames(childMin)[which(names(childMin) == "variable")] <- "parcel"

# Merge minimal of top 10% activation value
file_rep <- merge(file_rep, childMin, all.x = T)

# Check that merging did not create additional unwanted rows
length(parcel_rep) == nrow(file_rep)
# Check that each individual only has the set number of parcels
file_rep %>%
  arrange(file_rep) %>%
  group_by(part_id, run) %>%
  dplyr::summarise(n = n()) %>%
  filter(n != length(unique(langloc_parcels)))

colnames(file_rep)[which(names(file_rep) == "parcel_rep")] <- "parcel_path"

# Set file name for individuals' output sub-parcels
file_rep$output_file <- paste0(output_dir, file_rep$part_id, "_", "run-", file_rep$run, "_", file_rep$parcel, ".nii.gz") 

file_rep %>%
  group_by(part_id, run) %>%
  dplyr::summarise(n = n()) %>%
  distinct(.)
```

# Generate individual masks based on lang loc parcels
```{r}
for (i in 1:nrow(file_rep)) {

  fsl_command <- as.character(paste("fslmaths", file_rep[i, c("aliceFile")], "-thr", file_rep[i, c("value")], "-mas", file_rep[i, c("parcel_path")], file_rep[i, c("output_file")]))

  system(fsl_command)
}
```




# Resample individual masks
```{r}
resampled_dir <- "/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/indiv_langloc_output/resampled_mask/child/"

# Create subject sub-folders for resampled masks
subdir <- paste0(resampled_dir, file_rep$bare_id)
subdir <- unique(subdir)

for (i in 1:length(subdir)) {
  dir.create(subdir[i])
}

# List resampled individual masks output
file_rep$resampled_output <- paste0(resampled_dir, file_rep$bare_id, "/resampled_", basename(file_rep$output_file)) 

resampled_ref <- "/Volumes/data/projects/blast/data/derivatives/fitlins/analyzed/fitlins/sub-blasta044/level-run_name-run_sub-blasta044_run-1_contrast-strSpeechVRest_stat-z_statmap.nii.gz"

for (i in 1:nrow(file_rep)) {

  resample_command <- as.character(paste("3dresample", "-input", file_rep[i, c("output_file")], "-master", resampled_ref, "-prefix", file_rep[i, c("resampled_output")]))

  # print(resample_command)
  system(resample_command)
}
```




# Binarize all the resampled mask
```{r}
bin_dir <- "/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/indiv_langloc_output/bin_resampled_mask/child/"

# Create subject sub-folders for resampled masks
subdir <- paste0(bin_dir, file_rep$bare_id)
subdir <- unique(subdir)

for (i in 1:length(subdir)) {
  dir.create(subdir[i])
}
# To DO: Fix Scott script to take actual ID input and thus get rid of str_extract here!
file_rep$bin_output <- paste0(bin_dir, file_rep$bare_id, "/bin_resampled_", str_extract(file_rep$output_file, "run-[[:digit:]]_langloc_gcp[[:digit:]]+.nii.gz")) 

# Binarize all the resampled mask
for (i in 1:nrow(file_rep)) {

  bin_command <- as.character(paste("fslmaths", file_rep[i, c("resampled_output")], "-bin",  file_rep[i, c("bin_output")]))

  system(bin_command)
}
```




# Extract individualized sub-voxels based on a parcel mask for adults
# AFNI and FSL must be installed for the following to work
```{r}
library(stringr)
library(dplyr)
library(reshape2)

output_dir <- "/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/indiv_langloc_output/unresampled_mask/adult/"

# Read in minimal of top 10% activation value
childMin <- 
  read.csv("/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/indiv_langloc_output/child_langloc_minimum_top_10_data_03_17.csv", stringsAsFactors = F)

# List langloc individual intact > degraded z-maps 
aliceFile <-
  list.files("/Volumes/data/projects/blast/data/derivatives/fitlins/analyzed/fitlins_alice", 
           pattern = "sub-blasta", 
           full.names = T, recursive = F)

aliceFile <-
  list.files(aliceFile, 
           pattern = "level-run_name-runlevel_sub-blasta\\d+_run-\\d+_contrast-intactGtDegraded_stat-z_statmap.nii.gz", 
           full.names = T, recursive = F)


aliceFile <- as.data.frame(aliceFile)

aliceFile$aliceFile <- as.character(aliceFile$aliceFile)

aliceFile$basename <- basename(as.character(aliceFile$aliceFile))

aliceFile$part_id <- str_extract(aliceFile$basename, "sub-blasta[[:digit:]]+")

aliceFile$bare_id <- str_extract(aliceFile$basename, "(?<=sub-blasta)[[:digit:]]+")

aliceFile$run <- str_extract(aliceFile$basename, "(?<=run-)[[:digit:]]")

aliceFile$bare_run <- paste0(aliceFile$bare_id, "_", aliceFile$run)

aliceFile <- 
  aliceFile %>%
  arrange(aliceFile)
# List all parcels in langloc group-constrained mask
langloc_parcels <- 
  list.files("/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/langloc_fitlins/group_constrained_mask/combined/td_adult/006_00001_final/seg_parcels",
            pattern = "\\S+.nii.gz", full.names = T)

# Repeat each individual's row so that each individual will have the number of rows that matches the total number of parcels in the group-constrained mask
file_rep <- rep(aliceFile$aliceFile, length(unique(langloc_parcels)))

file_rep <- as.data.frame(file_rep)

file_rep$part_id <- str_extract(file_rep$file_rep, "sub-blasta[[:digit:]]+")
file_rep$run <- str_extract(file_rep$file_rep, "(?<=run-)[[:digit:]]")

file_rep <-
  file_rep %>%
  arrange(file_rep)
 
# Repeat each parcel row so that each parcel will have the number of rows that matches the total number of individuals (N)
parcel_rep <- rep(langloc_parcels, times = c(nrow(file_rep)/length(langloc_parcels)))

length(parcel_rep) == nrow(file_rep)

file_rep <- cbind(file_rep, parcel_rep)

file_rep <- merge(file_rep, aliceFile, all.x = T)

file_rep$parcel <- str_extract(file_rep$parcel_rep, "(?<=seg_parcels/)\\S+(?=.nii.gz)")

# Check that merging did not create additional unwanted rows
length(parcel_rep) == nrow(file_rep)
# Check that each individual only has the set number of parcels
file_rep %>%
  arrange(file_rep) %>%
  group_by(part_id, run) %>%
  dplyr::summarise(n = n()) %>%
  filter(n != length(unique(langloc_parcels)))

library(reshape2)
childMin <- melt(childMin, id.vars = c("Row"))

colnames(childMin)[which(names(childMin) == "Row")] <- "bare_run"
colnames(childMin)[which(names(childMin) == "variable")] <- "parcel"

# Merge minimal of top 10% activation value
file_rep <- merge(file_rep, childMin, all.x = T)

# Check that merging did not create additional unwanted rows
length(parcel_rep) == nrow(file_rep)
# Check that each individual only has the set number of parcels
file_rep %>%
  arrange(file_rep) %>%
  group_by(part_id, run) %>%
  dplyr::summarise(n = n()) %>%
  filter(n != length(unique(langloc_parcels)))

colnames(file_rep)[which(names(file_rep) == "parcel_rep")] <- "parcel_path"

# Set file name for individuals' output sub-parcels
file_rep$output_file <- paste0(output_dir, file_rep$part_id, "_", "run-", file_rep$run, "_", file_rep$parcel, ".nii.gz") 
```


# Generate individual masks based on lang loc parcels
```{r}
for (i in 1:nrow(file_rep)) {

  fsl_command <- as.character(paste("fslmaths", file_rep[i, c("aliceFile")], "-thr", file_rep[i, c("value")], "-mas", file_rep[i, c("parcel_path")], file_rep[i, c("output_file")]))

  system(fsl_command)
}
```


# Resample individual masks
```{r}
resampled_dir <- "/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/indiv_langloc_output/resampled_mask/adult/"

# Create subject sub-folders for resampled masks
subdir <- paste0(resampled_dir, file_rep$bare_id)
subdir <- unique(subdir)

for (i in 1:length(subdir)) {
  dir.create(subdir[i])
}

# List resampled individual masks output
file_rep$resampled_output <- paste0(resampled_dir, file_rep$bare_id, "/resampled_", basename(file_rep$output_file)) 

resampled_ref <- "/Volumes/data/projects/blast/data/derivatives/fitlins/analyzed/fitlins/sub-blasta044/level-run_name-run_sub-blasta044_run-1_contrast-strSpeechVRest_stat-z_statmap.nii.gz"

for (i in 1:nrow(file_rep)) {

  resample_command <- as.character(paste("3dresample", "-input", file_rep[i, c("output_file")], "-master", resampled_ref, "-prefix", file_rep[i, c("resampled_output")]))

  # print(resample_command)
  system(resample_command)
}
```



# Binarize all the resampled mask
```{r}
bin_dir <- "/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/indiv_langloc_output/bin_resampled_mask/adult/"

# Create subject sub-folders for resampled masks
subdir <- paste0(bin_dir, file_rep$bare_id)
subdir <- unique(subdir)

for (i in 1:length(subdir)) {
  dir.create(subdir[i])
}

file_rep$bin_output <- paste0(bin_dir, file_rep$bare_id, "/bin_resampled_", str_extract(file_rep$output_file, "run-[[:digit:]]_langloc_gcp[[:digit:]]+.nii.gz")) 

# Binarize all the resampled mask
for (i in 1:nrow(file_rep)) {

  bin_command <- as.character(paste("fslmaths", file_rep[i, c("resampled_output")], "-bin",  file_rep[i, c("bin_output")]))

  system(bin_command)
}
```




# Extract individualized sub-voxels based on a parcel mask for children for Attentional Network based on Random vs. Rest ASL contrasts
# AFNI and FSL must be installed for the following to work
```{r}
library(stringr)
library(dplyr)
library(reshape2)

output_dir <- "/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/asl_attention/indiv_att_ouput/resampled_mask/child/"

# Read in minimal of top 10% activation value
childMin <- 
  read.csv("/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/asl_attention/child_dan_minimum_top_10_data_03_17.csv", 
           stringsAsFactors = F)
# List ASL individual random > rest z-maps 
aslRandFile <-
  list.files("/Volumes/data/projects/blast/data/derivatives/fitlins/analyzed/fitlins", 
           pattern = "sub-blastc", 
           full.names = T, recursive = F)

aslRandFile <-
  list.files(aslRandFile, 
           pattern = "level-run_name-run_sub-blastc\\d+_run-\\d+_contrast-rand[[:alpha:]]+VRest_stat-z_statmap.nii.gz", 
           full.names = T, recursive = F)

aslRandFile <- as.data.frame(aslRandFile)

aslRandFile$aslRandFile <- as.character(aslRandFile$aslRandFile)

aslRandFile$basename <- basename(as.character(aslRandFile$aslRandFile))

aslRandFile$part_id <- str_extract(aslRandFile$basename, "sub-blastc[[:digit:]]+")

aslRandFile$bare_id <- str_extract(aslRandFile$basename, "(?<=sub-blastc)[[:digit:]]+")

aslRandFile$run <- str_extract(aslRandFile$basename, "(?<=run-)[[:digit:]]")

aslRandFile$bare_run <- paste0(aslRandFile$bare_id, "_", aslRandFile$run, "_", tolower(str_extract(aslRandFile$basename, "(Speech|Tone)")))

aslRandFile$stimuli <- str_extract(aslRandFile$basename, "(Speech|Tone)")

aslRandFile$condition <- str_extract(aslRandFile$basename, "(str|rand)")

aslRandFile12 <- 
  aslRandFile %>%
  filter(run == "1" | run == "2") %>%
  filter((stimuli == "Speech" & condition == "str") | (stimuli == "Tone" & condition == "rand"))

aslRandFile34 <- 
  aslRandFile %>%
  filter(run == "3" | run == "4") %>%
  filter((stimuli == "Speech" & condition == "rand") | (stimuli == "Tone" & condition == "str"))

aslRandFile <- rbind(aslRandFile12, aslRandFile34)

aslRandFile <- 
  aslRandFile %>%
  arrange(aslRandFile)

# List all parcels in langloc group-constrained mask
dan_parcels <- 
  list.files("/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/dorsal_attention_parcel/conn_resampled_parcel",
            pattern = "resampled_conn_dan.nii.gz", full.names = T)

# aslRandFile$parcel <- str_extract(aslRandFile$parcel, "resampled_conn_dan")

# Add parcel to aslRandFile
file_rep <- aslRandFile
file_rep$parcel_path <- dan_parcels
# Check that each individual only has the set number of parcels
file_rep %>%
  arrange(file_rep) %>%
  group_by(part_id, run) %>%
  dplyr::summarise(n = n()) %>%
  filter(n != length(unique(dan_parcels)))

library(reshape2)
childMin <- melt(childMin, id.vars = c("Row"))

colnames(childMin)[which(names(childMin) == "Row")] <- "bare_run"
colnames(childMin)[which(names(childMin) == "variable")] <- "parcel"

# Merge minimal of top 10% activation value
file_rep <- merge(file_rep, childMin, all.x = T)

# Check that each individual only has the set number of parcels
file_rep %>%
  arrange(file_rep) %>%
  group_by(part_id, run) %>%
  dplyr::summarise(n = n()) %>%
  filter(n != length(unique(dan_parcels)))

# Set file name for individuals' output sub-parcels
file_rep$output_file <- paste0(output_dir, file_rep$part_id, "_", "run-", file_rep$run, "_", file_rep$parcel, ".nii.gz") 

# Generate individual masks based on lang loc parcels
for (i in 1:nrow(file_rep)) {

  fsl_command <- as.character(paste("fslmaths", file_rep[i, c("aslRandFile")], "-thr", file_rep[i, c("value")], "-mas", file_rep[i, c("parcel_path")], file_rep[i, c("output_file")]))

  system(fsl_command)
}


# Binarize all the resampled mask
bin_dir <- "/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/asl_attention/indiv_att_ouput/bin_resampled_mask/child/"

# Create subject sub-folders for resampled masks
subdir <- paste0(bin_dir, file_rep$bare_id)
subdir <- unique(subdir)

for (i in 1:length(subdir)) {
  dir.create(subdir[i])
}
# To DO: Fix Scott script to take actual ID input and thus get rid of str_extract here!
file_rep$bin_output <- paste0(bin_dir, file_rep$bare_id, "/bin_resampled_", str_extract(file_rep$output_file, "run-[[:digit:]]_"), tolower(file_rep$stimuli), "_", tolower(file_rep$condition), "_dan.nii.gz")

# Binarize all the resampled mask
for (i in 1:nrow(file_rep)) {

  bin_command <- as.character(paste("fslmaths", file_rep[i, c("output_file")], "-bin",  file_rep[i, c("bin_output")]))

  system(bin_command)
}
```


# Extract individualized sub-voxels based on a parcel mask for adults for Attentional Network based on Random vs. Rest ASL contrasts
# AFNI and FSL must be installed for the following to work
```{r}
library(stringr)
library(dplyr)
library(reshape2)

output_dir <- "/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/asl_attention/indiv_att_ouput/resampled_mask/adult/"

# Read in minimal of top 10% activation value
childMin <- 
  read.csv("/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/asl_attention/adult_dan_minimum_top_10_data_03_17.csv", 
           stringsAsFactors = F)
# List ASL individual random > rest z-maps 
aslRandFile <-
  list.files("/Volumes/data/projects/blast/data/derivatives/fitlins/analyzed/fitlins", 
           pattern = "sub-blasta", 
           full.names = T, recursive = F)

aslRandFile <-
  list.files(aslRandFile, 
           pattern = "level-run_name-run_sub-blasta\\d+_run-\\d+_contrast-rand[[:alpha:]]+VRest_stat-z_statmap.nii.gz", 
           full.names = T, recursive = F)

aslRandFile <- as.data.frame(aslRandFile)

aslRandFile$aslRandFile <- as.character(aslRandFile$aslRandFile)

aslRandFile$basename <- basename(as.character(aslRandFile$aslRandFile))

aslRandFile$part_id <- str_extract(aslRandFile$basename, "sub-blasta[[:digit:]]+")

aslRandFile$bare_id <- str_extract(aslRandFile$basename, "(?<=sub-blasta)[[:digit:]]+")

aslRandFile$run <- str_extract(aslRandFile$basename, "(?<=run-)[[:digit:]]")

aslRandFile$bare_run <- paste0(aslRandFile$bare_id, "_", aslRandFile$run, "_", tolower(str_extract(aslRandFile$basename, "(Speech|Tone)")))

aslRandFile$stimuli <- str_extract(aslRandFile$basename, "(Speech|Tone)")

aslRandFile$condition <- str_extract(aslRandFile$basename, "(str|rand)")

aslRandFile12 <- 
  aslRandFile %>%
  filter(run == "1" | run == "2") %>%
  filter((stimuli == "Speech" & condition == "str") | (stimuli == "Tone" & condition == "rand"))

aslRandFile34 <- 
  aslRandFile %>%
  filter(run == "3" | run == "4") %>%
  filter((stimuli == "Speech" & condition == "rand") | (stimuli == "Tone" & condition == "str"))

aslRandFile <- rbind(aslRandFile12, aslRandFile34)

aslRandFile <- 
  aslRandFile %>%
  arrange(aslRandFile)

# List all parcels in langloc group-constrained mask
dan_parcels <- 
  list.files("/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/dorsal_attention_parcel/conn_resampled_parcel",
            pattern = "\\S+.nii.gz", full.names = T)

# aslRandFile$parcel <- str_extract(aslRandFile$parcel, "resampled_conn_dan")

# Add parcel to aslRandFile
file_rep <- aslRandFile
file_rep$parcel_path <- dan_parcels
# Check that each individual only has the set number of parcels
file_rep %>%
  arrange(file_rep) %>%
  group_by(part_id, run) %>%
  dplyr::summarise(n = n()) %>%
  filter(n != length(unique(dan_parcels)))

library(reshape2)
childMin <- melt(childMin, id.vars = c("Row"))

colnames(childMin)[which(names(childMin) == "Row")] <- "bare_run"
colnames(childMin)[which(names(childMin) == "variable")] <- "parcel"

# Merge minimal of top 10% activation value
file_rep <- merge(file_rep, childMin, all.x = T)

# Check that each individual only has the set number of parcels
file_rep %>%
  arrange(file_rep) %>%
  group_by(part_id, run) %>%
  dplyr::summarise(n = n()) %>%
  filter(n != length(unique(dan_parcels)))

# Set file name for individuals' output sub-parcels
file_rep$output_file <- paste0(output_dir, file_rep$part_id, "_", "run-", file_rep$run, "_", file_rep$parcel, ".nii.gz") 

# Generate individual masks based on lang loc parcels
for (i in 1:nrow(file_rep)) {

  fsl_command <- as.character(paste("fslmaths", file_rep[i, c("aslRandFile")], "-thr", file_rep[i, c("value")], "-mas", file_rep[i, c("parcel_path")], file_rep[i, c("output_file")]))

  system(fsl_command)
}


# Binarize all the resampled mask
bin_dir <- "/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/asl_attention/indiv_att_ouput/bin_resampled_mask/adult/"

# Create subject sub-folders for resampled masks
subdir <- paste0(bin_dir, file_rep$bare_id)
subdir <- unique(subdir)

for (i in 1:length(subdir)) {
  dir.create(subdir[i])
}
# To DO: Fix Scott script to take actual ID input and thus get rid of str_extract here!
file_rep$bin_output <- paste0(bin_dir, file_rep$bare_id, "/bin_resampled_", str_extract(file_rep$output_file, "run-[[:digit:]]_"), tolower(file_rep$stimuli), "_", tolower(file_rep$condition), "_dan.nii.gz")

# Binarize all the resampled mask
for (i in 1:nrow(file_rep)) {

  bin_command <- as.character(paste("fslmaths", file_rep[i, c("output_file")], "-bin",  file_rep[i, c("bin_output")]))

  system(bin_command)
}
```




