---
title: "ABCD Analysis"
author: "An Nguyen"
date: "October 9, 2017"
output:
  pdf_document: default
  html_document: default
header-includes:
  - \usepackage{color}
---
\definecolor{coolblack}{rgb}{0.0, 0.18, 0.39}
\definecolor{violet}{rgb}{0.19, 0.55, 0.91}
```{r,echo=FALSE,warning=FALSE}
#Loading library
library(ggplot2)
library(knitr)
library(readr)
```

```{r,echo=FALSE}
#Initialize variables
total_participant <- 30
total_vsl_trial <- 24 #number of trials in the familiarization block
total_tsl_trial <- 48
length_vsl <- 533 #number of rows in a vsl excel file
length_tsl <- 832 #number of rows in a tsl excel file
total_test_trial <- 32
```


```{r,echo=FALSE}
#importing files


tsl <- list()
vsl <- list()
vsl_par_id <- NULL
tsl_par_id <- NULL
path <- "C:/Users/Qlab/Downloads/sl-analysis/tsl/data/"
files <- list.files(path=path, pattern="*.csv") 
for(file in files)
{
   
    assign(
        gsub(" ","",file), 
        read.csv(paste(path,file,sep="")))
}
for(file in files){tsl <- append(tsl,list(eval(parse(text=file))))}

vsl_path <- "C:/Users/Qlab/Downloads/sl-analysis/vsl/"
vsl_files <- list.files(path=vsl_path, pattern="*.csv")
for(vslfile in vsl_files)
{
    assign(
        gsub(" ","",vslfile), 
        read.csv(paste(vsl_path,vslfile,sep="")))
}
for(text in vsl_files){vsl <- append(vsl,list(eval(parse(text=text))))}

vsl <- do.call(rbind.data.frame, vsl)
tsl <- do.call(rbind.data.frame, tsl)

#add an ID column for each row
for (i in seq(from=1,to=length(vsl$responses),by=length_vsl)){vsl_par_id<-append(vsl_par_id,rep(substr(vsl$responses[i],8,16),length_vsl))}
for (i in seq(from=1,to=length(tsl$responses),by=length_tsl)){tsl_par_id<-append(tsl_par_id,rep(substr(tsl$responses[i],8,16),length_tsl))}
vsl$par_id <- vsl_par_id
tsl$par_id <- tsl_par_id

list_vsl_id <- unique(vsl$par_id)
list_tsl_id <- unique(tsl$par_id)

#Group set up
DD <- list("ABCD_1711", "ABCD_1714", "ABCD_1727", "ABCD_1735", "ABCD_1751", "ABCD_1756", "ABCD_1764", "ABCD_1767", "ABCD_1768")

TYP <- list("ABCD_1702", "ABCD_1703", "ABCD_1705", "ABCD_1708", "ABCD_1709", "ABCD_1710", "ABCD_1716", "ABCD_1720", "ABCD_1721", "ABCD_1724", "ABCD_1725", "ABCD_1728", "ABCD_1729", "ABCD_1730", "ABCD_1732", "ABCD_1734", "ABCD_1736", "ABCD_1739", "ABCD_1742", "ABCD_1747", "ABCD_1749", "ABCD_1754" )
group <- NULL
for (i in seq(from=1,to=length(tsl$par_id),by=1))
    {if (tsl[i,]$par_id %in% TYP)
    {group[i]<-"TYP"}
    else if (tsl[i,]$par_id %in% DD)
    {group[i] <- "DD"}}
tsl$group <- group
groupv <- NULL
for (i in seq(from=1,to=length(vsl$par_id),by=1))
    {if (vsl[i,]$par_id %in% TYP)
    {groupv[i]<-"TYP"}
    else if (vsl[i,]$par_id %in% DD)
    {groupv[i] <- "DD"}}
vsl$group <- groupv


language_1 = list(1,2,2,2,1,1,2,1,1,2,1,2,1,1,2,2,1,1,2,1,2,2,1,2,2,2,1,2,1,2,1,1)
language_2 = list(1,1,2,1,1,1,2,2,2,2,1,1,1,2,2,1,2,2,1,1,2,1,2,1,2,1,2,1,1,2,2,2)
```

```{r,echo=FALSE}
#Clean data

vsl$stimulus<- gsub(".jpg","",vsl$stimulus)
vsl$stimulus<- gsub("../../images/","",vsl$stimulus)

tsl$stimulus<- gsub(".wav","",tsl$stimulus)
tsl$stimulus<- gsub("../../tones/","",tsl$stimulus)
```



```{r,echo=FALSE,warning=FALSE}
vsl_acc <- vsl[which(vsl$trial_index<614 & vsl$trial_index>309),] #the test block starts and ends with this index
tsl_acc <- tsl[which(tsl$trial_index<831 & tsl$trial_index>608),]
vsl_cond <- NULL
for (i in seq(from=1,to=length(vsl$cond),by=length_vsl)){vsl_cond<-append(vsl_cond,as.character(vsl[i,]$cond))}
tsl_cond <- NULL
for (i in seq(from=1,to=length(tsl$cond),by=length_tsl)){tsl_cond<-append(tsl_cond,as.character(tsl[i,]$cond))}

ans <- NULL
keyv <- NULL
subj <- NULL
cond<- NULL

#vsl acc
  row_numberv <- which(vsl_acc$key_press != -1 & vsl_acc$stimulus=="")
  for (i in row_numberv){
    ans<-append(ans,vsl_acc[i,]$key_press)
    subj <- append(subj,vsl_acc[i,]$par_id)
    cond <- append(cond,vsl_acc[i,]$group)
  }
  
vsl_accuracy <- data.frame(ans,subj,cond)

#tsl acc
ans <- NULL
keyt <- NULL
subj <- NULL
cond<- NULL

row_numbert <- which(tsl_acc$key_press != -1 & (tsl_acc$trial_index-613)%%7==0) #since there is no stimuli recorded for the test block of tsl, we can only get the correct answer by counting the index. The test starts at 613 and the response begins every 7 index after that
  for (i in row_numbert){
    ans<-append(ans,tsl_acc[i,]$key_press)
    subj <- append(subj,tsl_acc[i,]$par_id)
   cond <- append(cond,vsl_acc[i,]$group)

  }
 
tsl_accuracy <- data.frame(ans,subj,cond)

for(cond in vsl_cond){
    if (cond=="lang1"){keyv<-append(keyv,language_1)}
    else if (cond=="lang2"){keyv<-append(keyv,language_2)}}

for(cond in tsl_cond){
    if (cond=="lang1"){keyt<-append(keyt,language_1)}
    else if (cond=="lang2"){keyt<-append(keyt,language_2)}}



vsl_accuracy$key <- keyv
tsl_accuracy$key <- keyt

vsl_accuracy$ans <- gsub(50,2,vsl_accuracy$ans)
vsl_accuracy$ans <- gsub(49,1,vsl_accuracy$ans)

tsl_accuracy$ans <- gsub(37,1,tsl_accuracy$ans)
tsl_accuracy$ans <- gsub(39,2,tsl_accuracy$ans)

corr <- NULL
corrt <- NULL

for (i in seq(from=1,to=length(vsl_accuracy$ans),by=1)) {corr<-append(corr,as.numeric(vsl_accuracy[i,]$ans==vsl_accuracy[i,]$key))}
vsl_accuracy$corr <- corr
subj_corr <- NULL
for (id in list_vsl_id) {subj_corr <- append(subj_corr,round(sum(vsl_accuracy$corr[vsl_accuracy$subj==id])/total_test_trial,digits=3))}
vsl_acc_table <- data.frame(list_vsl_id,subj_corr,vsl_cond)

for (i in seq(from=1,to=length(tsl_accuracy$ans),by=1)) {corrt<-append(corrt,as.numeric(tsl_accuracy[i,]$ans==tsl_accuracy[i,]$key))}
tsl_accuracy$corr <- corrt
subj_corrt <- NULL
for (id in list_tsl_id) {subj_corrt <- append(subj_corrt,round(sum(tsl_accuracy$corr[tsl_accuracy$subj==id])/total_test_trial,digits=3))}
tsl_acc_table <- data.frame(list_tsl_id,subj_corrt,tsl_cond)
DD_acc_vsl <- NULL
DD_acc_tsl <- NULL
TYP_acc_vsl <- NULL
TYP_acc_tsl <- NULL

for(id in DD){
  DD_acc_vsl<- append(DD_acc_vsl,vsl_acc_table$subj_corr[vsl_acc_table$list_vsl_id==id])
  DD_acc_tsl<- append(DD_acc_tsl,tsl_acc_table$subj_corr[tsl_acc_table$list_tsl_id==id])
}

for(id in TYP){
  TYP_acc_vsl<- append(TYP_acc_vsl,vsl_acc_table$subj_corr[vsl_acc_table$list_vsl_id==id])
  TYP_acc_tsl<- append(TYP_acc_tsl,tsl_acc_table$subj_corr[tsl_acc_table$list_tsl_id==id])
}
mean_DD_vsl <- mean(DD_acc_vsl,na.rm=TRUE)
mean_DD_tsl <- mean(DD_acc_tsl,na.rm=TRUE)
mean_TYP_vsl <- mean(TYP_acc_vsl,na.rm=TRUE)
mean_TYP_tsl <- mean(TYP_acc_tsl,na.rm=TRUE)
DD_acc_col <- rbind(mean_DD_tsl,mean_DD_vsl)
TYP_acc_col <- rbind(mean_TYP_tsl,mean_TYP_vsl)
compare_acc_table <- cbind(DD_acc_col,TYP_acc_col)
colnames(compare_acc_table) <- c("Dylexia", "Typical")
rownames(compare_acc_table) <- c("TSL accuracy","VSL accuracy")
colnames(tsl_acc_table) <- c("Participant ID", "Percentage correct","Condition")
colnames(vsl_acc_table) <- c("Participant ID", "Percentage correct","Condition")


DDtestv <- t.test(DD_acc_vsl,mu=0.5)
DDtestt <- t.test(DD_acc_tsl,mu=0.5)
TYPtestv <- t.test(TYP_acc_vsl,mu=0.5)
TYPtestt <- t.test(TYP_acc_tsl,mu=0.5)

```
#\textcolor{coolblack}{VSL}

```{r,echo=FALSE}
compute_visual <- function(data)
{
rt_col <- NULL
id <- NULL
trial <- NULL
target <- NULL
group_cond <- NULL
row_number <- which(vsl$targ==vsl$stimulus)
for (i in row_number){
        rt_col <- append(rt_col,vsl[i,][,"rt"])
        trial <- append(trial,vsl[i,][,"trial_index"])
        id <- append(id,vsl[i,]$par_id)
        group_cond <- append(group_cond,vsl[i,]$group)
    if (vsl[i-1,][,"rt"]!=-1){
        rt_col[(match(i,row_number))] <- vsl[i-1,][,"rt"]
        
    }}
rt_df1 <- data.frame(trial,rt_col,id,group_cond)
fam_block <- vsl[which(vsl$trial_index<303 & vsl$trial_index>14),] #the familiarization block starts with index number 15 and ends with index 302
fam_trial <- rt_df1[which(rt_df1$trial<303 & rt_df1$trial>14), ]
reindex <- rep(1:total_vsl_trial,total_participant)
fam_trial$reindex <- reindex
hit_rate <- NULL
miss_rate <- NULL
correct_rejection <- NULL
false_alarm <- NULL
mean_rt <- NULL
rt_slope <- NULL
timeline <- c(rep("first half",total_vsl_trial/2),rep("second half",total_vsl_trial/2))
timeline <- rep(timeline,total_participant)
fam_trial$timeline <- timeline
mean_table <- fam_trial[which(fam_trial$rt_col!=-1 & fam_trial$rt_col<1000 & fam_trial$rt_col>-1000), ] #only accept answers in range of -1000 < x < 1000

for(id in list_vsl_id){
  mean_rt<-append(mean_rt,round(mean(mean_table$rt_col[mean_table$id==id]),digits=3))
  rt_slope <-append(rt_slope,round(summary(lm(mean_table$rt_col[mean_table$id==id]~mean_table$trial[mean_table$id==id]))$coefficient[2,1],digits=3))
  hit_rate<-append(hit_rate,round(sum(!is.na(mean_table$rt_col[mean_table$id==id]))/total_vsl_trial,digits =2))
  miss_rate<-append(miss_rate,round(sum(fam_trial$rt_col[fam_trial$id==id]==-1)/total_vsl_trial,digits=2))
  correct_rejection <- append(correct_rejection, round(sum(fam_block$rt[fam_block$par_id==id]==-1 & fam_block$targ[fam_block$par_id==id]!=fam_block$stimulus[fam_block$par_id==id])/264,digits=2)) #264 is the total number of stimuli in the familiarization block
  false_alarm <- append(false_alarm, round(sum(fam_block$rt[fam_block$par_id==id]!=-1 & fam_block$targ[fam_block$par_id==id]!=fam_block$stimulus[fam_block$par_id==id])/264,digits=2))
}

subj_table <- data.frame(list_vsl_id,mean_rt, rt_slope,hit_rate, miss_rate,correct_rejection,false_alarm)
dprime<-NULL
for (i in seq(from=1,to=length(subj_table$list_vsl_id),by=1)){dprime<-append(dprime,qnorm(subj_table[i,]$hit_rate-0.00000001)-qnorm(subj_table[i,]$false_alarm))} #minus 0.000000001 to avoid perfect hit rate
subj_table$dprime <- dprime

DD_prime_v <- NULL
TYP_prime_v <- NULL
for (i in DD){DD_prime_v <- append(DD_prime_v,subj_table$dprime[subj_table$list_vsl_id==i])}
for (i in TYP){TYP_prime_v <- append(TYP_prime_v,subj_table$dprime[subj_table$list_vsl_id==i])}

dprimetestv <<- wilcox.test(DD_prime_v,TYP_prime_v)

colnames(subj_table) <- c("VSL_ID","mean_rt", "rt_slope","hit", "miss","corr_rejection","false_alarm","dprime")
print(kable(subj_table,format = "pandoc"))

return(mean_table)
}
```

##\textcolor{blue}{Summary Table}
```{r,echo=FALSE,warning=FALSE}
fam_trial_vsl <- compute_visual()

model1v <- lm(rt_col~reindex*group_cond,data=fam_trial_vsl)
model2v <- aov(rt_col~group_cond*timeline + Error(id/timeline),data=fam_trial_vsl)
```

##\textcolor{blue}{Plot of VSL}
```{r,echo=FALSE}
ggplot(fam_trial_vsl,aes(y=rt_col,x=reindex))+geom_point(color='deepskyblue3') + geom_smooth(method='lm') + labs(x="Trial Index", y="Response time (ms)",title="Resposne time by trial index in VSL")
```
```{r,echo=FALSE}
par(mfrow=c(1,2))
boxplot(fam_trial_vsl$rt_col[fam_trial_vsl$reindex<total_vsl_trial/2], main="RT - first half of the trials",col="deepskyblue4",pars=list(ylim=c(100,800)))
boxplot(fam_trial_vsl$rt_col[fam_trial_vsl$reindex>total_vsl_trial/2], main="RT - latter half of the trials",col="deepskyblue4")
```

##\textcolor{blue}{VSL Accuracy across subjects}
```{r,echo=FALSE}
print(kable(vsl_acc_table))
```

#\textcolor{coolblack}{TSL}
```{r,echo=FALSE}
compute_aud <- function(data)
{
rt_col <- NULL
id <- NULL
trial <- NULL
target <- NULL
group_cond <- NULL
row_number <- which(tsl$targ==tsl$stimulus)
for (i in row_number){
  #the audio plays 100ms after the trial begins, and the trial lasts 480ms, hence the number
        if (tsl[i,]$rt > 0){rt_col <- append(rt_col,tsl[i,][,"rt"]-100)} 
        if (tsl[i,]$rt < 0){rt_col <- append(rt_col,100-tsl[i,][,"rt"]-100)}
        trial <- append(trial,tsl[i,][,"trial_index"])
        id <- append(id,tsl[i,]$par_id)
         group_cond <- append(group_cond,tsl[i,]$group)
   if (tsl[i+1,][,"rt"]!=-1000 & tsl[i+1,][,"rt"]<0){
        rt_col[(match(i,row_number))] <- 480-tsl[i+1,][,"rt"]}
    
    if (tsl[i-1,][,"rt"]>0){
        rt_col[(match(i,row_number))] <- 480-tsl[i-1,][,"rt"]
        
    }}
rt_df1 <- data.frame(trial,rt_col,id,group_cond)
fam_block <- tsl[which(tsl$trial_index<603 & tsl$trial_index>26),] #fam block in tsl starts at index 27 and ends at index 602
fam_trial <- rt_df1[which(rt_df1$trial<603 & rt_df1$trial>26), ]
reindex <- rep(1:total_tsl_trial,total_participant)
fam_trial$reindex <- reindex
timeline <- c(rep("first half",total_tsl_trial/2),rep("second half",total_tsl_trial/2))
timeline <- rep(timeline,total_participant)
fam_trial$timeline <- timeline
mean_table <- fam_trial[which(fam_trial$rt_col!=-1000),]
mean_table <- fam_trial[which(fam_trial$rt_col<580 & fam_trial$rt_col>-380), ] #only accepts answer in range of -380 < x < 580 (one stimulus before and one stimulus after the target)
hit_rate <- NULL
miss_rate <- NULL
correct_rejection <- NULL
false_alarm <- NULL
mean_rt <- NULL
rt_slope <- NULL
for(id in list_tsl_id){
  mean_rt<-append(mean_rt,round(mean(mean_table$rt_col[mean_table$id==id]),digits=3))
  rt_slope <-append(rt_slope,round(summary(lm(mean_table$rt_col[mean_table$id==id]~mean_table$trial[mean_table$id==id]))$coefficient[2,1],digits=3))
  hit_rate<-append(hit_rate,round(sum(mean_table$rt_col[mean_table$id==id]!=-1000)/total_tsl_trial,digits =2))
  miss_rate<-append(miss_rate,round(sum(fam_trial$rt_col[fam_trial$id==id]==-1000 | fam_trial$rt_col[fam_trial$id==id]<=-480 | fam_trial$rt_col[fam_trial$id==id]>960)/total_tsl_trial,digits=2))
  correct_rejection <- append(correct_rejection, round(sum(fam_block$rt[fam_block$par_id==id]==-1000 & fam_block$targ[fam_block$par_id==id]!=fam_block$stimulus[fam_block$par_id==id])/528,digits=2)) #528 is the total number of stimuli in the fam block
  false_alarm <- append(false_alarm, round(sum(fam_block$rt[fam_block$par_id==id]!=-1000 & fam_block$targ[fam_block$par_id==id]!=fam_block$stimulus[fam_block$par_id==id])/528,digits=2))
}


subj_table <- data.frame(list_tsl_id,mean_rt, rt_slope,hit_rate, miss_rate,correct_rejection,false_alarm)
dprime<-NULL
for (i in seq(from=1,to=length(subj_table$list_tsl_id),by=1)){dprime<-append(dprime,qnorm(subj_table[i,]$hit_rate-0.00000001)-qnorm(subj_table[i,]$false_alarm))}
subj_table$dprime <- dprime

DD_prime_t <- NULL
TYP_prime_t <- NULL
for (i in DD){DD_prime_t <- append(DD_prime_t,subj_table$dprime[subj_table$list_tsl_id==i])}
for (i in TYP){TYP_prime_t <- append(TYP_prime_t,subj_table$dprime[subj_table$list_tsl_id==i])}

dprimetest <<- wilcox.test(DD_prime_t,TYP_prime_t)

colnames(subj_table) <- c("TSL_ID","mean_rt", "rt_slope","hit", "miss","corr_rejection","false_alarm","dprime")
print(kable(subj_table,format = "pandoc"))
return(mean_table)
}
```

##\textcolor{blue}{Summary Table}
```{r,echo=FALSE,warning=FALSE}
fam_trial_tsl <- compute_aud()

model1 <- lm(rt_col~reindex*group_cond,data=fam_trial_tsl)
model2 <- aov(rt_col~group_cond*timeline + Error(id/timeline),data=fam_trial_tsl)
```

##\textcolor{blue}{Plot of TSL}
```{r,echo=FALSE}
ggplot(fam_trial_tsl,aes(y=rt_col,x=reindex))+geom_point(color='deepskyblue3') + geom_smooth(method='lm') + labs(x="Trial Index", y="Response time (ms)",title="Resposne time by trial index in TSL")
```

```{r,echo=FALSE}
par(mfrow=c(1,2))
boxplot(fam_trial_tsl$rt_col[fam_trial_tsl$reindex<total_tsl_trial/2], main="RT - first half of the trials",col="deepskyblue4")
boxplot(fam_trial_tsl$rt_col[fam_trial_tsl$reindex>total_tsl_trial/2], main="RT - latter half of the trials",col="deepskyblue4")

```

##\textcolor{blue}{TSL Accuracy across subjects}
```{r,echo=FALSE}
print(kable(tsl_acc_table))
```

#\textcolor{coolblack}{Compare between Dylexia and Typical group}

##\textcolor{blue}{Performance in familiarization phase}
```{r,fig.width=10, fig.height=6, echo=FALSE}
DD_mean_vsl <- NULL
DD_mean_tsl <- NULL
DD_tsl_hit_rate <- NULL
DD_vsl_hit_rate <- NULL
TYP_mean_vsl <- NULL
TYP_mean_tsl <- NULL
TYP_tsl_hit_rate <- NULL
TYP_vsl_hit_rate <- NULL
number_DD <- NULL
number_TYP <- NULL

for(id in DD){
  DD_mean_vsl<- mean(append(DD_mean_vsl,round(mean(fam_trial_vsl$rt_col[fam_trial_vsl$id==id]))),na.rm=TRUE)
  DD_mean_tsl<- mean(append(DD_mean_tsl,round(mean(fam_trial_tsl$rt_col[fam_trial_tsl$id==id]))),na.rm=TRUE)
  DD_vsl_hit_rate<-round(mean(append(DD_vsl_hit_rate,round(sum(fam_trial_vsl$rt_col[fam_trial_vsl$id==id]!=-1)/total_vsl_trial,digits =2)),na.rm=TRUE),digits=2)
  DD_tsl_hit_rate<-round(mean(append(DD_tsl_hit_rate,round(sum(fam_trial_tsl$rt_col[fam_trial_tsl$id==id]!=-1000)/total_tsl_trial,digits =2)),na.rm=TRUE),digits=2) 
  number_DD <- length(intersect(list_vsl_id, DD))
}

for(id in TYP){
  TYP_mean_vsl<-mean(append(TYP_mean_vsl,round(mean(fam_trial_vsl$rt_col[fam_trial_vsl$id==id]))),na.rm=TRUE)
   TYP_mean_tsl<-mean(append(TYP_mean_tsl,round(mean(fam_trial_tsl$rt_col[fam_trial_tsl$id==id]))),na.rm=TRUE)
  TYP_vsl_hit_rate<-round(mean(append(TYP_vsl_hit_rate,round(sum(fam_trial_vsl$rt_col[fam_trial_vsl$id==id]!=-1)/total_vsl_trial,digits =2)),na.rm=TRUE),digits=2)
  TYP_tsl_hit_rate<-round(mean(append(TYP_tsl_hit_rate,round(sum(fam_trial_tsl$rt_col[fam_trial_tsl$id==id]!=-1000)/total_tsl_trial,digits =2)),na.rm=TRUE),digits=2)
  number_TYP <- length(intersect(list_vsl_id, TYP))
}

DD_col <- rbind(DD_mean_tsl,DD_mean_vsl,DD_tsl_hit_rate,DD_vsl_hit_rate,number_DD)
TYP_col <- rbind(TYP_mean_tsl,TYP_mean_vsl,TYP_tsl_hit_rate,TYP_vsl_hit_rate,number_TYP)
compare_table <- cbind(DD_col,TYP_col)
colnames(compare_table) <- c("Dylexia","Typical")
rownames(compare_table) <- c("RT_TSL","RT_VSL","Hit_rate_tsl","Hit_rate_vsl","Number of participants")
print(kable(compare_table))
par(mfrow=c(1,2))

qplot(reindex,rt_col,data=fam_trial_vsl,facets=(. ~ fam_trial_vsl$group_cond),color= group_cond, main="VSL RT by group", ylab="Response time", xlab="Trial index") + geom_smooth(method='lm') + scale_color_discrete(name="Group",labels=c("Dylexia","Typical"))
qplot(reindex,rt_col,data=fam_trial_tsl,facets=(. ~ fam_trial_tsl$group_cond),color= group_cond,main="TSL RT by group",ylab="Response time", xlab="Trial index") + geom_smooth(method='lm') + scale_color_discrete(name="Group",labels=c("Dylexia","Typical"))

```

##\textcolor{blue}{Accuracy between Dylexia and Typical group}
```{r,echo=FALSE}
print(kable(compare_acc_table))

```


## \textcolor{blue}{A line plot to compare mean accuracy of each group accross 32 trials}
```{r,echo=FALSE}
 index <- rep(1:total_test_trial,total_participant)
indx <- c(1:total_test_trial)
vsl_accuracy$index <- index
tsl_accuracy$index <- index
DD_vsl_point <- NULL
TYP_vsl_point <- NULL
DD_tsl_point <- NULL
TYP_tsl_point <- NULL
for (i in indx){DD_vsl_point <- append(DD_vsl_point,mean(vsl_accuracy$corr[vsl_accuracy$index==i & vsl_accuracy$cond=="DD"]))
DD_tsl_point <- append(DD_tsl_point,mean(tsl_accuracy$corr[tsl_accuracy$index==i & tsl_accuracy$cond=="DD"]))
TYP_tsl_point <- append(TYP_tsl_point,mean(tsl_accuracy$corr[tsl_accuracy$index==i & tsl_accuracy$cond=="TYP"]))
TYP_vsl_point <- append(TYP_vsl_point,mean(vsl_accuracy$corr[vsl_accuracy$index==i & vsl_accuracy$cond=="TYP"]))}
DDi <- rep("DD",total_test_trial)
Ti <- rep("TYP",total_test_trial)
dv <- cbind(DD_vsl_point,indx,DDi)
tv <- cbind(TYP_vsl_point,indx,Ti)
dt <- cbind(DD_tsl_point,indx,DDi)
tt <- cbind(TYP_tsl_point,indx,Ti)
vtable <- data.frame(rbind(dv,tv))
ttable <- data.frame(rbind(dt,tt))

ggplot(data=vtable,aes(x=as.numeric(indx),y=as.numeric(paste(DD_vsl_point)), color=DDi,group=DDi),ylim=c(0,1)) + geom_point() + geom_line() + ggtitle("Accuracy accross trials in VSL") + xlab("Trial index")+ylab("Accuracy (%)") + scale_color_discrete(name="Group",labels=c("Dylexia","Typical"))
ttable <- data.frame(rbind(dt,tt))
ggplot(data=ttable,aes(x=as.numeric(indx),y=as.numeric(paste(DD_tsl_point)), color=DDi,group=DDi),ylim=c(0,1)) + geom_point() + geom_line() + ggtitle("Accuracy accross trials in TSL") + xlab("Trial index")+ylab("Accuracy (%)") + scale_color_discrete(name="Group",labels=c("Dylexia","Typical"))
```

##\textcolor{blue}{A box plot to compare the average accuracy between each group}
```{r,fig.width=10, fig.height=10, echo=FALSE}
par(mfrow=c(2,2))
boxplot(DD_vsl_point, main="Dylexia-VSL",col="deepskyblue4", pars=list(ylim=c(0.2,1)))
boxplot(TYP_vsl_point, main="Typical-VSL",col="deepskyblue4", pars=list(ylim=c(0.2,1)))

boxplot(DD_tsl_point, main="Dylexia-TSL",col="deepskyblue4", pars=list(ylim=c(0.2,1)))

boxplot(TYP_vsl_point, main="Typical-TSL",col="deepskyblue4", pars=list(ylim=c(0.2,1)))
```


##\textcolor{coolblack}{In vsl}


##\textcolor{blue}{Linear regression model}
```{r,echo=FALSE}
print(summary(model1v))
```
##\textcolor{blue}{Anova table}
```{r,echo=FALSE,warning=FALSE}
print(model2)
print(summary(model2v))

```

## \textcolor{blue}{Wilcox test between dprime of Dylexia and Typical}

```{r,echo=FALSE}
print(dprimetestv)

```
## \textcolor{blue}{t-test to make sure that the accuracy of each group is above chance}
### \textcolor{violet}{t-test of Dylexia group}
```{r,echo=FALSE}
print(DDtestv)
```

### \textcolor{violet}{t-test of Typical group}
```{r,echo=FALSE}
print(TYPtestv)
```
##\textcolor{blue}{A t-test to compare accuracy between Dylexia and Typical group}

```{r,echo=FALSE}
t.test(DD_acc_vsl,TYP_acc_vsl)
```

##\textcolor{coolblack}{In tsl}

##\textcolor{blue}{Linear regression model}
```{r,echo=FALSE}
print(summary(model1))
```
##\textcolor{blue}{Anova table}
```{r,echo=FALSE,warning=FALSE}
print(model2)
print(summary(model2))
```

## \textcolor{blue}{Wilcox test between dprime of Dylexia and Typical}

```{r,echo=FALSE}
print(dprimetest)

```
## \textcolor{blue}{t-test to make sure that the accuracy of each group is above chance}
### \textcolor{violet}{t-test of Dylexia group}
```{r,echo=FALSE}
print(DDtestt)
```

### \textcolor{violet}{t-test of Typical group}
```{r,echo=FALSE}
print(TYPtestt)
```

##\textcolor{blue}{A t-test to compare accuracy between Dylexia and Typical group}
```{r,echo=FALSE}
t.test(DD_acc_tsl,TYP_acc_tsl)
```
