---
title: "tsl_analysis"
author: "An Nguyen"
date: "November 9, 2017"
output: html_document
header-includes:
  - \usepackage{color}
---
\definecolor{coolblack}{rgb}{0.0, 0.18, 0.39}
\definecolor{violet}{rgb}{0.19, 0.55, 0.91}
```{r,echo=FALSE,warning=FALSE}
#Loading library
library(ggplot2)
library(knitr)
library(readr)
library(ppcor)

```


```{r,echo=FALSE}
#Please refer to mturk_vsl to see the specific comment for each step, since they are similar 


#importing files
total_tsl_trial <- 48
language_1 = list(1,2,2,2,1,1,2,1,1,2,1,2,1,1,2,2,1,1,2,1,2,2,1,2,2,2,1,2,1,2,1,1)
language_2 = list(1,1,2,1,1,1,2,2,2,2,1,1,1,2,2,1,2,2,1,1,2,1,2,1,2,1,2,1,1,2,2,2)

tsl <- read_csv("Z:/projects/mturk/raw/cleaned_data/tsl2.csv")
wj3 <- read.csv("C:/Users/Qlab/Downloads/mturk/mturk_data/wj3_score.csv")
scf <-  read.csv("C:/Users/Qlab/Downloads/mturk/mturk_data/scf.csv")
#Clean data


tsl$stimulus<- gsub(".wav","",tsl$stimulus)
tsl$stimulus<- gsub("../../tones/","",tsl$stimulus)

```


```{r,echo=FALSE}
#analysis on RT

fam_block <- tsl[which(tsl$trial_index<=600 & tsl$trial_index>=24),]
fam_block <- fam_block[!(fam_block$stimulus=="../../tone_instr/instr_8"),]
fam_block <- fam_block[!(fam_block$stimulus=="../../tone_instr/fixation_instr"),]
fam_block$targ <- paste(fam_block$targ)
fam_block$stimulus <- paste(fam_block$stimulus)
fam_block$rt <- as.numeric(paste(fam_block$rt))

rt_col <- NULL
id <- NULL
trial <- NULL
target <- NULL
row_number <- which(fam_block$targ==fam_block$stimulus)
for (i in row_number){
    if (fam_block[i,]$rt > 0){rt_col <- append(rt_col,fam_block[i,][,"rt"]-100)} 
    if (fam_block[i,]$rt < 0){rt_col <- append(rt_col,fam_block[i,][,"rt"])}
    trial <- append(trial,paste(fam_block[i,][,"trial_index"]))
    id <- append(id,paste(fam_block[i,]$par_id))
    if (fam_block[i+1,][,"rt"]!=-1000 & fam_block[i+1,][,"rt"]<0){
        rt_col[(match(i,row_number))] <- 380-fam_block[i+1,][,"rt"]}
 
      if (fam_block[i+1,][,"rt"]!=-1000 & fam_block[i+1,][,"rt"]>0){
    rt_col[(match(i,row_number))] <- 580+fam_block[i+1,][,"rt"]}
    
    if (fam_block[i-1,][,"rt"]>0){
        rt_col[(match(i,row_number))] <- 480-fam_block[i-1,][,"rt"]
        
    }}

fam_trial <- data.frame(unlist(trial),unlist(rt_col),id)
colnames(fam_trial) <- c("trial","rt_col","id")
reindex <- rep(1:total_tsl_trial,length(fam_trial$trial)/48)
fam_trial$reindex <- reindex
hit_rate <- NULL
miss_rate <- NULL
correct_rejection <- NULL
false_alarm <- NULL
mean_rt <- NULL
rt_slope <- NULL
timeline <- c(rep("first half",total_tsl_trial/2),rep("second half",total_tsl_trial/2))
timeline <- rep(timeline,length(fam_trial$trial)/48)
fam_trial$timeline <- timeline
mean_table <- fam_trial[which(fam_trial$rt_col!=-1000 & fam_trial$rt_col<960 & fam_trial$rt_col>-480), ] #only accept answers in range of -1000 < x < 1000

#exclude people who only have one rt point, so rtslope cannot be computed
#mean_table <- mean_table[mean_table$id!="A3QS96739O5M6F",]
#mean_table <- mean_table[mean_table$id!="A36TE52PSYAAD6",]
#mean_table <- mean_table[mean_table$id!="mtslcc0991",]
#mean_table <- mean_table[mean_table$id!="mtslnn0585",]
#mean_table <- mean_table[mean_table$id!="mtslsc0184",]
list_tsl_id <- unique(mean_table$id)
for(id in list_tsl_id){
  mean_rt<-append(mean_rt,round(mean(mean_table$rt_col[mean_table$id==id]),digits=3))
  rt_slope <-append(rt_slope,round(summary(lm(mean_table$rt_col[mean_table$id==id]~mean_table$reindex[mean_table$id==id]))$coefficient[2,1],digits=3))
  hit_rate<-append(hit_rate,round(sum(!is.na(mean_table$rt_col[mean_table$id==id]))/total_tsl_trial,digits =2))
  miss_rate<-append(miss_rate,round(sum(fam_trial$rt_col[fam_trial$id==id]==-1000)/total_tsl_trial,digits=2))
  correct_rejection <- append(correct_rejection, round(sum(fam_block$rt[fam_block$par_id==id]==-1000 & fam_block$targ[fam_block$par_id==id]!=fam_block$stimulus[fam_block$par_id==id])/528,digits=2)) #528 is the total number of stimuli in the familiarization block
  false_alarm <- append(false_alarm, round(sum(fam_block$rt[fam_block$par_id==id]!=-1000 & fam_block$targ[fam_block$par_id==id]!=fam_block$stimulus[fam_block$par_id==id])/528,digits=2))
}

subj_table <- data.frame(list_tsl_id,mean_rt, rt_slope,hit_rate, miss_rate,correct_rejection,false_alarm)
dprime<-NULL
for (i in seq(from=1,to=length(subj_table$list_tsl_id),by=1)){dprime<-append(dprime,qnorm(subj_table[i,]$hit_rate-0.00000001)-qnorm(subj_table[i,]$false_alarm+0.000000001))} #minus 0.000000001 to avoid perfect hit rate
subj_table$dprime <- round(dprime,3)

wj3$ID<-gsub("_wj3.csv","",wj3$ID)
for(id in wj3$ID){ subj_table$wj3_score[which(subj_table$list_tsl_id==id)]<-wj3$total[wj3$ID==id]}

for(id in scf$ID){ subj_table$gender[which(subj_table$list_tsl_id==id)]<-paste(scf$Gender[scf$ID==id])}
for(id in scf$ID){ subj_table$handedness[which(subj_table$list_tsl_id==id)]<-paste(scf$Hand[scf$ID==id])}
for(id in scf$ID){ subj_table$Language[which(subj_table$list_tsl_id==id)]<-paste(scf$Language[scf$ID==id])}
for(id in scf$ID){ subj_table$age[which(subj_table$list_tsl_id==id)]<-paste(scf$age[scf$ID==id])}

subj_table$Language <- as.numeric(subj_table$Language)
subj_table$age <- as.numeric(subj_table$age)

lowerbound <- mean(subj_table$rt_slope) - 2.5*sd(subj_table$rt_slope)
upperbound <- mean(subj_table$rt_slope) + 2.5*sd(subj_table$rt_slope)
subj_table <- subj_table[subj_table$rt_slope>=lowerbound,]
subj_table <- subj_table[subj_table$rt_slope<=upperbound,]


```

```{r,echo=FALSE}
#test block
 test_block <- tsl[which(tsl$trial_index<=829 & tsl$trial_index>=605),]
test_block <- test_block[!(test_block$stimulus==""),]
test_block <- test_block[!(test_block$stimulus=="silent" & test_block$key_press==-1),]

ans <- NULL
keyv <- NULL
subj <- NULL
cond<- NULL

 row_number <- which(test_block$key_press != -1 & test_block$stimulus=="silent")
  for (i in row_number){
    ans<-append(ans,test_block[i,]$key_press)
    subj <- append(subj,paste(test_block[i,]$par_id))
    cond <- append(cond,paste(test_block[i,]$cond))
  }
  
tsl_accuracy <- data.frame(ans,subj,cond)
tsl_accuracy <- tsl_accuracy[!(tsl_accuracy$ans==32),]
tsl_cond <- NULL
for (i in seq(from=1,to=length(tsl_accuracy$cond),by=32)){tsl_cond<-append(tsl_cond,as.character(tsl_accuracy[i,]$cond))}

key<- NULL


for(cond in tsl_cond){
    if (cond=="lang1"){key<-append(key,language_1)}
    else if (cond=="lang2"){key<-append(key,language_2)}}



acc_id <- unique(tsl_accuracy$subj)

tsl_accuracy$key <- key

tsl_accuracy$ans <- gsub(37,1,tsl_accuracy$ans)
tsl_accuracy$ans <- gsub(39,2,tsl_accuracy$ans)

corr <- NULL
for (i in seq(from=1,to=length(tsl_accuracy$ans),by=1)) {corr<-append(corr,as.numeric(tsl_accuracy[i,]$ans==tsl_accuracy[i,]$key))}
tsl_accuracy$corr <- corr
subj_corr <- NULL
for (id in acc_id) {subj_corr <- append(subj_corr,round(sum(tsl_accuracy$corr[tsl_accuracy$subj==id])/32,digits=3))}
tsl_acc_table <- data.frame(acc_id,subj_corr,tsl_cond)


lowerbound <- mean(tsl_acc_table$subj_corr) - 2.5*sd(tsl_acc_table$subj_corr)
upperbound <- mean(tsl_acc_table$subj_corr) + 2.5*sd(tsl_acc_table$subj_corr)
tsl_acc_table <- tsl_acc_table[tsl_acc_table$subj_corr>=lowerbound,]
tsl_acc_table <- tsl_acc_table[tsl_acc_table$subj_corr<=upperbound,]


for(id in scf$ID){ tsl_acc_table$gender[which(tsl_acc_table$acc_id==id)]<-paste(scf$Gender[scf$ID==id])}
for(id in wj3$ID){ tsl_acc_table$wj3_score[which(tsl_acc_table$acc_id==id)]<-wj3$total[wj3$ID==id]}
for(id in scf$ID){ tsl_acc_table$hand[which(tsl_acc_table$acc_id==id)]<-paste(scf$Hand[scf$ID==id])}
 for(id in scf$ID){ tsl_acc_table$age[which(tsl_acc_table$acc_id==id)]<-paste(scf$age[scf$ID==id])}

 for(id in scf$ID){ tsl_acc_table$Language[which(tsl_acc_table$acc_id==id)]<-paste(scf$Language[scf$ID==id])}
tsl_acc_table$Language <- as.numeric(tsl_acc_table$Language)
tsl_acc_table$age <- as.numeric(tsl_acc_table$age)

```


### Cronbach's alpha score
```{r,echo=FALSE,warning=FALSE}
#d <- matrix(nrow=(length(tsl_accuracy$ans)/32),ncol=32)
#for(i in seq(from=1,to=(length(tsl_accuracy$ans)/32),by=1)){d[i,] <- rbind(tsl_accuracy$corr[((i-1)*32+1):(i*32)])}
#psych::alpha(d,check.keys = TRUE)$total$std.alpha

tsl_acc1 <- tsl_accuracy[tsl_accuracy$cond=="lang1",]
d1 <- matrix(nrow=66,ncol=32)
for(i in seq(from=1,to=66,by=1)){d1[i,] <- rbind(tsl_acc1$corr[((i-1)*32+1):(i*32)])}
a1<-psych::alpha(d1,check.keys = TRUE)$total$std.alpha

tsl_acc2 <- tsl_accuracy[tsl_accuracy$cond=="lang2",]
d2 <- matrix(nrow=67,ncol=32)
for(i in seq(from=1,to=67,by=1)){d2[i,] <- rbind(tsl_acc2$corr[((i-1)*32+1):(i*32)])}
a2<-psych::alpha(d2,check.keys = TRUE)$total$std.alpha

alpha <- mean(a1,a2)
print(alpha)
```


#Testing SL ability through the task:
###Looking at RT 

```{r,echo=FALSE,warning=FALSE}
t.test(subj_table$rt_slope,mu=0,alternative="less")

ggplot(mean_table,aes(y=rt_col,x=reindex))+geom_point(color='deepskyblue3') + geom_smooth(method='lm') + labs(x="Trial Index", y="Response time (ms)",title="Resposne time by trial index in tsl")

```

###Looking at Accuracy: the mean accuracy of this task is above chance (50%)
```{r,echo=FALSE}
t.test(tsl_acc_table$subj_corr,mu=0.5,alternative="greater")
```


```{r,echo=FALSE,warning=FALSE,include=FALSE}
#RT by WJ4 score
#ggplot(subj_table[subj_table$wj3_score>25,],aes(y=mean_rt,x=wj3_score))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="WJ4 Score", y="Response time (ms)",title="Resposne time by WJ4 score in tsl") + ylim(c(100,700))

#RT Slope by WJ4
#ggplot(subj_table[subj_table$wj3_score>25,],aes(y=rt_slope,x=wj3_score))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="WJ4 Score", y="Response time slope",title="Resposne time slope by WJ4 score in tsl")  + ylim(c(-15,15))

#RT slope  vs WJ4 score by gender
#qplot(wj3_score,rt_slope,data=subset1[subset1$wj3_score>25,],facets=(. ~ gender),color= gender, main="tsl RT slope vs WJ4 scpre by gender", ylab="RT Slope", xlab="WJ4 score", ylim=c(-15,15)) + geom_smooth(method='lm') + scale_color_discrete(name="Gender")


#Mean rt vs WJ4 score by Handedness
#qplot(wj3_score,mean_rt,data=subj_table[subj_table$wj3_score>25,],facets=(. ~ handedness),color= handedness, main="tsl RT vs WJ4 score by Handedness", ylab="Response time", xlab="WJ4 score", ylim=c(100,600)) + geom_smooth(method='lm') + scale_color_discrete(name="Handedness")
#RT Slope vs WJ4 score by Handedness
#qplot(wj3_score,rt_slope,data=subj_table[subj_table$wj3_score>25,],facets=(. ~ handedness),color= handedness, main="tsl RT slope vs WJ4 score by Handedness", ylab="Response time slope", xlab="WJ4 score", ylim=c(-15,15)) + geom_smooth(method='lm') + scale_color_discrete(name="Handedness")



#RT by Language
#ggplot(subset2,aes(y=mean_rt,x=Language))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="WJ4 Score", y="Response time (ms)",title="Resposne time by Language score in tsl") + ylim(c(100,700))
#RT Slope by Language
#ggplot(subset2,aes(y=rt_slope,x=Language))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="WJ4 Score", y="Response time (ms)",title="Resposne time slope by Language score in tsl") + ylim(c(-15,15))



```

## A simple correlation test between WJ4 score and RT Slope, controlling for age
```{r,echo=FALSE}

#correlation test between rt slope and wj4 score
pcor.test(subj_table$rt_slope, subj_table$wj3_score,subj_table$age,method="spearman")
```

## A simple correlation test between WJ4 score and Accuracy, controlling for age
```{r,echo=FALSE}
#correlation test between rt slope and wj4 score
pcor.test(tsl_acc_table$subj_corr,tsl_acc_table$wj3_score,tsl_acc_table$age,method="spearman")
```

##RT slope and other factors
```{r,echo=FALSE}
a<-lm(formula = subj_corr ~ wj3_score * age + as.factor(hand) + as.factor(gender), data = tsl_acc_table)
summary(a)
```
##Accuracy and other factors
```{r,echo=FALSE}
a1<-lm(formula = rt_slope ~ wj3_score * age + as.factor(handedness) + as.factor(gender), data = subj_table)
summary(a1)
```



