---
title: "ssl_analysis"
author: "An Nguyen"
date: "November 9, 2017"
output: html_document
header-includes:
  - \usepackage{color}
---



\definecolor{coolblack}{rgb}{0.0, 0.18, 0.39}
\definecolor{violet}{rgb}{0.19, 0.55, 0.91}
```{r,echo=FALSE,warning=FALSE}
#Loading library
library(ggplot2)
library(knitr)
library(readr)
library(ppcor)
```


```{r,echo=FALSE,warning=FALSE}
#Please refer to mturk_ssl to see the specific comment for each step, since they are similar 

#importing files
total_ssl_trial <- 48
language_1 = list(1,1,2,1,1,1,2,2,1,1,1,2,2,1,2,1,2,2,1,2,1,1,2,2,2,2,1,1,2,1,2,2)
language_2 = list(1,1,2,1,1,1,2,2,2,2,1,1,1,2,2,1,2,2,1,1,2,1,2,1,2,1,2,1,1,2,2,2)

ssl <- read_csv("Z:/projects/mturk/raw/cleaned_data/ssl2.csv")
wj3 <- read.csv("C:/Users/Qlab/Downloads/mturk/mturk_data/wj3_score.csv")
scf <-  read.csv("C:/Users/Qlab/Downloads/mturk/mturk_data/scf.csv")
#Clean data

#for ssl2
ssl_par_id <- NULL
for (i in seq(from=2,to=length(ssl$responses),by=816)){ssl_par_id<-append(ssl_par_id,rep(as.character(ssl$value[i]),816))}
ssl$par_id<-ssl_par_id

ssl$stimulus<- gsub(".wav","",ssl$stimulus)
ssl$stimulus<- gsub("sound/","",ssl$stimulus)

```


```{r,echo=FALSE}
#analysis on RT

fam_block <- ssl[which(ssl$trial_index<=586 & ssl$trial_index>=11),]
fam_block <- fam_block[!(fam_block$stimulus=="ssl_instr7"),]
fam_block <- fam_block[!(fam_block$stimulus=="ssl_instr8"),]
fam_block$targ <- paste(fam_block$targ)
fam_block$stimulus <- paste(fam_block$stimulus)
fam_block$rt <- as.numeric(paste(fam_block$rt))

rt_col <- NULL
id <- NULL
trial <- NULL
target <- NULL
row_number <- which(fam_block$targ==fam_block$stimulus)
for (i in row_number){
    if (fam_block[i,]$rt > 0){rt_col <- append(rt_col,fam_block[i,][,"rt"]-100)} 
    if (fam_block[i,]$rt < 0){rt_col <- append(rt_col,fam_block[i,][,"rt"])}
    trial <- append(trial,paste(fam_block[i,][,"trial_index"]))
    id <- append(id,paste(fam_block[i,]$par_id))
    if (fam_block[i+1,][,"rt"]!=-1000 & fam_block[i+1,][,"rt"]<0){
        rt_col[(match(i,row_number))] <- 380-fam_block[i+1,][,"rt"]}
    
    if (fam_block[i+1,][,"rt"]!=-1000 & fam_block[i+1,][,"rt"]>0){
    rt_col[(match(i,row_number))] <- 580+fam_block[i+1,][,"rt"]}
    
    if (fam_block[i-1,][,"rt"]>0){
        rt_col[(match(i,row_number))] <- 480-fam_block[i-1,][,"rt"]
        
    }}
fam_trial <- data.frame(unlist(trial),unlist(rt_col),id)
colnames(fam_trial) <- c("trial","rt_col","id")
a<-NULL
for (i in (unique(fam_trial$id))){a<- append(a,sum(fam_trial$id==i))}
reindex <- NULL
for (i in a) {reindex <- append(reindex,rep(1:i,1))}     
fam_trial$reindex <- reindex
hit_rate <- NULL
miss_rate <- NULL
correct_rejection <- NULL
false_alarm <- NULL
mean_rt <- NULL
rt_slope <- NULL



mean_table <- fam_trial[which(fam_trial$rt_col!=-1000 & fam_trial$rt_col<960 & fam_trial$rt_col>-480), ] #only accept answers in range of -1000 < x < 1000

#mean_table <- mean_table[mean_table$id!="A1KAIOBTXQ77A6",]
#mean_table <- mean_table[mean_table$id!="mtslAG1213",]
mean_table <- mean_table[mean_table$id!="A2Z0XILU6M38BTn",]

list_ssl_id <- unique(mean_table$id)
for(id in list_ssl_id){
  mean_rt<-append(mean_rt,round(mean(mean_table$rt_col[mean_table$id==id]),digits=3))
 rt_slope <-append(rt_slope,round(summary(lm(mean_table$rt_col[mean_table$id==id]~mean_table$reindex[mean_table$id==id]))$coefficient[2,1],digits=3))
  hit_rate<-append(hit_rate,round(sum(!is.na(mean_table$rt_col[mean_table$id==id]))/sum(fam_trial$id==id),digits =2))
  miss_rate<-append(miss_rate,round(sum(fam_trial$rt_col[fam_trial$id==id]==-1000)/sum(fam_trial$id==id),digits=2))
  correct_rejection <- append(correct_rejection, round(sum(fam_block$rt[fam_block$par_id==id]==-1000 & fam_block$targ[fam_block$par_id==id]!=fam_block$stimulus[fam_block$par_id==id])/528,digits=2)) #528 is the total number of stimuli in the familiarization block
  false_alarm <- append(false_alarm, round(sum(fam_block$rt[fam_block$par_id==id]!=-1000 & fam_block$targ[fam_block$par_id==id]!=fam_block$stimulus[fam_block$par_id==id])/528,digits=2))
}

subj_table <- data.frame(list_ssl_id,mean_rt, rt_slope,hit_rate, miss_rate,correct_rejection,false_alarm)
dprime<-NULL
for (i in seq(from=1,to=length(subj_table$list_ssl_id),by=1)){dprime<-append(dprime,qnorm(subj_table[i,]$hit_rate-0.00000001)-qnorm(subj_table[i,]$false_alarm+0.000000001))} #minus 0.000000001 to avoid perfect hit rate
subj_table$dprime <- round(dprime,3)


#Add Wj4 score into a column to look at SL performance and language skills
wj3$ID<-gsub("_wj3.csv","",wj3$ID)
for(id in wj3$ID){ subj_table$wj3_score[which(subj_table$list_ssl_id==id)]<-wj3$total[wj3$ID==id]}

for(id in scf$ID){ subj_table$gender[which(subj_table$list_ssl_id==id)]<-paste(scf$Gender[scf$ID==id])}
for(id in scf$ID){ subj_table$handedness[which(subj_table$list_ssl_id==id)]<-paste(scf$Hand[scf$ID==id])}
for(id in scf$ID){ subj_table$Language[which(subj_table$list_ssl_id==id)]<-paste(scf$Language[scf$ID==id])}
for(id in scf$ID){ subj_table$age[which(subj_table$list_ssl_id==id)]<-paste(scf$age[scf$ID==id])}
subj_table$Language <- as.numeric(subj_table$Language)
subj_table$age <- as.numeric(subj_table$age)

lowerbound <- mean(subj_table$rt_slope) - 2.5*sd(subj_table$rt_slope)
upperbound <- mean(subj_table$rt_slope) + 2.5*sd(subj_table$rt_slope)
subj_table <- subj_table[subj_table$rt_slope>=lowerbound,]
subj_table <- subj_table[subj_table$rt_slope<=upperbound,]

subset2<- subj_table[subj_table$Language>=20,]
subset1 <- subj_table[subj_table$gender!="Other",]

```

```{r, echo=FALSE}
#test block
test_block <- ssl[which(ssl$trial_index<=814 & ssl$trial_index>=590),]
test_block <- test_block[!(test_block$stimulus==""),]
test_block <- test_block[!(test_block$stimulus=="silence" & test_block$key_press==-1),]

ans <- NULL
keyv <- NULL
subj <- NULL
cond<- NULL

 row_number <- which(test_block$key_press != -1 & test_block$stimulus=="silence")
  for (i in row_number){
    ans<-append(ans,test_block[i,]$key_press)
    subj <- append(subj,paste(test_block[i,]$par_id))
    cond <- append(cond,paste(test_block[i,]$cond))
  }
  
ssl_accuracy <- data.frame(ans,subj,cond)
ssl_cond <- NULL
for (i in seq(from=1,to=length(ssl_accuracy$cond),by=32)){ssl_cond<-append(ssl_cond,as.character(ssl_accuracy[i,]$cond))}

key<- NULL


for(cond in ssl_cond){
    if (cond=="lang1"){key<-append(key,language_1)}
    else if (cond=="lang2"){key<-append(key,language_2)}}



acc_id <- unique(ssl_accuracy$subj)

ssl_accuracy$key <- key

ssl_accuracy$ans <- gsub(37,1,ssl_accuracy$ans)
ssl_accuracy$ans <- gsub(39,2,ssl_accuracy$ans)

corr <- NULL
for (i in seq(from=1,to=length(ssl_accuracy$ans),by=1)) {corr<-append(corr,as.numeric(ssl_accuracy[i,]$ans==ssl_accuracy[i,]$key))}
ssl_accuracy$corr <- corr
subj_corr <- NULL
for (id in acc_id) {subj_corr <- append(subj_corr,round(sum(ssl_accuracy$corr[ssl_accuracy$subj==id])/32,digits=3))}
ssl_acc_table <- data.frame(acc_id,subj_corr,ssl_cond)

wj3$ID<-gsub("_wj3.csv","",wj3$ID)
for(id in wj3$ID){ subj_table$wj3_score[which(subj_table$list_ssl_id==id)]<-wj3$total[wj3$ID==id]}



for(id in scf$ID){ ssl_acc_table$gender[which(ssl_acc_table$acc_id==id)]<-paste(scf$Gender[scf$ID==id])}
for(id in wj3$ID){ ssl_acc_table$wj3_score[which(ssl_acc_table$acc_id==id)]<-wj3$total[wj3$ID==id]}
 for(id in scf$ID){ ssl_acc_table$age[which(ssl_acc_table$acc_id==id)]<-paste(scf$age[scf$ID==id])}
 for(id in scf$ID){ ssl_acc_table$hand[which(ssl_acc_table$acc_id==id)]<-paste(scf$Hand[scf$ID==id])}

 for(id in scf$ID){ ssl_acc_table$Language[which(ssl_acc_table$acc_id==id)]<-paste(scf$Language[scf$ID==id])}
ssl_acc_table$Language <- as.numeric(ssl_acc_table$Language)
ssl_acc_table$age <- as.numeric(ssl_acc_table$age)

```

### Cronbach's alpha score 
```{r,echo=FALSE,warning=FALSE}

ssl_acc1 <- ssl_accuracy[ssl_accuracy$cond=="lang1",]
d1 <- matrix(nrow=62,ncol=32)
for(i in seq(from=1,to=62,by=1)){d1[i,] <- rbind(ssl_acc1$corr[((i-1)*32+1):(i*32)])}
a1<-psych::alpha(d1,check.keys = TRUE)$total$std.alpha

ssl_acc2 <- ssl_accuracy[ssl_accuracy$cond=="lang2",]
d2 <- matrix(nrow=76,ncol=32)
for(i in seq(from=1,to=76,by=1)){d2[i,] <- rbind(ssl_acc2$corr[((i-1)*32+1):(i*32)])}
a2<-psych::alpha(d2,check.keys = TRUE)$total$std.alpha
a<- c(a1,a2)
mean(a)
```


#Testing SL ability through the task:
###Looking at RT 

```{r,echo=FALSE,warning=FALSE}
t.test(subj_table$rt_slope,mu=0,alternative="less")

#mean time by trial
ggplot(mean_table,aes(y=rt_col,x=reindex))+geom_point(color='deepskyblue3') + geom_smooth(method='lm') + labs(x="Trial Index", y="Response time (ms)",title="Resposne time by trial index in ssl")
```


###Looking at Accuracy: the mean accuracy of this task is above chance (50%)
```{r,echo=FALSE}
t.test(ssl_acc_table$subj_corr,mu=0.5,alternative="greater")
```


#Relationship between SL and other factors

##RT and other factors
```{r,echo=FALSE,warning=FALSE,include=FALSE}

#RT by WJ4 score
ggplot(subj_table[subj_table$wj3_score>25,],aes(y=mean_rt,x=wj3_score))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="WJ4 Score", y="Response time (ms)",title="Resposne time by WJ4 score in ssl") + ylim(c(100,700))
#RT Slope by WJ4
ggplot(subj_table[subj_table$wj3_score>25,],aes(y=rt_slope,x=wj3_score))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="WJ4 Score", y="Response time slope",title="Resposne time slope by WJ4 score in SSL")  + ylim(c(-15,15))

#Mean rt vs WJ4 score by gender
qplot(wj3_score,mean_rt,data=subset1[subset1$wj3_score>25,],facets=(. ~ gender),color= gender, main="ssl RT vs WJ4 score by gender", ylab="Response time", xlab="WJ4 score", ylim=c(100,600)) + geom_smooth(method='lm') + scale_color_discrete(name="Gender") 

#RT slope  vs WJ4 score by gender
qplot(wj3_score,rt_slope,data=subset1[subset1$wj3_score>25,],facets=(. ~ gender),color= gender, main="ssl RT slope vs WJ4 scpre by gender", ylab="RT Slope", xlab="WJ4 score", ylim=c(-15,15)) + geom_smooth(method='lm') + scale_color_discrete(name="Gender")


#Mean rt vs WJ4 score by Handedness
qplot(wj3_score,mean_rt,data=subj_table[subj_table$wj3_score>25,],facets=(. ~ handedness),color= handedness, main="ssl RT by Handedness", ylab="Response time", xlab="Trial index", ylim=c(100,600)) + geom_smooth(method='lm') + scale_color_discrete(name="Handedness")
#RT Slope vs WJ4 score by Handedness
qplot(wj3_score,rt_slope,data=subj_table[subj_table$wj3_score>25,],facets=(. ~ handedness),color= handedness, main="ssl RT slope by Handedness", ylab="Response time", xlab="Trial index", ylim=c(-15,15)) + geom_smooth(method='lm') + scale_color_discrete(name="Handedness")



#RT by Language
ggplot(subset2,aes(y=mean_rt,x=Language))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="WJ4 Score", y="Response time (ms)",title="Resposne time by Language score in ssl") + ylim(c(100,700))
#RT Slope by Language
ggplot(subset2,aes(y=rt_slope,x=Language))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="WJ4 Score", y="Response time (ms)",title="Resposne time slope by Language score in ssl") + ylim(c(-15,15))
```


## A simple correlation test between WJ4 score and RT Slope, controlling for age
```{r,echo=FALSE}

#correlation test between rt slope and wj4 score
pcor.test(subj_table$rt_slope, subj_table$wj3_score,subj_table$age,method="spearman")
```

## A simple correlation test between WJ4 score and Accuracy, controlling for age
```{r,echo=FALSE}

#correlation test between rt slope and wj4 score
pcor.test(ssl_acc_table$subj_corr,ssl_acc_table$wj3_score,ssl_acc_table$age,method="spearman")
```

##RT slope and other factors
```{r,echo=FALSE}
a<-lm(formula = subj_corr ~ wj3_score * age + as.factor(hand) + as.factor(gender), data = ssl_acc_table)
summary(a)
```
##Accuracy and other factors
```{r,echo=FALSE}
a1<-lm(formula = rt_slope ~ wj3_score * age + as.factor(handedness) + as.factor(gender), data = subj_table)
summary(a1)
```