---
title: "ssl_analysis"
author: "An Nguyen"
date: "November 9, 2017"
output: html_document
header-includes:
  - \usepackage{color}
---

\definecolor{coolblack}{rgb}{0.0, 0.18, 0.39}
\definecolor{violet}{rgb}{0.19, 0.55, 0.91}
```{r,echo=FALSE,warning=FALSE}
#Loading library
library(ggplot2)
library(ppcor)
library(knitr)
library(nortest)
library(readr)
```


```{r,echo=FALSE}
#importing files
total_ssl_trial <- 48
language_1 = list(1,2,2,2,1,1,2,1,1,2,1,2,1,1,2,2,1,1,2,1,2,2,1,2,2,2,1,2,1,2,1,1)
language_2 = list(1,1,2,1,1,1,2,2,2,2,1,1,1,2,2,1,2,2,1,1,2,1,2,1,2,1,2,1,1,2,2,2)

ssl <- read.csv("C:/Users/Qlab/Downloads/mturk_data/ssl.csv")
wj3 <- read.csv("C:/Users/Qlab/Downloads/mturk_data/wj3_score.csv")
scf <-  read.csv("C:/Users/Qlab/Downloads/mturk_data/scf.csv")
#Clean data


ssl$stimulus<- gsub(".wav","",ssl$stimulus)
ssl$stimulus<- gsub("sound/","",ssl$stimulus)

#exclusion for people who only have 0-1 correct hit
ssl <- ssl[which(ssl$par_id!="A1KAIOBTXQ77A6" & ssl$par_id != "mtslAG1213" & ssl$par_id!="A3UVW94KB9UBAJ" & ssl$par_id!="mtslaa0292"),]
```


```{r,echo=FALSE}
#analysis on RT

fam_block <- ssl[which(ssl$trial_index<=586 & ssl$trial_index>=11),]
fam_block <- fam_block[!(fam_block$stimulus=="ssl_instr7"),]
fam_block <- fam_block[!(fam_block$stimulus=="ssl_instr8"),]
fam_block$targ <- paste(fam_block$targ)
fam_block$stimulus <- paste(fam_block$stimulus)
fam_block$rt <- as.numeric(paste(fam_block$rt))

rt_col <- NULL
id <- NULL
trial <- NULL
target <- NULL
row_number <- which(fam_block$targ==fam_block$stimulus)
for (i in row_number){
    rt_col <- append(rt_col,fam_block[i,][,"rt"]) 
    trial <- append(trial,paste(fam_block[i,][,"trial_index"]))
    id <- append(id,paste(fam_block[i,]$par_id))
    if (fam_block[i+1,][,"rt"]!=-1000){
        rt_col[(match(i,row_number))] <- 480+fam_block[i+1,][,"rt"]}
    
    if (fam_block[i-1,][,"rt"]>0){
        rt_col[(match(i,row_number))] <- -(480-fam_block[i-1,][,"rt"])
    if (fam_block[i-1,][,"rt"]<0){
        rt_col[(match(i,row_number))] <- -(480+fam_block[i-1,][,"rt"])   
    }}
fam_trial <- data.frame(trial,rt_col,id)

a<-NULL
for (i in (unique(fam_trial$id))){a<- append(a,sum(fam_trial$id==i))}
reindex <- NULL
for (i in a) {reindex <- append(reindex,rep(1:i,1))}     
fam_trial$reindex <- reindex
hit_rate <- NULL
miss_rate <- NULL
correct_rejection <- NULL
false_alarm <- NULL
mean_rt <- NULL
rt_slope <- NULL

mean_table <- fam_trial[which(fam_trial$rt_col!=-1000 & fam_trial$rt_col<960 & fam_trial$rt_col>-480), ] #only accept answers in range of -1000 < x < 1000
list_ssl_id <- unique(mean_table$id)
for(id in list_ssl_id){
  mean_rt<-append(mean_rt,round(mean(mean_table$rt_col[mean_table$id==id]),digits=3))
 rt_slope <-append(rt_slope,round(summary(lm(mean_table$rt_col[mean_table$id==id]~mean_table$reindex[mean_table$id==id]))$coefficient[2,1],digits=3))
  hit_rate<-append(hit_rate,round(sum(!is.na(mean_table$rt_col[mean_table$id==id]))/sum(fam_trial$id==id),digits =2))
  miss_rate<-append(miss_rate,round(sum(fam_trial$rt_col[fam_trial$id==id]==-1000)/sum(fam_trial$id==id),digits=2))
  correct_rejection <- append(correct_rejection, round(sum(fam_block$rt[fam_block$par_id==id]==-1000 & fam_block$targ[fam_block$par_id==id]!=fam_block$stimulus[fam_block$par_id==id])/528,digits=2)) #528 is the total number of stimuli in the familiarization block
  false_alarm <- append(false_alarm, round(sum(fam_block$rt[fam_block$par_id==id]!=-1000 & fam_block$targ[fam_block$par_id==id]!=fam_block$stimulus[fam_block$par_id==id])/528,digits=2))
}

subj_table <- data.frame(list_ssl_id,mean_rt, rt_slope,hit_rate, miss_rate,correct_rejection,false_alarm)
dprime<-NULL
for (i in seq(from=1,to=length(subj_table$list_ssl_id),by=1)){dprime<-append(dprime,qnorm(subj_table[i,]$hit_rate-0.00000001)-qnorm(subj_table[i,]$false_alarm+0.000000001))} #minus 0.000000001 to avoid perfect hit rate
subj_table$dprime <- round(dprime,3)
```

```{r, echo=FALSE}
#test block
test_block <- ssl[which(ssl$trial_index<=814 & ssl$trial_index>=590),]
test_block <- test_block[!(test_block$stimulus==""),]
test_block <- test_block[!(test_block$stimulus=="silence" & test_block$key_press==-1),]

ans <- NULL
keyv <- NULL
subj <- NULL
cond<- NULL

 row_number <- which(test_block$key_press != -1 & test_block$stimulus=="silence")
  for (i in row_number){
    ans<-append(ans,test_block[i,]$key_press)
    subj <- append(subj,paste(test_block[i,]$par_id))
    cond <- append(cond,paste(test_block[i,]$cond))
  }
  
ssl_accuracy <- data.frame(ans,subj,cond)
ssl_cond <- NULL
for (i in seq(from=1,to=length(ssl_accuracy$cond),by=32)){ssl_cond<-append(ssl_cond,as.character(ssl_accuracy[i,]$cond))}

key<- NULL


for(cond in ssl_cond){
    if (cond=="lang1"){key<-append(key,language_1)}
    else if (cond=="lang2"){key<-append(key,language_2)}}



acc_id <- unique(ssl_accuracy$subj)

ssl_accuracy$key <- key

ssl_accuracy$ans <- gsub(37,1,ssl_accuracy$ans)
ssl_accuracy$ans <- gsub(39,2,ssl_accuracy$ans)

corr <- NULL
for (i in seq(from=1,to=length(ssl_accuracy$ans),by=1)) {corr<-append(corr,as.numeric(ssl_accuracy[i,]$ans==ssl_accuracy[i,]$key))}
ssl_accuracy$corr <- corr
subj_corr <- NULL
for (id in acc_id) {subj_corr <- append(subj_corr,round(sum(ssl_accuracy$corr[ssl_accuracy$subj==id])/32,digits=3))}
ssl_acc_table <- data.frame(acc_id,subj_corr,ssl_cond)

wj3$ID<-gsub("_wj3.csv","",wj3$ID)
for(id in wj3$ID){ subj_table$wj3_score[which(subj_table$list_ssl_id==id)]<-wj3$total[wj3$ID==id]}

for(id in scf$ID){ subj_table$gender[which(subj_table$list_ssl_id==id)]<-paste(scf$Gender[scf$ID==id])}
for(id in scf$ID){ subj_table$handedness[which(subj_table$list_ssl_id==id)]<-paste(scf$Hand[scf$ID==id])}
for(id in scf$ID){ subj_table$age[which(subj_table$list_ssl_id==id)]<-paste(scf$age[scf$ID==id])}
subj_table$age <- as.numeric(subj_table$age)

subset1 <- subj_table[subj_table$gender!="Other",]

 for(id in scf$ID){ subj_table$Language[which(subj_table$list_ssl_id==id)]<-paste(scf$Language[scf$ID==id])}
subj_table$Language <- as.numeric(subj_table$Language)

subset2<- subj_table[subj_table$Language>=20,]


for(id in scf$ID){ ssl_acc_table$gender[which(ssl_acc_table$acc_id==id)]<-paste(scf$Gender[scf$ID==id])}
for(id in wj3$ID){ ssl_acc_table$wj3_score[which(ssl_acc_table$acc_id==id)]<-wj3$total[wj3$ID==id]}

 for(id in scf$ID){ ssl_acc_table$Language[which(ssl_acc_table$acc_id==id)]<-paste(scf$Language[scf$ID==id])}
for(id in scf$ID){ ssl_acc_table$age[which(ssl_acc_table$acc_id==id)]<-paste(scf$age[scf$ID==id])}
ssl_acc_table$age <- as.numeric(ssl_acc_table$age)
for(id in scf$ID){ ssl_acc_table$handedness[which(ssl_acc_table$acc_id==id)]<-paste(scf$Hand[scf$ID==id])}

ssl_acc_table$Language <- as.numeric(ssl_acc_table$Language)
```

### Cronbach's alpha score for the consistency of the SSL Accuracy task is 0.6. This is a lower score which may imply that the questions of this task are not good enough. 
```{r,echo=FALSE,warning=FALSE}

d <- matrix(nrow=(length(ssl_accuracy$ans)/32),ncol=32)
for(i in seq(from=1,to=(length(ssl_accuracy$ans)/32),by=1)){d[i,] <- rbind(ssl_accuracy$corr[((i-1)*32+1):(i*32)])}
psych::alpha(d,check.keys = TRUE)$total$std.alpha
```

##Check some variables for normality
```{r,echo=FALSE}
par(mfrow=c(2,2))
qqnorm(subj_table$wj3_score,main="WJ4 Score");qqline(subj_table$wj3_score, col = 2)
qqnorm(subj_table$rt_slope, main="RT Slope");qqline(subj_table$rt_slope, col = 2)
qqnorm(subj_table$age,main="Age");qqline(subj_table$age, col = 2)
qqnorm(ssl_acc_table$subj_corr,main="Accuracy");qqline(ssl_acc_table$subj_corr, col = 2)
ad.test(subj_table$wj3_score)
ad.test(subj_table$rt_slope)
ad.test(subj_table$age)
ad.test(ssl_acc_table$subj_corr)
```


#Testing SL ability through the task:
###Looking at RT 

```{r,echo=FALSE,warning=FALSE}

#mean time by trial
ggplot(mean_table,aes(y=rt_col,x=reindex))+geom_point(color='deepskyblue3') + geom_smooth(method='lm') + labs(x="Trial Index", y="Response time (ms)",title="Resposne time by trial index in ssl")
```

###Whether trial index is related to response time
```{r,echo=FALSE}
m1 = aov(rt_col~reindex+Error(id/reindex),data=mean_table)
summary(m1)
```

###Looking at Accuracy: the mean accuracy of this task is above chance (50%)
```{r,echo=FALSE}
t.test(ssl_acc_table$subj_corr,mu=0.5,alternative="greater")
```


#Relationship between SL and other factors

```{r,echo=FALSE}
summary(lm(rt_slope~ wj3_score * age + as.factor(handedness) + as.factor(gender),data=subj_table))

summary(lm(subj_corr ~ wj3_score * age + as.factor(handedness) + as.factor(gender) ,data=ssl_acc_table))
```


##RT slope and other factors
```{r,echo=FALSE,warning=FALSE}

#RT by WJ4 score
#ggplot(subj_table[subj_table$wj3_score>25,],aes(y=mean_rt,x=wj3_score))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="WJ4 Score", y="Response time (ms)",title="Resposne time by WJ4 score in ssl") + ylim(c(100,700))

#RT Slope by WJ4
ggplot(subj_table[subj_table$wj3_score>25,],aes(y=rt_slope,x=wj3_score))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="WJ4 Score", y="Response time slope",title="Resposne time slope by WJ4 score in SSL")  + ylim(c(-15,15))

#Mean rt vs WJ4 score by gender
#qplot(wj3_score,mean_rt,data=subset1[subset1$wj3_score>25,],facets=(. ~ gender),color= gender, main="ssl RT vs WJ4 score by gender", ylab="Response time", xlab="WJ4 score", ylim=c(100,600)) + geom_smooth(method='lm') + scale_color_discrete(name="Gender") 

#RT slope  vs WJ4 score by gender
qplot(wj3_score,rt_slope,data=subset1[subset1$wj3_score>25,],facets=(. ~ gender),color= gender, main="ssl RT slope vs WJ4 scpre by gender", ylab="RT Slope", xlab="WJ4 score", ylim=c(-15,15)) + geom_smooth(method='lm') + scale_color_discrete(name="Gender")


#Mean rt vs WJ4 score by Handedness
#qplot(wj3_score,mean_rt,data=subj_table[subj_table$wj3_score>25,],facets=(. ~ handedness),color= handedness, main="ssl RT by Handedness", ylab="Response time", xlab="Trial index", ylim=c(100,600)) + geom_smooth(method='lm') + scale_color_discrete(name="Handedness")

#RT Slope vs WJ4 score by Handedness
qplot(wj3_score,rt_slope,data=subj_table[subj_table$wj3_score>25,],facets=(. ~ handedness),color= handedness, main="ssl RT slope by Handedness", ylab="Response time", xlab="Trial index", ylim=c(-15,15)) + geom_smooth(method='lm') + scale_color_discrete(name="Handedness")



#RT by Language
#ggplot(subset2,aes(y=mean_rt,x=Language))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="WJ4 Score", y="Response time (ms)",title="Resposne time by Language score in ssl") + ylim(c(100,700))

#RT Slope by Language
ggplot(subset2[subset2$Language<=50,],aes(y=rt_slope,x=Language))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="Language Experience Score", y="Response time (ms)",title="RT slope by Language score in ssl") + ylim(c(-15,15))
```


## A partial correlation test between WJ4 score and RT Slope, controlling for age
```{r,echo=FALSE}

#correlation test between rt slope and wj4 score
pcor.test(subj_table$wj3_score, subj_table$rt_slope, subj_table$age, method="spearman")
```


##Accuracy and other factors
```{r,echo=FALSE}

ggplot(ssl_acc_table[ssl_acc_table$wj3_score>25,],aes(y=subj_corr,x=wj3_score))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="WJ4 Score", y="Accuracy",title="Accuracy by WJ4 score in ssl") 
ggplot(ssl_acc_table[ssl_acc_table$Language>=20,],aes(y=subj_corr,x=Language))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="Language", y="Accuracy",title="Accuracy by Language in ssl") 


```



## A partial correlation test between WJ4 score and Accuracy, controlling for age
```{r,echo=FALSE}

#correlation test between rt slope and wj4 score
pcor.test(subj_table$wj3_score, ssl_acc_table$subj_corr, subj_table$age, method="spearman")
```


#Appendix
##Table 1
```{r,echo=FALSE}
table_output <- subj_table[,c("list_ssl_id","mean_rt","rt_slope","dprime")]
a <- seq(1,134,1)
new_id <- sprintf("mtsl_%03d", a)
table_output$list_ssl_id<-new_id
colnames(table_output) <- c("ID","Mean RT","RT Slope","D'")
kable(table_output)
```

##Table 2


```{r,echo=FALSE}
table_output2 <- ssl_acc_table[,c("acc_id","subj_corr","ssl_cond")]
a <- seq(1,134,1)
new_id <- sprintf("mtsl_%03d", a)
table_output2$acc_id<-new_id
colnames(table_output2) <- c("ID","accuracy(%)","condition")
kable(table_output2)
```
