---
title: "lsl_analylsis"
author: "An Nguyen"
date: "November 13, 2017"
output: html_document
---
```{r,echo=FALSE,warning=FALSE}
#Loading library
library(ggplot2)
library(knitr)
library(readr)
library(psych)
```


```{r,echo=FALSE,warning=FALSE}

wj3 <- read.csv("C:/Users/Qlab/Downloads/mturk_data/wj3_score.csv")
scf <-  read.csv("C:/Users/Qlab/Downloads/mturk_data/scf.csv")

language_1 = list(1,2,2,2,1,1,2,1,1,2,1,2,1,1,2,2,1,1,2,1,2,2,1,2,2,2,1,2,1,2,1,1)
language_2 = list(1,1,2,1,1,1,2,2,2,2,1,1,1,2,2,1,2,2,1,1,2,1,2,1,2,1,2,1,1,2,2,2)

path <- "C:/Users/Qlab/Downloads/mt/lsl/"
files <- list.files(path=path, pattern="*.csv") 
for(file in files)
{
   
    assign(
        gsub(" ","",file), 
        read.csv(paste(path,file,sep="")))
}
lsl <- list()

for(file in files){lsl <- append(lsl,list(eval(parse(text=file))))}
lsl <- do.call(rbind.data.frame, lsl)

lsl$rt <- lsl$col1-lsl$time

lsl$stim_disp<- gsub(".png","",lsl$stim_disp)
lsl$stim_disp<- gsub("image/","",lsl$stim_disp)


lsl$col2<- gsub(".png","",lsl$col2)
lsl$col2<- gsub("image/","",lsl$col2)

row_number <- which(lsl$target==lsl$stim_disp)

rt_col <- NULL
id <- NULL
trial <- NULL
for (i in row_number){
        rt_col <- append(rt_col,lsl[i,][,"rt"])
        trial <- append(trial,lsl[i,][,"X"])
        id <- append(id,paste(lsl[i,]$par_id))
    if (!is.na(lsl[i+1,][,"rt"])){
        rt_col[(match(i,row_number))] <- (480+lsl[i+1,][,"rt"])
        
    }
    if (!is.na(lsl[i-1,][,"rt"])){
        rt_col[(match(i,row_number))] <- (0-lsl[i+1,][,"rt"])
        
    }}
fam_trial <- data.frame(trial,rt_col,id)

reindex <- rep(1:24,length(fam_trial$trial)/24)
fam_trial$reindex <- reindex
hit_rate <- NULL
miss_rate <- NULL
correct_rejection <- NULL
false_alarm <- NULL
mean_rt <- NULL
rt_slope <- NULL

mean_table <- fam_trial[which(fam_trial$rt_col!=-1 & fam_trial$rt_col<1000 & fam_trial$rt_col>-1000), ] #only accept answers in range of -1000 < x < 1000
list_lsl_id <- unique(mean_table$id)

for(id in list_lsl_id){
  mean_rt<-append(mean_rt,round(mean(mean_table$rt_col[mean_table$id==id]),digits=3))
  if(id=="A3SD02HCW68EUL" | id == "mtslAG1213" | id == "mturk"){rt_slope <- append(rt_slope,0)
  } else {
    rt_slope <-append(rt_slope,round(summary(lm(mean_table$rt_col[mean_table$id==id]~mean_table$reindex[mean_table$id==id]))$coefficient[2,1],digits=3))}
  
  hit_rate<-append(hit_rate,round(sum(!is.na(mean_table$rt_col[mean_table$id==id]))/24,digits =2))
 
   miss_rate<-append(miss_rate,round(sum(is.na(fam_trial$rt_col[fam_trial$id==id]))/24,digits =2))
 
  correct_rejection <- append(correct_rejection,  round(sum(is.na(lsl$rt[lsl$par_id==id]) & lsl$target[lsl$par_id==id]!=lsl$stim_disp[lsl$par_id==id])/552,digits=2) )  #552 is the total number of stimuli in the familiarization block
  false_alarm <- append(false_alarm, round(sum(!is.na(lsl$rt[lsl$par_id==id]) & lsl$target[lsl$par_id==id]!=lsl$stim_disp[lsl$par_id==id])/552,digits=2) ) 
}
subj_table <- data.frame(list_lsl_id,mean_rt, rt_slope,hit_rate, miss_rate,correct_rejection,false_alarm)

dprime<-NULL
for (i in seq(from=1,to=length(subj_table$list_lsl_id),by=1)){dprime<-append(dprime,qnorm(subj_table[i,]$hit_rate-0.00000001)-qnorm(subj_table[i,]$false_alarm+0.000000001))} #minus 0.000000001 to avoid perfect hit rate
subj_table$dprime <- round(dprime,3)


wj3$ID<-gsub("_wj3.csv","",wj3$ID)
for(id in wj3$ID){ subj_table$wj3_score[which(subj_table$list_lsl_id==id)]<-wj3$total[wj3$ID==id]}

for(id in scf$ID){ subj_table$gender[which(subj_table$list_lsl_id==id)]<-paste(scf$Gender[scf$ID==id])}
for(id in scf$ID){ subj_table$handedness[which(subj_table$list_lsl_id==id)]<-paste(scf$Hand[scf$ID==id])}
for(id in scf$ID){ subj_table$Language[which(subj_table$list_lsl_id==id)]<-paste(scf$Language[scf$ID==id])}
subj_table$Language <- as.numeric(subj_table$Language)

subset2<- subj_table[subj_table$Language>=20,]
subset1 <- subj_table[subj_table$gender!="Other",]


```





```{r,echo=FALSE,warning=FALSE}
lslacc <- list()
path <- "C:/Users/Qlab/Downloads/mt/lsl/copy/"
files <- list.files(path=path, pattern="*.csv") 
for(file in files)
{
   
    assign(
        gsub(" ","",file), 
        read.csv(paste(path,file,sep="")))
}
for(file in files){lslacc <- append(lslacc,list(eval(parse(text=file))))}
lslacc <- do.call(rbind.data.frame, lslacc)

test_block <- lslacc[which(lslacc$trial_index<=242 & lslacc$trial_index>=16),]
test_block <- test_block[!(test_block$stimulus==""),]
test_block <- test_block[!(test_block$stimulus=="image/white.png" & test_block$key_press==-1),]

ans <- NULL
keyv <- NULL
subj <- NULL
cond<- NULL

 row_numberv <- which(test_block$key_press != -1 & test_block$stimulus=="image/white.png")
  for (i in row_numberv){
    ans<-append(ans,test_block[i,]$key_press)
    subj <- append(subj,paste(test_block[i,]$par_id))
    cond <- append(cond,paste(test_block[i,]$cond))
  }
  
lsl_accuracy <- data.frame(ans,subj,cond)
lsl_cond <- NULL
for (i in seq(from=1,to=length(lsl_accuracy$cond),by=32)){lsl_cond<-append(lsl_cond,as.character(lsl_accuracy[i,]$cond))}

keyv<- NULL


for(cond in lsl_cond){
    if (cond=="lang1"){keyv<-append(keyv,language_1)}
    else if (cond=="lang2"){keyv<-append(keyv,language_2)}}



acc_id <- unique(lsl_accuracy$subj)

lsl_accuracy$key <- keyv

lsl_accuracy$ans <- gsub(50,2,lsl_accuracy$ans)
lsl_accuracy$ans <- gsub(49,1,lsl_accuracy$ans)

corr <- NULL
for (i in seq(from=1,to=length(lsl_accuracy$ans),by=1)) {corr<-append(corr,as.numeric(lsl_accuracy[i,]$ans==lsl_accuracy[i,]$key))}
lsl_accuracy$corr <- corr
subj_corr <- NULL
for (id in acc_id) {subj_corr <- append(subj_corr,round(sum(lsl_accuracy$corr[lsl_accuracy$subj==id])/32,digits=3))}
lsl_acc_table <- data.frame(acc_id,subj_corr,lsl_cond)


for(id in scf$ID){ lsl_acc_table$gender[which(lsl_acc_table$acc_id==id)]<-paste(scf$Gender[scf$ID==id])}

for(id in scf$ID){ lsl_acc_table$gender[which(lsl_acc_table$acc_id==id)]<-paste(scf$Gender[scf$ID==id])}
for(id in wj3$ID){ lsl_acc_table$wj3_score[which(lsl_acc_table$acc_id==id)]<-wj3$total[wj3$ID==id]}

 for(id in scf$ID){ lsl_acc_table$Language[which(lsl_acc_table$acc_id==id)]<-paste(scf$Language[scf$ID==id])}
lsl_acc_table$Language <- as.numeric(lsl_acc_table$Language)

```

### Cronbach's alpha score for the consistency of the lsl Accuracy task is 0.72. The consistency of the questions in this task is fair.
```{r,echo=FALSE,warning=FALSE}

d <- matrix(nrow=144,ncol=32)
for(i in seq(from=1,to=144,by=1)){d[i,] <- rbind(lsl_accuracy$corr[((i-1)*32+1):(i*32)])}
psych::alpha(d,check.keys = TRUE)$total$std.alpha
```


#Testing SL ability through the task:
###Looking at RT 

```{r,echo=FALSE,warning=FALSE}

ggplot(mean_table,aes(y=rt_col,x=reindex))+geom_point(color='deepskyblue3') + geom_smooth(method='lm') + labs(x="Trial Index", y="Response time (ms)",title="Resposne time by trial index in lsl")

```


###Whether trial index is related to response time
```{r,echo=FALSE}
m1 = aov(rt_col~reindex+Error(id/reindex),data=mean_table)
summary(m1)
```


###Looking at Accuracy: the mean accuracy of this task is above chance (50%)
```{r,echo=FALSE}
t.test(lsl_acc_table$subj_corr,mu=0.5,alternative="greater")
```

#Relationship between SL and other factors

##RT and other factors
```{r,echo=FALSE,warning=FALSE}
#RT by WJ4 score
ggplot(subj_table[subj_table$wj3_score>25,],aes(y=mean_rt,x=wj3_score))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="WJ4 Score", y="Response time (ms)",title="Resposne time by WJ4 score in lsl") + ylim(c(100,700))

#RT Slope by WJ4
ggplot(subj_table[subj_table$wj3_score>25,],aes(y=rt_slope,x=wj3_score))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="WJ4 Score", y="Response time slope",title="Resposne time slope by WJ4 score in lsl")  + ylim(c(-15,15))

#RT slope  vs WJ4 score by gender
qplot(wj3_score,rt_slope,data=subset1[subset1$wj3_score>25,],facets=(. ~ gender),color= gender, main="lsl RT slope vs WJ4 scpre by gender", ylab="RT Slope", xlab="WJ4 score", ylim=c(-15,15)) + geom_smooth(method='lm') + scale_color_discrete(name="Gender")


#Mean rt vs WJ4 score by Handedness
qplot(wj3_score,mean_rt,data=subj_table[subj_table$wj3_score>25,],facets=(. ~ handedness),color= handedness, main="lsl RT by Handedness", ylab="Response time", xlab="WJ4 Score", ylim=c(100,600)) + geom_smooth(method='lm') + scale_color_discrete(name="Handedness")
#RT Slope vs WJ4 score by Handedness
qplot(wj3_score,rt_slope,data=subj_table[subj_table$wj3_score>25,],facets=(. ~ handedness),color= handedness, main="lsl RT slope vs WJ4 score by Handedness", ylab="Response time slope", xlab="WJ4 Score", ylim=c(-15,15)) + geom_smooth(method='lm') + scale_color_discrete(name="Handedness")



#RT by Language
ggplot(subset2,aes(y=mean_rt,x=Language))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="WJ4 Score", y="Response time (ms)",title="Resposne time by Language score in lsl") + ylim(c(100,700))
#RT Slope by Language
ggplot(subset2,aes(y=rt_slope,x=Language))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="WJ4 Score", y="Response time (ms)",title="Resposne time slope by Language score in lsl") + ylim(c(-15,15))

```



## A simple correlation test between WJ4 score and RT Slope
```{r,echo=FALSE}

#correlation test between rt slope and wj4 score
cor.test(subj_table[subj_table$wj3_score>25,]$rt_slope,subj_table[subj_table$wj3_score>25,]$wj3_score)
```


##Accuracy and other factors
```{r,echo=FALSE}

ggplot(lsl_acc_table[lsl_acc_table$wj3_score>25,],aes(y=subj_corr,x=wj3_score))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="WJ4 Score", y="Accuracy",title="Accuracy by WJ4 score in lsl") 
ggplot(lsl_acc_table[lsl_acc_table$Language>=20,],aes(y=subj_corr,x=Language))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="Language", y="Accuracy",title="Accuracy by Language in lsl") 


for(id in scf$ID){ lsl_acc_table$gender[which(lsl_acc_table$acc_id==id)]<-paste(scf$Gender[scf$ID==id])}
t.test(lsl_acc_table$subj_corr[lsl_acc_table$gender=="Female"],lsl_acc_table$subj_corr[lsl_acc_table$gender=="Male"])


```


#Appendix
##Table 1
```{r,echo=FALSE}
table_output <- subj_table[,c("list_lsl_id","mean_rt","rt_slope","dprime")]
a <- seq(1,119,1)
new_id <- sprintf("mtsl_%03d", a)
table_output$list_lsl_id<-new_id
colnames(table_output) <- c("ID","Mean RT","RT Slope","D'")
kable(table_output)
```

##Table 2


```{r,echo=FALSE}
table_output2 <- lsl_acc_table[,c("acc_id","subj_corr","lsl_cond")]
a <- seq(1,144,1)
new_id <- sprintf("mtsl_%03d", a)
table_output2$acc_id<-new_id
colnames(table_output2) <- c("ID","accuracy(%)","condition")
kable(table_output2)
```

