---
title: "vsl_analysis"
author: "An Nguyen"
date: "November 9, 2017"
output: html_document
header-includes:
  - \usepackage{color}
---
\definecolor{coolblack}{rgb}{0.0, 0.18, 0.39}
\definecolor{violet}{rgb}{0.19, 0.55, 0.91}
```{r,echo=FALSE,warning=FALSE}
#Loading library
library(ggplot2)
library(knitr)
library(readr)
library(psych)
library(ppcor)
library(nortest)
```


```{r,echo=FALSE}
#importing files
total_vsl_trial <- 24
language_1 = list(1,2,2,2,1,1,2,1,1,2,1,2,1,1,2,2,1,1,2,1,2,2,1,2,2,2,1,2,1,2,1,1)
language_2 = list(1,1,2,1,1,1,2,2,2,2,1,1,1,2,2,1,2,2,1,1,2,1,2,1,2,1,2,1,1,2,2,2)

vsl <- read.csv("C:/Users/Qlab/Downloads/mturk_data/vsl.csv")
wj3 <- read.csv("C:/Users/Qlab/Downloads/mturk_data/wj3_score.csv")
scf <-  read.csv("C:/Users/Qlab/Downloads/mturk_data/scf.csv")
#Clean data

vsl$stimulus<- gsub(".jpg","",vsl$stimulus)
vsl$stimulus<- gsub("../../images/","",vsl$stimulus)
vsl <- vsl[which(vsl$par_id != "mtslAG1213" & vsl$par_id!="A1FDP7EMSL9T9F" & vsl$par_id!="A3LMI7ZDFO8JHR" & vsl$par_id!="A3UVW94KB9UBAJ"),]

```


```{r,echo=FALSE}
#analysis on RT

fam_block <- vsl[which(vsl$trial_index<=300 & vsl$trial_index>=12),]
fam_block <- fam_block[!(fam_block$stimulus=="../../vsl_audio/vsl_instr_between.wav"),]
fam_block <- fam_block[!(fam_block$stimulus=="../../vsl_audio/sound_instruct/vsl_instr7.wav"),]

fam_block$targ <- paste(fam_block$targ)
fam_block$stimulus <- paste(fam_block$stimulus)

rt_col <- NULL
id <- NULL
trial <- NULL
target <- NULL
row_number <- which(fam_block$targ==fam_block$stimulus)
for (i in row_number){
        rt_col <- append(rt_col,fam_block[i,][,"rt"])
        trial <- append(trial,fam_block[i,][,"trial_index"])
        id <- append(id,paste(fam_block[i,]$par_id))
    if (fam_block[i-1,][,"rt"]!=-1){
        rt_col[(match(i,row_number))] <- (0-fam_block[i-1,][,"rt"])
        
    }}
fam_trial <- data.frame(trial,rt_col,id)
reindex <- rep(1:total_vsl_trial,length(fam_trial$trial)/24)
fam_trial$reindex <- reindex
hit_rate <- NULL
miss_rate <- NULL
correct_rejection <- NULL
false_alarm <- NULL
mean_rt <- NULL
rt_slope <- NULL
timeline <- c(rep("first half",total_vsl_trial/2),rep("second half",total_vsl_trial/2))
timeline <- rep(timeline,length(fam_trial$trial)/24)
fam_trial$timeline <- timeline
mean_table <- fam_trial[which(fam_trial$rt_col!=-1 & fam_trial$rt_col<1000 & fam_trial$rt_col>-1000), ] #only accept answers in range of -1000 < x < 1000
list_vsl_id <- unique(mean_table$id)
for(id in list_vsl_id){
  mean_rt<-append(mean_rt,round(mean(mean_table$rt_col[mean_table$id==id]),digits=3))
  rt_slope <-append(rt_slope,round(summary(lm(mean_table$rt_col[mean_table$id==id]~mean_table$reindex[mean_table$id==id]))$coefficient[2,1],digits=3))
  hit_rate<-append(hit_rate,round(sum(!is.na(mean_table$rt_col[mean_table$id==id]))/total_vsl_trial,digits =2))
  miss_rate<-append(miss_rate,round(sum(fam_trial$rt_col[fam_trial$id==id]==-1)/total_vsl_trial,digits=2))
  correct_rejection <- append(correct_rejection, round(sum(fam_block$rt[fam_block$par_id==id]==-1 & fam_block$targ[fam_block$par_id==id]!=fam_block$stimulus[fam_block$par_id==id])/264,digits=2)) #264 is the total number of stimuli in the familiarization block
  false_alarm <- append(false_alarm, round(sum(fam_block$rt[fam_block$par_id==id]!=-1 & fam_block$targ[fam_block$par_id==id]!=fam_block$stimulus[fam_block$par_id==id])/264,digits=2))
}

subj_table <- data.frame(list_vsl_id,mean_rt, rt_slope,hit_rate, miss_rate,correct_rejection,false_alarm)
dprime<-NULL
for (i in seq(from=1,to=length(subj_table$list_vsl_id),by=1)){dprime<-append(dprime,qnorm(subj_table[i,]$hit_rate-0.00000001)-qnorm(subj_table[i,]$false_alarm+0.000000001))} #minus 0.000000001 to avoid perfect hit rate
subj_table$dprime <- round(dprime,3)

```



```{r,echo=FALSE}

#test block
 test_block <- vsl[which(vsl$trial_index<=532 & vsl$trial_index>=307),]
test_block <- test_block[!(test_block$stimulus=="../../vsl_audio/sound_instruct/vsl_instr14.wav"),]
test_block <- test_block[!(test_block$stimulus=="" & test_block$key_press==-1),]

ans <- NULL
keyv <- NULL
subj <- NULL
cond<- NULL

 row_numberv <- which(test_block$key_press != -1 & test_block$stimulus=="")
  for (i in row_numberv){
    ans<-append(ans,test_block[i,]$key_press)
    subj <- append(subj,paste(test_block[i,]$par_id))
    cond <- append(cond,paste(test_block[i,]$cond))
  }
  
vsl_accuracy <- data.frame(ans,subj,cond)
vsl_accuracy <- vsl_accuracy[!(vsl_accuracy$ans==32),]
vsl_cond <- NULL
for (i in seq(from=1,to=length(vsl_accuracy$cond),by=32)){vsl_cond<-append(vsl_cond,as.character(vsl_accuracy[i,]$cond))}

keyv<- NULL


for(cond in vsl_cond){
    if (cond=="lang1"){keyv<-append(keyv,language_1)}
    else if (cond=="lang2"){keyv<-append(keyv,language_2)}}



acc_id <- unique(vsl_accuracy$subj)

vsl_accuracy$key <- keyv

vsl_accuracy$ans <- gsub(50,2,vsl_accuracy$ans)
vsl_accuracy$ans <- gsub(49,1,vsl_accuracy$ans)

corr <- NULL
for (i in seq(from=1,to=length(vsl_accuracy$ans),by=1)) {corr<-append(corr,as.numeric(vsl_accuracy[i,]$ans==vsl_accuracy[i,]$key))}
vsl_accuracy$corr <- corr
subj_corr <- NULL
for (id in acc_id) {subj_corr <- append(subj_corr,round(sum(vsl_accuracy$corr[vsl_accuracy$subj==id])/32,digits=3))}
vsl_acc_table <- data.frame(acc_id,subj_corr,vsl_cond)



wj3$ID<-gsub("_wj3.csv","",wj3$ID)
for(id in wj3$ID){ subj_table$wj3_score[which(subj_table$list_vsl_id==id)]<-wj3$total[wj3$ID==id]}

for(id in scf$ID){ subj_table$gender[which(subj_table$list_vsl_id==id)]<-paste(scf$Gender[scf$ID==id])}
for(id in scf$ID){ subj_table$handedness[which(subj_table$list_vsl_id==id)]<-paste(scf$Hand[scf$ID==id])}
for(id in scf$ID){ subj_table$Language[which(subj_table$list_vsl_id==id)]<-paste(scf$Language[scf$ID==id])}
subj_table$Language <- as.numeric(subj_table$Language)
for(id in scf$ID){ subj_table$age[which(subj_table$list_vsl_id==id)]<-paste(scf$age[scf$ID==id])}
subj_table$age <- as.numeric(subj_table$age)

subset2<- subj_table[subj_table$Language>=20,]
subset1 <- subj_table[subj_table$gender!="Other",]

for(id in scf$ID){ vsl_acc_table$gender[which(vsl_acc_table$acc_id==id)]<-paste(scf$Gender[scf$ID==id])}
for(id in wj3$ID){ vsl_acc_table$wj3_score[which(vsl_acc_table$acc_id==id)]<-wj3$total[wj3$ID==id]}

 for(id in scf$ID){ vsl_acc_table$Language[which(vsl_acc_table$acc_id==id)]<-paste(scf$Language[scf$ID==id])}
vsl_acc_table$Language <- as.numeric(vsl_acc_table$Language)

for(id in scf$ID){ vsl_acc_table$age[which(vsl_acc_table$acc_id==id)]<-paste(scf$age[scf$ID==id])}
vsl_acc_table$age <- as.numeric(vsl_acc_table$age)
for(id in scf$ID){ vsl_acc_table$handedness[which(vsl_acc_table$acc_id==id)]<-paste(scf$Hand[scf$ID==id])}

```


### Cronbach's alpha score for the consistency of the vsl Accuracy task is 0.89. The consistency of the questions in this task is good.
```{r,echo=FALSE,warning=FALSE}
d <- matrix(nrow=145,ncol=32)
for(i in seq(from=1,to=145,by=1)){d[i,] <- rbind(vsl_accuracy$corr[((i-1)*32+1):(i*32)])}
psych::alpha(d,check.keys = TRUE)$total$std.alpha
```


##Check some variables for normality
```{r,echo=FALSE}
par(mfrow=c(2,2))
qqnorm(subj_table$wj3_score,main="WJ4 Score");qqline(subj_table$wj3_score, col = 2)
qqnorm(subj_table$rt_slope, main="RT Slope");qqline(subj_table$rt_slope, col = 2)
qqnorm(subj_table$age,main="Age");qqline(subj_table$age, col = 2)
qqnorm(vsl_acc_table$subj_corr,main="Accuracy");qqline(vsl_acc_table$subj_corr, col = 2)
ad.test(subj_table$wj3_score)
ad.test(subj_table$rt_slope)
ad.test(subj_table$age)
ad.test(vsl_acc_table$subj_corr)
```


#Testing SL ability through the task:
###Looking at RT 

```{r,echo=FALSE,warning=FALSE}

ggplot(mean_table,aes(y=rt_col,x=reindex))+geom_point(color='deepskyblue3') + geom_smooth(method='lm') + labs(x="Trial Index", y="Response time (ms)",title="Resposne time by trial index in VSL")

```


###Whether trial index is related to response time
```{r,echo=FALSE}
m1 = aov(rt_col~reindex+Error(id/reindex),data=mean_table)
summary(m1)
```

###Looking at Accuracy: the mean accuracy of this task is above chance (50%)
```{r,echo=FALSE}
t.test(vsl_acc_table$subj_corr,mu=0.5,alternative="greater")
```

#Relationship between SL and other factors

##RT Slope
```{r,echo=FALSE}
summary(lm(rt_slope~ wj3_score * age + as.factor(handedness) + as.factor(gender),data=subj_table))

```
#Accuracy
```{r,echo=FALSE}
summary(lm(subj_corr ~ wj3_score * age + as.factor(handedness) + as.factor(gender) ,data=vsl_acc_table))

```

##RT slope and other factors
```{r,echo=FALSE,warning=FALSE}
#RT by WJ4 score
#ggplot(subj_table[subj_table$wj3_score>25,],aes(y=mean_rt,x=wj3_score))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="WJ4 Score", y="Response time (ms)",title="Resposne time by WJ4 score in vsl") + ylim(c(100,700))

#RT Slope by WJ4
ggplot(subj_table[subj_table$wj3_score>25,],aes(y=rt_slope,x=wj3_score))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="WJ4 Score", y="Response time slope",title="Resposne time slope by WJ4 score in VSL")  + ylim(c(-15,15))

#RT slope  vs WJ4 score by gender
#qplot(wj3_score,rt_slope,data=subset1[subset1$wj3_score>25,],facets=(. ~ gender),color= gender, main="vsl RT slope vs WJ4 scpre by gender", ylab="RT Slope", xlab="WJ4 score", ylim=c(-15,15)) + geom_smooth(method='lm') + scale_color_discrete(name="Gender")


#Mean rt vs WJ4 score by Handedness
#qplot(wj3_score,mean_rt,data=subj_table[subj_table$wj3_score>25,],facets=(. ~ handedness),color= handedness, main="vsl RT vs WJ4 score by Handedness", ylab="Response time", xlab="WJ4 score", ylim=c(100,600)) + geom_smooth(method='lm') + scale_color_discrete(name="Handedness")

#RT Slope vs WJ4 score by Handedness
#qplot(wj3_score,rt_slope,data=subj_table[subj_table$wj3_score>25,],facets=(. ~ handedness),color= handedness, main="vsl RT slope vs WJ4 score by Handedness", ylab="Response time slope", xlab="WJ4 score", ylim=c(-15,15)) + geom_smooth(method='lm') + scale_color_discrete(name="Handedness")



#RT by Language
#ggplot(subset2,aes(y=mean_rt,x=Language))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="WJ4 Score", y="Response time (ms)",title="Resposne time by Language score in vsl") + ylim(c(100,700))

#RT Slope by Language
#ggplot(subset2,aes(y=rt_slope,x=Language))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="Language Experience Score", y="Response time (ms)",title="RT slope by Language score in vsl") + ylim(c(-15,15))



```


## A partial correlation test between WJ4 score and RT Slope, controlling for age
```{r,echo=FALSE}

#correlation test between rt slope and wj4 score
pcor.test(subj_table$wj3_score, subj_table$rt_slope, subj_table$age, method="spearman")
```



##Accuracy and other factors
```{r,echo=FALSE}

ggplot(vsl_acc_table[vsl_acc_table$wj3_score>25,],aes(y=subj_corr,x=wj3_score))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="WJ4 Score", y="Accuracy",title="Accuracy by WJ4 score in vsl") 
#ggplot(vsl_acc_table[vsl_acc_table$Language>=20,],aes(y=subj_corr,x=Language))+geom_point(color='sienna') + geom_smooth(method='lm',color="sienna1") + labs(x="Language", y="Accuracy",title="Accuracy by Language in vsl") 



```



## A partial correlation test between WJ4 score and Accuracy, controlling for age
```{r,echo=FALSE}

#correlation test between rt slope and wj4 score
pcor.test(vsl_acc_table$wj3_score, vsl_acc_table$subj_corr, vsl_acc_table$age, method="spearman")
```


#Appendix
##Table 1
```{r,echo=FALSE}
table_output <- subj_table[,c("list_vsl_id","mean_rt","rt_slope","dprime")]
a <- seq(1,140,1)
new_id <- sprintf("mtsl_%03d", a)
table_output$list_vsl_id<-new_id
colnames(table_output) <- c("ID","Mean RT","RT Slope","D'")
kable(table_output)
```

##Table 2


```{r,echo=FALSE}
table_output2 <- vsl_acc_table[,c("acc_id","subj_corr","vsl_cond")]
a <- seq(1,142,1)
new_id <- sprintf("mtsl_%03d", a)
table_output2$acc_id<-new_id
colnames(table_output2) <- c("ID","accuracy(%)","condition")
kable(table_output2)
```

