---
title: "blast_fmri_clean_file"
author: "Jojo Hu"
date: "9/23/2022"
output: html_document
---

# Clean and move Adult Langloc files for extracting minimal of top 10% activation for each individual
```{r}
library(stringr)

aliceFile <-
  list.files("/Volumes/data/projects/blast/data/derivatives/fitlins/analyzed/fitlins_alice", 
           pattern = "sub-blasta", 
           full.names = T, recursive = F)

aliceFile <-
  list.files(paste0(aliceFile), 
           pattern = "level-run_name-runlevel_sub-blasta\\d+_run-\\d+_contrast-intactGtDegraded_stat-z_statmap.nii.gz", 
           full.names = T, recursive = F)

aliceFile <- as.data.frame(aliceFile)

aliceFile$aliceFile <- as.character(aliceFile$aliceFile)

aliceFile$basename <- basename(as.character(aliceFile$aliceFile))

aliceFile$part_id <- str_extract(aliceFile$basename, "sub-blasta[[:digit:]]+")

aliceFile$bare_id <- str_extract(aliceFile$basename, "(?<=sub-blasta)[[:digit:]]+")

aliceFile$run <- str_extract(aliceFile$basename, "(?<=run-)[[:digit:]]")

aliceFile$bare_run <- paste0(aliceFile$bare_id, "_", aliceFile$run)

aliceFile <- 
  aliceFile %>%
  arrange(aliceFile)

aliceFile$rename_id <- paste0(seq(1:nrow(aliceFile)), "_stat-z_statmap.nii.gz")

aliceFile$rename_number <- seq(1:nrow(aliceFile))

aliceFile$new_path <- paste0("/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/langloc_fitlins/adult/",
                             aliceFile$basename)

aliceFile$new_name <- paste0("/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/langloc_fitlins/adult/",
                             aliceFile$rename_id)


file.copy(as.character(aliceFile$aliceFile), aliceFile$new_path, overwrite = T)

file.rename(aliceFile$new_path, aliceFile$new_name)

write.csv(aliceFile, 
          "/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/langloc_fitlins/renamed_id_adult.csv", row.names = F)

my_output <- capture.output(write.table(aliceFile[, "bare_run"], sep = " ", col.names = F, row.names = F, quote = F, eol = "\n"))
writeBin(paste(my_output, collapse = "\n"),  "/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/langloc_fitlins/langloc_adult.txt")
```


# Clean and move Children Langloc files for extracting minimal of top 10% activation for each individual
```{r}
library(stringr)

aliceFile <-
  list.files("/Volumes/data/projects/blast/data/derivatives/fitlins/analyzed/fitlins_alice", 
           pattern = "level-run_name-runlevel_sub-blastc\\d+_run-\\d+_contrast-intactGtDegraded_stat-z_statmap.nii", 
           full.names = T, recursive = T)

aliceFile <- as.data.frame(aliceFile)

aliceFile$aliceFile <- as.character(aliceFile$aliceFile)

aliceFile$basename <- basename(as.character(aliceFile$aliceFile))

aliceFile$part_id <- str_extract(aliceFile$basename, "sub-blastc[[:digit:]]+")

aliceFile$bare_id <- str_extract(aliceFile$basename, "(?<=sub-blastc)[[:digit:]]+")

aliceFile$run <- str_extract(aliceFile$basename, "(?<=run-)[[:digit:]]")

aliceFile$bare_run <- paste0(aliceFile$bare_id, "_", aliceFile$run)

aliceFile <- 
  aliceFile %>%
  arrange(aliceFile)

aliceFile$rename_id <- paste0(seq(1:nrow(aliceFile)), "_stat-z_statmap.nii.gz")

aliceFile$rename_number <- seq(1:nrow(aliceFile))

aliceFile$new_path <- paste0("/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/langloc_fitlins/child/td/",
                             aliceFile$basename)

aliceFile$new_name <- paste0("/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/langloc_fitlins/child/td/",
                             aliceFile$rename_id)


file.copy(as.character(aliceFile$aliceFile), aliceFile$new_path, overwrite = T)

file.rename(aliceFile$new_path, aliceFile$new_name)

write.csv(aliceFile, 
          "/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/langloc_fitlins/renamed_id_child.csv", row.names = F)

my_output <- capture.output(write.table(aliceFile[, "bare_run"], sep = " ", col.names = F, row.names = F, quote = F, eol = "\n"))
writeBin(paste(my_output, collapse = "\n"),  "/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/langloc_fitlins/langloc_child.txt")
```


# Move and Rename ASL All adult contrasts to individual folders and rename them for Subject-specific ASL/ LangLoc analyses
```{r}
library(stringr)
library(dplyr)

output_path <- "/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/indiv_langloc_output/asl/adult/"

sl_path <- "/Volumes/data/projects/blast/data/derivatives/fitlins/analyzed/fitlins"

slFile <-
  list.files(sl_path,
           pattern = "sub-blasta", 
           full.names = T, recursive = F)

slFile <-
  list.files(slFile,
           pattern = "level-run_name-run_sub-blasta\\d+_run-\\d+_contrast-[[:alpha:]]+VRest_stat-z_statmap.nii.gz", 
           full.names = T, recursive = F)

bk <- slFile

slFile <- as.data.frame(slFile)

slFile$basename <- basename(as.character(slFile$slFile))

slFile$part_id <- str_extract(slFile$basename, "sub-blasta[[:digit:]]+")

slFile$bare_id <- str_extract(slFile$basename, "(?<=sub-blasta)[[:digit:]]+")

slFile$run <- str_extract(slFile$basename, "(?<=run-)[[:digit:]]")

slFile$stimuli <- str_extract(slFile$basename, "(Speech|Tone)")

slFile$condition <- str_extract(slFile$basename, "(rand|str)")

slFile12 <- 
  slFile %>%
  filter(run == "1" | run == "2") %>%
  filter((stimuli == "Speech" & condition == "str") | (stimuli == "Tone" & condition == "rand"))

slFile34 <- 
  slFile %>%
  filter(run == "3" | run == "4") %>%
  filter((stimuli == "Speech" & condition == "rand") | (stimuli == "Tone" & condition == "str"))

slRest <- rbind(slFile12, slFile34)

slRest <-
  slRest %>%
  arrange(slRest) 

slRest$stimuli <- tolower(slRest$stimuli)

slRest$subj_cond <- paste0(slRest$bare_id, "_", "run_", slRest$run, "_", slRest$stimuli, "_", slRest$condition)

for (i in 1:length(unique(slRest$bare_id))) {
  dir.create(paste0(output_path, unique(slRest$bare_id)[i]))
}

slRest$rename_path <- paste0(output_path, slRest$bare_id, "/", slRest$subj_cond, ".nii.gz")

file.copy(as.character(slRest$slFile), slRest$rename_path, overwrite = F)

for (i in unique(slRest$bare_id)) {
  temp <- slRest[which(slRest$bare_id %in% i), "subj_cond"]
  
  my_output <- capture.output(write.table(temp, sep = " ", col.names = F, row.names = F, quote = F, eol = "\n"))
  writeBin(paste(my_output, collapse = "\n"),  paste0(output_path, i, "/", i, ".txt"))
}
```



# Move and Rename ASL All child contrasts to individual folders and rename them for Subject-specific ASL/ LangLoc analyses
```{r}
library(stringr)
library(dplyr)

output_path <- "/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/indiv_langloc_output/asl/child/"

sl_path <- "/Volumes/data/projects/blast/data/derivatives/fitlins/analyzed/fitlins"

slFile <-
  list.files(sl_path,
           pattern = "sub-blastc", 
           full.names = T, recursive = F)

slFile <-
  list.files(slFile,
           pattern = "level-run_name-run_sub-blastc\\d+_run-\\d+_contrast-[[:alpha:]]+VRest_stat-z_statmap.nii.gz", 
           full.names = T, recursive = F)

bk <- slFile

slFile <- as.data.frame(slFile)

slFile$basename <- basename(as.character(slFile$slFile))

slFile$part_id <- str_extract(slFile$basename, "sub-blastc[[:digit:]]+")

slFile$bare_id <- str_extract(slFile$basename, "(?<=sub-blastc)[[:digit:]]+")

slFile$run <- str_extract(slFile$basename, "(?<=run-)[[:digit:]]")

slFile$stimuli <- str_extract(slFile$basename, "(Speech|Tone)")

slFile$condition <- str_extract(slFile$basename, "(rand|str)")

slFile12 <- 
  slFile %>%
  filter(run == "1" | run == "2") %>%
  filter((stimuli == "Speech" & condition == "str") | (stimuli == "Tone" & condition == "rand"))

slFile34 <- 
  slFile %>%
  filter(run == "3" | run == "4") %>%
  filter((stimuli == "Speech" & condition == "rand") | (stimuli == "Tone" & condition == "str"))

slRest <- rbind(slFile12, slFile34)

slRest <-
  slRest %>%
  arrange(slRest) 

slRest$stimuli <- tolower(slRest$stimuli)

slRest$subj_cond <- paste0(slRest$bare_id, "_", "run_", slRest$run, "_", slRest$stimuli, "_", slRest$condition)

for (i in 1:length(unique(slRest$bare_id))) {
  dir.create(paste0(output_path, unique(slRest$bare_id)[i]))
}

slRest$rename_path <- paste0(output_path, slRest$bare_id, "/", slRest$subj_cond, ".nii.gz")

file.copy(as.character(slRest$slFile), slRest$rename_path, overwrite = F)

for (i in unique(slRest$bare_id)) {
  temp <- slRest[which(slRest$bare_id %in% i), "subj_cond"]
  
  my_output <- capture.output(write.table(temp, sep = " ", col.names = F, row.names = F, quote = F, eol = "\n"))
  writeBin(paste(my_output, collapse = "\n"),  paste0(output_path, i, "/", i, ".txt"))
}
```



# Dorsal Attention Network Cleaning
# Clean and Move ASL Random vs. Rest output for adults for extracting minimal of top 10% activation for each individual
```{r}
library(stringr)

aslRandFile <-
  list.files("/Volumes/data/projects/blast/data/derivatives/fitlins/analyzed/fitlins", 
           pattern = "sub-blasta", 
           full.names = T, recursive = F)

aslRandFile <-
  list.files(aslRandFile, 
           pattern = "level-run_name-run_sub-blasta\\d+_run-\\d+_contrast-rand[[:alpha:]]+VRest_stat-z_statmap.nii.gz", 
           full.names = T, recursive = F)

aslRandFile <- as.data.frame(aslRandFile)

aslRandFile$aslRandFile <- as.character(aslRandFile$aslRandFile)

aslRandFile$basename <- basename(as.character(aslRandFile$aslRandFile))

aslRandFile$part_id <- str_extract(aslRandFile$basename, "sub-blasta[[:digit:]]+")

aslRandFile$bare_id <- str_extract(aslRandFile$basename, "(?<=sub-blasta)[[:digit:]]+")

aslRandFile$run <- str_extract(aslRandFile$basename, "(?<=run-)[[:digit:]]")

aslRandFile$bare_run <- paste0(aslRandFile$bare_id, "_", aslRandFile$run, "_", tolower(str_extract(aslRandFile$basename, "(Speech|Tone)")))

aslRandFile$stimuli <- str_extract(aslRandFile$basename, "(Speech|Tone)")

aslRandFile$condition <- str_extract(aslRandFile$basename, "(str|rand)")

aslRandFile12 <- 
  aslRandFile %>%
  filter(run == "1" | run == "2") %>%
  filter((stimuli == "Speech" & condition == "str") | (stimuli == "Tone" & condition == "rand"))

aslRandFile34 <- 
  aslRandFile %>%
  filter(run == "3" | run == "4") %>%
  filter((stimuli == "Speech" & condition == "rand") | (stimuli == "Tone" & condition == "str"))

aslRandFile <- rbind(aslRandFile12, aslRandFile34)

aslRandFile <- 
  aslRandFile %>%
  arrange(aslRandFile)

aslRandFile$rename_id <- paste0(seq(1:nrow(aslRandFile)), "_stat-z_statmap.nii.gz")

aslRandFile$rename_number <- seq(1:nrow(aslRandFile))

aslRandFile$new_path <- paste0("/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/asl_attention/adult/",
                             aslRandFile$basename)

aslRandFile$new_name <- paste0("/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/asl_attention/adult/",
                             aslRandFile$rename_id)


file.copy(as.character(aslRandFile$aslRandFile), aslRandFile$new_path, overwrite = F)

file.rename(aslRandFile$new_path, aslRandFile$new_name)

write.csv(aslRandFile, 
          "/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/asl_attention/renamed_id_adult.csv", row.names = F)

my_output <- capture.output(write.table(aslRandFile[, "bare_run"], sep = " ", col.names = F, row.names = F, quote = F, eol = "\n"))
writeBin(paste(my_output, collapse = "\n"),  "/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/asl_attention/langloc_adult.txt")
```


# Clean and Move ASL Random vs. Rest output for children for extracting minimal of top 10% activation for each individual
```{r}
library(stringr)

aslRandFile <-
  list.files("/Volumes/data/projects/blast/data/derivatives/fitlins/analyzed/fitlins", 
           pattern = "sub-blastc", 
           full.names = T, recursive = F)

aslRandFile <-
  list.files(aslRandFile, 
           pattern = "level-run_name-run_sub-blastc\\d+_run-\\d+_contrast-rand[[:alpha:]]+VRest_stat-z_statmap.nii.gz", 
           full.names = T, recursive = F)

aslRandFile <- as.data.frame(aslRandFile)

aslRandFile$aslRandFile <- as.character(aslRandFile$aslRandFile)

aslRandFile$basename <- basename(as.character(aslRandFile$aslRandFile))

aslRandFile$part_id <- str_extract(aslRandFile$basename, "sub-blastc[[:digit:]]+")

aslRandFile$bare_id <- str_extract(aslRandFile$basename, "(?<=sub-blastc)[[:digit:]]+")

aslRandFile$run <- str_extract(aslRandFile$basename, "(?<=run-)[[:digit:]]")

aslRandFile$bare_run <- paste0(aslRandFile$bare_id, "_", aslRandFile$run, "_", tolower(str_extract(aslRandFile$basename, "(Speech|Tone)")))

aslRandFile$stimuli <- str_extract(aslRandFile$basename, "(Speech|Tone)")

aslRandFile$condition <- str_extract(aslRandFile$basename, "(str|rand)")

aslRandFile12 <- 
  aslRandFile %>%
  filter(run == "1" | run == "2") %>%
  filter((stimuli == "Speech" & condition == "str") | (stimuli == "Tone" & condition == "rand"))

aslRandFile34 <- 
  aslRandFile %>%
  filter(run == "3" | run == "4") %>%
  filter((stimuli == "Speech" & condition == "rand") | (stimuli == "Tone" & condition == "str"))

aslRandFile <- rbind(aslRandFile12, aslRandFile34)

aslRandFile <- 
  aslRandFile %>%
  arrange(aslRandFile)

aslRandFile$rename_id <- paste0(seq(1:nrow(aslRandFile)), "_stat-z_statmap.nii.gz")

aslRandFile$rename_number <- seq(1:nrow(aslRandFile))

aslRandFile$new_path <- paste0("/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/asl_attention/child/",
                             aslRandFile$basename)

aslRandFile$new_name <- paste0("/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/asl_attention/child/",
                             aslRandFile$rename_id)


file.copy(as.character(aslRandFile$aslRandFile), aslRandFile$new_path, overwrite = T)

file.rename(aslRandFile$new_path, aslRandFile$new_name)

write.csv(aslRandFile, 
          "/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/asl_attention/renamed_id_child.csv", row.names = F)

my_output <- capture.output(write.table(aslRandFile[, "bare_run"], sep = " ", col.names = F, row.names = F, quote = F, eol = "\n"))
writeBin(paste(my_output, collapse = "\n"),  "/Volumes/data/projects/blast/data/mri/imaging/scott_gcss_lpsa/data/asl_attention/langloc_child.txt")
```


