---
title: "in_scanner_aduly_beh_run1_3_analysis"
author: "Jojo Hu"
date: "9/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Blast In Scanner Adult Behavioral Analysis for Run 1 and 3

1. Please look at the histogram, scatter plots for data distribution. 
2. Please look at the descriptive statistics.
3. Please look at mean RT paired t-test results.
4. RT slope has not been analyzed. Please ignore any results for RT slope now.
5. Bar graphs do not have significance level marked. Please check t.test.

```{r}
#Set up current working directory
setwd (
  ""
)

output_path <- (
  ""
)

# Read in in-scanner behavioral data
visual_data <-
  read.csv("adult_in_scanner_visual_behavioral_run1_3.csv")
auditory_data <-
  read.csv("adult_in_scanner_auditory_behavioral_run1_3.csv")

#Visual data--------------------------------------------------------------------------------------
#Plot the basic data------------------------------------------------------------------------------
#Remove the participants who do not have data
#First, transform the column type to numeric for later analysis
type_converted_column_index <-
  match(
    c(
      "structured_vsl_rt_slope",
      "random_vsl_rt_slope",
      "structured_lsl_rt_slope",
      "random_lsl_rt_slope",
      "structured_image_mean_rt",
      "random_image_mean_rt",
      "structured_letter_mean_rt",
      "random_letter_mean_rt"
    ),
    names(visual_data)
  )

visual_data[, c(type_converted_column_index)] <-
  lapply(visual_data[, c(type_converted_column_index)],
         function(x)
           as.numeric(as.character(x)))

#Remove participants that do have all data
#Save whose data are deleted, participants with too few hits or no hits.

deleted_id_incomplete_data <-
  paste("deleted visual id due to too few or no hits:",
        visual_data[!complete.cases(visual_data[, c(type_converted_column_index)]),
                    "visual_part_id"])

visual_data <-
  visual_data[complete.cases(visual_data[, c(type_converted_column_index)]),]

#Plot histograms and dot plots to look at the distribution of the data first (Normal Distribution? Outliners?)
#Save the plots into a pdf file

library("reshape")
library("ggplot2")

hist_long_data <- melt(visual_data, id.vars = "visual_part_id")

hist_var_plotted <- c(
  "total_image_rts",
  "total_letter_rts",
  "structured_image_mean_rt",
  "random_image_mean_rt",
  "structured_letter_mean_rt",
  "random_letter_mean_rt",
  "structured_vsl_rt_slope",
  "random_vsl_rt_slope",
  "structured_lsl_rt_slope",
  "random_lsl_rt_slope"
)

hist_long_data <-
  hist_long_data[which(hist_long_data$variable %in% hist_var_plotted),]

pdf("visual_data_distribution_sanity_check.pdf")

hist_visual <-
  ggplot(hist_long_data,
         aes(value)) +
  geom_histogram() +
  facet_wrap(~ variable, scales = "free")

#Histogram for visual data
print(hist_visual)

dot_visual <-
  ggplot(hist_long_data,
         aes(x = visual_part_id, y = value)) +
  geom_point() +
  facet_wrap(~ variable, scales = "free")

#Scatter plot for visual data
print(dot_visual)

dev.off()

#----------------------------------------------------------------------------------------------

#Learning Effect Analysis----------------------------------------------------------------------------
#Descriptive Stats for Visual Data
library("psych")
descrip_visual_column <- c(
  "structured_image_mean_rt",
  "random_image_mean_rt",
  "structured_letter_mean_rt",
  "random_letter_mean_rt"
)

descrip_visual_data <-
  visual_data[, which(names(visual_data) %in% descrip_visual_column)]

descrip_stat_visual <- describe(descrip_visual_data)

#Descriptive statistics for visual data
print(descrip_stat_visual)

write.csv(descrip_stat_visual,
          paste0(output_path, "descrip_stat_visual.csv"))

# Run Welch's paired t-test on mean RT
# p<0.05 tells us that random has significantly longer mean RT than structured, and there is learning effect

#T.test for letter
t.test(
  visual_data$random_letter_mean_rt,
  visual_data$structured_letter_mean_rt,
  paired = TRUE,
  alternative = "greater"
)

#T.test for image
t.test(
  visual_data$random_image_mean_rt,
  visual_data$structured_image_mean_rt,
  paired = TRUE,
  alternative = "greater"
)

#Auditory_data---------------------------------------------------------------------------------------
type_converted_column_index_auditory <-
  match(
    c(
      "structured_ssl_rt_slope",
      "random_ssl_rt_slope",
      "structured_tsl_rt_slope",
      "random_tsl_rt_slope",
      "structured_syllable_mean_rt",
      "random_syllable_mean_rt",
      "structured_tone_mean_rt",
      "random_tone_mean_rt"
    ),
    names(auditory_data)
  )

auditory_data[, c(type_converted_column_index_auditory)] <-
  lapply(auditory_data[, c(type_converted_column_index_auditory)],
         function(x)
           as.numeric(as.character(x)))

#Remove participants that do have all data
#Save whose data are deleted, participants with too few hits or no hits.

deleted_id_incomplete_data_auditory <-
  paste("deleted auditory id due to too few or no hits:",
        auditory_data[!complete.cases(auditory_data[, c(type_converted_column_index_auditory)]),
                      "auditory_part_id"])

deleted_id_incomplete_data <-
  rbind(deleted_id_incomplete_data,
        deleted_id_incomplete_data_auditory)

write.csv(deleted_id_incomplete_data,
          paste0(output_path, "deleted_id_in_analysis.csv"))

#THe participants that are deleted because of too few hits or no hits
print(deleted_id_incomplete_data)

auditory_data <- auditory_data[complete.cases(auditory_data[, c(type_converted_column_index_auditory)]), ]

#Plot histograms and dot plots to look at the distribution of the data first (Normal Distribution? Outliners?)
#Save the plots into a pdf file
pdf("auditory_data_distribution_sanity_check.pdf")

library("reshape")
library("ggplot2")

hist_long_data_auditory <-
  melt(auditory_data, id.vars = "auditory_part_id")

hist_auditory_column <- c(
  "total_tone_rts",
  "total_syllable_rts",
  "structured_tone_mean_rt",
  "random_tone_mean_rt",
  "structured_syllable_mean_rt",
  "random_syllable_mean_rt",
  "structured_tsl_rt_slope",
  "random_tsl_rt_slope",
  "structured_ssl_rt_slope",
  "random_ssl_rt_slope"
)

hist_long_data_auditory <-
  hist_long_data_auditory[which(hist_long_data_auditory$variable %in% hist_auditory_column), ]

hist_auditory <- ggplot(hist_long_data_auditory,
                        aes(value)) +
  geom_histogram() +
  facet_wrap(~ variable, scales = "free")

#Histogram for auditory data
print(hist_auditory)

dot_auditory <- ggplot(hist_long_data_auditory,
                       aes(x = auditory_part_id, y = value)) +
  geom_point() +
  facet_wrap(~ variable, scales = "free")

#Scatter plots for auditory data
print(dot_auditory)

dev.off()


#---------------------------------------------------------------------------------

#Learning Effect Analysis---------------------------------------------------------
#Descriptive Stats for auditory Data
library("psych")
descrip_auditory_column <- c(
  "structured_tone_mean_rt",
  "random_tone_mean_rt",
  "structured_syllable_mean_rt",
  "random_syllable_mean_rt"
)

descrip_auditory_data <-
  auditory_data[, which(names(auditory_data) %in% descrip_auditory_column)]

descrip_stat_auditory <- describe(descrip_auditory_data)

write.csv(descrip_stat_auditory,
          paste0(output_path, "descrip_stat_auditory.csv"))

#Descriptive data for auditory
print(descrip_stat_auditory)

#T.test for auditory data-------------------------------------------------------
# p<0.05 tells us that random has significantly longer mean RT than structured, and there is learning effect

#T.test for tone
t.test(
  auditory_data$random_tone_mean_rt,
  auditory_data$structured_tone_mean_rt,
  paired = TRUE,
  alternative = "greater"
)

#T.test for syllable
t.test(
  auditory_data$random_syllable_mean_rt,
  auditory_data$structured_syllable_mean_rt,
  paired = TRUE,
  alternative = "greater"
)
```

Plot Bar graphs for Mean RT

```{r}
#Prepare visual bar graph data-----------------------------------------------
library("reshape")

bar_visual_data <-
  melt(
    visual_data,
    by.vars = c("visual_part_id"),
    measure.vars = c(
      "structured_image_mean_rt",
      "random_image_mean_rt",
      "structured_letter_mean_rt",
      "random_letter_mean_rt"
    )
  )

library("stringr")

colnames(bar_visual_data)[colnames(bar_visual_data) == "value"] <-
  "Mean_Reaction_Time"

bar_visual_data[which(str_detect(bar_visual_data$variable, "structured") == TRUE),
                c("Condition")] <-
  "Structured"

bar_visual_data[which(str_detect(bar_visual_data$variable, "random") == TRUE),
                c("Condition")] <-
  "Random"

bar_visual_data[which(str_detect(bar_visual_data$variable, "image") == TRUE), c("Type")]  <-
  "Image"

bar_visual_data[which(str_detect(bar_visual_data$variable, "letter") == TRUE), c("Type")]  <-
  "Letter"

#ggplot visual bar grapgh--------------------------------------------------------
library("ggbeeswarm")
library("ggsignif")

visual_bar_graph <-
  ggplot(bar_visual_data, aes(x = Type, y = Mean_Reaction_Time)) +
  geom_bar(
    aes(fill = Condition),
    stat = "summary",
    fun.y = "mean",
    position = position_dodge(width = 0.9),
    width = 0.9
  ) +
  geom_beeswarm(
    aes(fill = Condition),
    dodge.width = 0.9,
    cex = 2.5,
    size = 0.8,
    show.legend = FALSE
  ) +
  ylab("Mean Reaction Time (ms)") +
  xlab("Task") +
  theme(
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 14, face = "bold"),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 12)
  ) +
  geom_signif(
    annotations = "*",
    y_position = 650,
    xmin = 0.75,
    xmax = 1.25,
    tip_length = 0.01,
    vjust = 0.4
  ) +
  geom_signif(
    annotations = "***",
    y_position = 650,
    xmin = 1.75,
    xmax = 2.25,
    tip_length = 0.01,
    vjust = 0.4
  )

ggsave(paste0(output_path, "visual_mean_rt_graph.png"),
       dpi = 150)

#Bar plot for visual mean RT by task and condition
print(visual_bar_graph)

#Prepare auditory bar graph data---------------------------------------------
bar_auditory_data <-
  melt(
    auditory_data,
    by.vars = c("auditory_part_id"),
    measure.vars = c(
      "structured_tone_mean_rt",
      "random_tone_mean_rt",
      "structured_syllable_mean_rt",
      "random_syllable_mean_rt"
    )
  )

colnames(bar_auditory_data)[colnames(bar_auditory_data) == "value"] <-
  "Mean_Reaction_Time"


bar_auditory_data[which(str_detect(bar_auditory_data$variable, "structured") == TRUE),
                  c("Condition")] <-
  "Structured"

bar_auditory_data[which(str_detect(bar_auditory_data$variable, "random") == TRUE),
                  c("Condition")] <-
  "Random"

bar_auditory_data[which(str_detect(bar_auditory_data$variable, "tone") == TRUE), c("Type")]  <-
  "Tone"

bar_auditory_data[which(str_detect(bar_auditory_data$variable, "syllable") == TRUE), c("Type")]  <-
  "Syllable"

bar_auditory_data$Type <- as.character(bar_auditory_data$Type)
bar_auditory_data$Type <- factor(bar_auditory_data$Type, levels =
                                   c("Tone", "Syllable"))

bar_auditory_data <-
  bar_auditory_data[order(bar_auditory_data$Type),]

#Plot auditory bar graph-----------------------------------------------------
auditory_bar_graph <-
  ggplot(bar_auditory_data, aes(x = Type, y = Mean_Reaction_Time)) +
  geom_bar(
    aes(fill = Condition),
    stat = "summary",
    fun.y = "mean",
    position = position_dodge(width = 0.9),
    width = 0.9
  ) +
  geom_beeswarm(
    aes(fill = Condition),
    dodge.width = 0.9,
    cex = 2.5,
    size = 0.8,
    show.legend = FALSE
  ) +
  ylab("Mean Reaction Time (ms)") +
  xlab("Task") +
  theme(
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 14, face = "bold"),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 12)
  ) +
  geom_signif(
    annotations = "check t.test",
    y_position = 800,
    xmin = 1.75,
    xmax = 2.25,
    tip_length = 0.01,
    vjust = 0.4
  ) +
  geom_signif(
    annotations = "check t.test",
    y_position = 800,
    xmin = 0.75,
    xmax = 1.25,
    tip_length = 0.01,
    vjust = 0.4
  ) +
  scale_fill_brewer(palette = "Set2")

ggsave("auditory_mean_rt_graph.png",
       dpi = 150)

#Bar plot for auditory data by task and condition
print(auditory_bar_graph)
```
