---
title: "HEB_Online_Rating"
author: "JM Schneider"
date: "12/8/2020"
output: html_document
---
### Import libraries
```{r loadlib, echo=T, results='hide', message=F, warning=F}
library(psych)
library(readr)
library(optimx)
library(corrplot)
library(reshape)
library(reshape2)
library(lmerTest)
library(ggplot2)
library(scales)
library(ggbeeswarm)
library(Hmisc)
library(arm)
library(ez)
library(dplyr)
library(arm)
library(tidyr)
library(tidyverse)
```

### Load HEB Online Rating data output as dataframe

```{r}
setwd("/Volumes/data/projects/writing/heb/data_paper/data/")
df_eng=read.csv('english.csv')
df_heb=read.csv('hebrew.csv')
```

### Rename columns to words
```{r}
df_eng <- df_eng %>% rename(part_ID = Q4, gobuku = Q70_1, daropi = Q71_1, dabitu = Q68_1, bidapu = Q67_1, golatu = Q72_1, kubiro = Q73_1, pabiku = Q74_1, parodo = Q75_1, tibudo = Q76_1, tilapi = Q77_1, dukame = Q78_1, duloga = Q79_1, gedino = Q80_1, gekalu = Q81_1, kibano = Q82_1, kimuga = Q83_1, nadima = Q84_1, nalobi = Q85_1, tobalu = Q86_1, tomubi = Q87_1)

df_heb <- df_heb %>% rename(part_ID = Q4, gobuku = Q70_1, daropi = Q71_1, dabitu = Q68_1, bidapu = Q67_1, golatu = Q72_1, kubiro = Q73_1, pabiku = Q74_1, parodo = Q75_1, tibudo = Q76_1, tilapi = Q77_1, dukame = Q78_1, duloga = Q79_1, gedino = Q80_1, gekalu = Q81_1, kibano = Q82_1, kimuga = Q83_1, nadima = Q84_1, nalobi = Q85_1, tobalu = Q86_1, tomubi = Q87_1)
```


### Compute average rating on each English and Hebrew Item for both groups of Speakers
```{r}
df_eng = df_eng[-1,]
df_eng <- mutate_all(df_eng, function(x) as.numeric(as.character(x)))
colMeans(df_eng)

df_heb = df_heb[-1,]
df_heb <- mutate_all(df_heb, function(x) as.numeric(as.character(x)))
colMeans(df_heb)
```

### Compute average overall rating for English and Hebrew Items for both groups of Speakers
```{r}
df_eng$eng_item_mean <- rowMeans(subset(df_eng, select = c(3:12)), na.rm = TRUE)
df_eng$heb_item_mean <- rowMeans(subset(df_eng, select = c(13:22)), na.rm = TRUE)
df_heb$eng_item_mean <- rowMeans(subset(df_heb, select = c(3:12)), na.rm = TRUE)
df_heb$heb_item_mean <- rowMeans(subset(df_heb, select = c(13:22)), na.rm = TRUE)
```

## Statistics
### Do English and Hebrew speakers significantly differ in their ratings of English-like words?
```{r}
t.test(df_eng$eng_item_mean,df_heb$eng_item_mean, paired = TRUE)
eng_eng_item_mean = mean(df_eng$eng_item_mean)
heb_eng_item_mean = mean(df_heb$eng_item_mean)
eng_eng_item_mean
heb_eng_item_mean
```
### Do English and Hebrew speakers significantly differ in their ratings of Hebrew-like words?
```{r}
t.test(df_eng$heb_item_mean,df_heb$heb_item_mean, paired = TRUE)
eng_heb_item_mean = mean(df_eng$heb_item_mean)
heb_heb_item_mean = mean(df_heb$heb_item_mean)
eng_heb_item_mean
heb_heb_item_mean
```
