---
title: "manuscript_analysis_clean"
author: "Jojo Hu"
date: "06/10/2021"
output: html_document
---

# Manuscript Analysis Cleaned (02/18/2021)


``` {r}
# setwd("/manuscript")

allData <- read.csv("allSLData.csv")
```

# Section 1: Demographic Analyses

## Gender
```{r}
library(reshape)

allData_gender_wide <- allData[,c("part_id", "group", "gender")]

allData_gender_long <- melt(allData_gender_wide, id.vars = c("part_id", "group"))

gender_wide <- cast(allData_gender_long, group~value, length)

# Chi-square on gender
# p<0.05 tells us that they are not matched for gender between group
print(gender_wide)

print(chisq.test(gender_wide))
```

**Gender is matched between group**

## Age
```{r}
library(dplyr)

allData$age_at_web_year <- allData$age_at_web_month/12

allData %>%
  group_by(group) %>%
  dplyr::summarise(mean_age = mean(age_at_web_year), SD = sd(age_at_web_year), min = min(age_at_web_year), max = max(age_at_web_year)) %>%
  mutate_if(is.numeric, round, 2) %>%
  slice(match(c("TD", "ASD"), group))
  
allData_td <- 
  allData[which(allData$group == "TD"),]
allData_asd <- 
  allData[which(allData$group == "ASD"),]

#Test age difference between group, p <0.05 means age is significantly different between group
print(t.test(allData_td$age_at_web_year, allData_asd$age_at_web_year))
```

## Parental Report of Language Level in ASD
```{r}
allData %>%
  group_by(group, language_age_level) %>%
  dplyr::summarise(n = n())
```

## SCQ, RBS-R Descriptive Stat
```{r, include = F}
allData %>%
  dplyr::rename(scq_current = scq_total,
                scq_lifetime = scq_web) %>%
  group_by(group) %>%
  dplyr::summarise(across(c("scq_current", "scq_lifetime", "rbs_r"), 
                   list(mean = ~ mean(., na.rm = TRUE), SD = ~ sd(., na.rm = TRUE), N = ~ sum(!is.na(.))))) %>%
   slice(match(c("TD", "ASD"), group))
```

## SCQ T-tests
```{r}
# SCQ comparison between ASD and TD
t.test(allData_td$scq_total, allData_asd$scq_web)
```

## Remove outliers for RT and RT slope 
```{r}
library(stringr)

rt_hit_count_child <- read.csv("rt_hit_count_child.csv")
child_rt_outlier <- rt_hit_count_child[which(rt_hit_count_child$hit_trial_number < 6), ]
print(child_rt_outlier)
```
**Table above are RT outliers in children with less than 6 hit trials in the familiarization phase**

## Remove outliers in the children group
```{r, include = F}
outlier_extract <-
  function(DF, task) {
    part_id <- DF[which(DF$task == task), "part_id"]
    rt_col <- paste0(task, "_rt")
    slope_col <- paste0(task, "_slope")
    
    if(length(part_id) != 0) {
      allData[which(allData$part_id %in% part_id), 
              c(rt_col, slope_col)] <- NA
      }
    return(allData)
    }

allData <- outlier_extract(child_rt_outlier, "ssl")
allData <- outlier_extract(child_rt_outlier, "tsl")
allData <- outlier_extract(child_rt_outlier, "vsl")
allData <- outlier_extract(child_rt_outlier, "lsl")

print(child_rt_outlier)
```

**Above is removed outliers in the children group:**

**RT and Slope < 6 hits:+ 1 ASD spoli_c_097 (jsPsyc technical error in SSL RT)**

## Count the number of completed participants for each task
```{r,include = F}
allData$scq_web <- as.numeric(as.character(allData$scq_web))

completeCount <- function(group) {
  df <- sapply(allData[which(allData$group == group),
                       c("scq_web",
                         "scq_total",
                         "rbs_r",
                         "vsl_acc",
                         "lsl_acc",
                         "tsl_acc",
                         "ssl_acc")],
               function(x) sum(!is.na(x)))
  return(df)
}

taskcomp_td <- completeCount("TD")
taskcomp_asd <- completeCount("ASD")

taskcomp_count<- rbind(taskcomp_td, taskcomp_asd)
taskcomp_count <- data.frame(taskcomp_count)

colnames(taskcomp_count) <- c("SCQ Lifetime", "SCQ Current", "RBS-R", "Image", "Letter", "Tone", "Syllable")

missing_scq_web <- allData[which(is.na(allData$scq_web) & allData$group == "ASD"), "part_id"]

countThreeTask <- function(group) {
  threeTaskCount <- rowSums(!is.na(allData[which(allData$group == group),
                       c("vsl_acc", 
                           "lsl_acc",
                           "tsl_acc", 
                           "ssl_acc")]))
  return(threeTaskCount)
}
# Number of participants with 3 SL tasks
length(which(countThreeTask("TD") == 3))
length(which(countThreeTask("ASD") == 3))

print(taskcomp_count)
```

**Missing SCQ: spoli_c_439; spoli_c_448: No SCQ-L scores from SPARK; blast_c_438: Not from SPARK**


# Section 2: SL Group Comparison Reaction Time 

## Preprocess by trial RT data, remove the RT Slope outliers
```{r, include = F}
rt_trial <- read.csv("rt_trial.csv")

outlier_extract_trial_rt <-
  function(DF, task) {
    part_id <- DF[which(DF$task == task), "part_id"]
    
    if (length(part_id) != 0) {
      rt_trial[-which(rt_trial$id %in% part_id & rt_trial$task == task), ]
    }
    return(rt_trial)
  }

rt_trial <- outlier_extract_trial_rt(child_rt_outlier, "ssl")
rt_trial <- outlier_extract_trial_rt(child_rt_outlier, "tsl")
rt_trial <- outlier_extract_trial_rt(child_rt_outlier, "vsl")
rt_trial <- outlier_extract_trial_rt(child_rt_outlier, "lsl")

# Count N for each task
rt_trial %>%
  group_by(group, task) %>%
  filter(!is.na(reaction_time)) %>%
  summarize(n = length(unique(id))) %>%
  slice(match(c("lsl", "ssl", "vsl", "tsl"), task))
```

## Number of hit trials in TD vs. ASD
```{r}
hit_trialN <- 
  rt_trial %>%
  subset(., !is.na(reaction_time)) %>%
  group_by(group, id, task) %>%
  dplyr::summarise(hit_trial_n = n())

# Count hits for each task
hit_trial_mean <-
  hit_trialN %>%
  group_by(group, task) %>%
  dplyr::summarise(
    mean_hit_trial = mean(hit_trial_n),
    sd = sd(hit_trial_n),
    n = n()
  ) %>%
  mutate(
    se = sd / sqrt(n),
    lower_ci = mean_hit_trial - qt(1 - (0.05 / 2), n - 1) * se,
    upper_ci = mean_hit_trial + qt(1 - (0.05 / 2), n - 1) * se
  ) %>%
  select(group, task, mean_hit_trial, lower_ci, upper_ci) %>%
  slice(match(c("lsl", "ssl", "vsl", "tsl"), task))

hit_trial_mean[,-c(1:2)] <- round(hit_trial_mean[,-c(1:2)], 2)

print(hit_trial_mean)
```

## Compare hit trials in TD vs. ASD
```{r}
library("stringr")
library("lmerTest")
add_dom_mod_func <-
  function(df) {
    df[which(str_detect(df$task, "ssl")), "domain"] <- "ling"
    df[which(str_detect(df$task, "lsl")), "domain"] <- "ling"
    df[which(str_detect(df$task, "vsl")), "domain"] <- "nonling"
    df[which(str_detect(df$task, "tsl")), "domain"] <- "nonling"
    df[which(str_detect(df$task, "ssl")), "modality"] <- "auditory"
    df[which(str_detect(df$task, "tsl")), "modality"] <- "auditory"
    df[which(str_detect(df$task, "vsl")), "modality"] <- "visual"
    df[which(str_detect(df$task, "lsl")), "modality"] <- "visual"
    return (df)
  }

hit_trialN <- add_dom_mod_func(hit_trialN)

m1_hit_trial <-
lmer(hit_trial_n ~ group*domain*modality + (1+domain+modality|id), data = hit_trialN,
       contrasts = list(group = c(-1,1),
                        domain = c(-1,1),
                        modality = c(-1,1)))

summary(m1_hit_trial)

hitsASD <- subset(hit_trialN, group == "ASD")
hitsTD <- subset(hit_trialN, group == "TD")

hit_trialN <- hit_trialN[!colnames(hit_trialN) %in% "group"]

# Add number of hits to the by trial RT data
rt_trial <- 
  merge(rt_trial, hit_trialN[,c("id", "task", "hit_trial_n")], by.x = c("id", "task"), by.y = c("id", "task"), all.x = T)

# Post-hoc t-tests for number of hits in each task
t.test(hitsTD[which(hitsTD$task == "lsl"),]$hit_trial_n, hitsASD[which(hitsASD$task == "lsl"),]$hit_trial_n)
t.test(hitsTD[which(hitsTD$task == "ssl"),]$hit_trial_n, hitsASD[which(hitsASD$task == "ssl"),]$hit_trial_n)
t.test(hitsTD[which(hitsTD$task == "vsl"),]$hit_trial_n, hitsASD[which(hitsASD$task == "vsl"),]$hit_trial_n)
t.test(hitsTD[which(hitsTD$task == "tsl"),]$hit_trial_n, hitsASD[which(hitsASD$task == "tsl"),]$hit_trial_n)
```

## Normalize by trial raw RT for each participant and each task
```{r}
rt_trial_scaled <- rt_trial
rt_trial_scaled <- rt_trial_scaled[!is.na(rt_trial_scaled$reaction_time),]

for(id in unique(rt_trial_scaled$id)) {
    # Extract each id's individual rt by trial (normalized results below are the same as the scaled RT in the RT slope analyses; checked)
    rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "lsl"), "scaled_rt"] <- 
      scale(rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "lsl"),"reaction_time"], center = T)
    rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "vsl"), "scaled_rt"] <- 
      scale(rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "vsl"),"reaction_time"], center = T)
    rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "tsl"), "scaled_rt"] <- 
      scale(rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "tsl"),"reaction_time"], center = T)
    rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "ssl"), "scaled_rt"] <- 
      scale(rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "ssl"),"reaction_time"], center = T)
    
    # Using the first 3 target trials as baseline do not seem to be a very good idea; looking at the raw data the variances seem to be great among the first three trials:
    # firstThreeTrial <- sort(rt_trial_scaled[which(rt_trial_scaled$id == "blast_c_002" & rt_trial_scaled$task == "lsl"), "targ_index"])[1:3]
    # rt_trial_scaled[which(rt_trial_scaled$id == "blast_c_213" & rt_trial_scaled$targ_index %in% firstThreeTrial & rt_trial_scaled$task == "lsl"), ] 
}

# Add mean RT to by trial RT data
mean_rt <- allData[,c("part_id","lsl_rt", "vsl_rt", "tsl_rt", "ssl_rt")]
mean_rt <- melt(mean_rt, id.vars = ("part_id"))
colnames(mean_rt) <- c("part_id", "task", "mean_rt")
mean_rt$task <- gsub("_rt", "", mean_rt$task)
rt_trial_scaled <- merge(rt_trial_scaled, mean_rt, by.x = c("id", "task"), by.y = c("part_id", "task"), all.x = T)

hist(rt_trial_scaled$reaction_time)
hist(rt_trial_scaled$scaled_rt)
```


## SL Group Comparison RT: By Trial RT LMER
```{r}
rt_trial_scaled$reaction_time <- as.numeric(as.character(rt_trial_scaled$reaction_time))
rt_trial_scaled$id <- as.factor(rt_trial_scaled$id)
rt_trial_scaled$task <- as.factor(rt_trial_scaled$task)
rt_trial_scaled$targ_index <- as.numeric(as.character(rt_trial_scaled$targ_index))
rt_trial_scaled$mean_rt <- as.numeric(as.character(rt_trial_scaled$mean_rt))

rt_trial_scaled$group <- 
  factor(rt_trial_scaled$group,
         levels = c("ASD", 
                    "TD"))
rt_trial_scaled <- rt_trial_scaled[order(rt_trial_scaled$group), ]

rt_trial_scaled$domain <- 
  factor(rt_trial_scaled$domain,
         levels = c("nonling", 
                    "ling"))
rt_trial_scaled <- rt_trial_scaled[order(rt_trial_scaled$domain), ]

rt_trial_scaled$modality <- 
  factor(rt_trial_scaled$modality,
         levels = c("auditory", 
                    "visual"))
rt_trial_scaled <- rt_trial_scaled[order(rt_trial_scaled$modality), ]

head(rt_trial_scaled)
```

## RT Model:
```{r}
lmer_slope_m1 <-
  lmer(
    scaled_rt ~ group*targ_index*domain*modality + (1+domain+modality|id),
    # + (0 + (modality + domain) | id),
    data = rt_trial_scaled,
    contrasts = list(
      group = c(-0.5, 0.5),
      modality = c(-0.5, 0.5),
      domain = c(-0.5, 0.5)
    ),
    control=lmerControl(optimizer = "bobyqa")
  )
summary(lmer_slope_m1)

rtTrialModel <- summary(lmer_slope_m1)
rtTrialModel$coefficients <- round(rtTrialModel$coefficients, 2)
write.csv(as.data.frame(rtTrialModel$coefficients), "rtTrialModel.csv")
# Troubleshoot the model (no success):
# library(afex)
# all_fit(lmerrt_scaled_m1)
# print(lmerrt_scaled_m1, correlation=TRUE)
```

## Trying Other RT Models:
```{r}
# Using raw reaction time and controlling for mean reaction time (Scaling issues)
lmer_slope_m2 <-
  lmer(reaction_time~group*targ_index*domain*modality + mean_rt + (1+domain+modality| id),
       data = rt_trial_scaled,
       contrasts = list(group = c(-0.5,0.5),
                        modality = c(-0.5, 0.5),
                        domain = c(-0.5, 0.5))
      )

summary(lmer_slope_m2)
```

## SL Group Comparison RT: Follow-up on four-way interaction (diagnostic group x trial order x domain x modality)
```{r}
rt_trial_scaledLING <- rt_trial_scaled[which(rt_trial_scaled$domain == "ling"),]
rt_trial_scaledNonling <- rt_trial_scaled[which(rt_trial_scaled$domain == "nonling"),]

lmer_slopeLING <-
  lmer(scaled_rt~group*targ_index*modality + (1+modality|id),
       data = rt_trial_scaledLING,
       contrasts = list(group = c(-1,1),
                        modality = c(-1, 1)),
       control=lmerControl(optimizer = "bobyqa"))

summary(lmer_slopeLING)

rtTrialLingModel <- summary(lmer_slopeLING)
rtTrialLingModel$coefficients <- round(rtTrialLingModel$coefficients, 2)
write.csv(as.data.frame(rtTrialLingModel$coefficients), "rtTrialLingModel.csv")

lmer_slopeNonling <-
  lmer(scaled_rt~group*targ_index*modality + (1+modality|id),
       data = rt_trial_scaledNonling,
       contrasts = list(group = c(-1,1),
                        modality = c(-1, 1)),
       control=lmerControl(optimizer = "bobyqa"))

summary(lmer_slopeNonling)

rtTrialNonlingModel <- summary(lmer_slopeNonling)
rtTrialNonlingModel$coefficients <- round(rtTrialNonlingModel$coefficients, 2)
write.csv(as.data.frame(rtTrialNonlingModel$coefficients), "rtTrialNonlingModel.csv")
```

## SL Group Comparison RT Slope: Post-hoc T-tests TD vs. ASD
```{r}
t_test_multi_pair_slope <- 
  function(x,y){
  test <- t.test(x, y, alternative = "less")

  data.frame(p_value = test$p.value,
             df = test$parameter,
             t_stat = test$statistic)
  }

# RT slope
sapply(intersect(colnames(allData_td),colnames(allData_asd))[c(16:19)], 
                 function(x) t_test_multi_pair_slope(allData_td[,x], allData_asd[,x]))
```


# Section 3: SL Group Comparison Accuracy 

## Preprocess SL data: Extract data for each measure (accuracy, slope, mean rt) and add domain and modality
```{r, include = F}
extract_measure_child <-
function(df, taskCol) {
  df <- 
    allData[,which(str_detect(
      colnames(allData), paste0("part_id|group|age_at_web_year|", taskCol)))]
  
  df <- melt(df, id.vars = c("part_id", "group", "age_at_web_year"))
  
  colnames(df)[colnames(df) == "variable"] <- "task"
  colnames(df)[colnames(df) == "value"] <- taskCol
  
  return(df)
}

allData_acc <- extract_measure_child(allData_acc, "acc")
allData_slope <- extract_measure_child(allData_slope, "slope")
allData_rt <- extract_measure_child(allData_rt, "rt")

colnames(allData_acc)[colnames(allData_acc) == "acc"] <- "accuracy"
colnames(allData_rt)[colnames(allData_rt) == "rt"] <- "mean_rt"
colnames(allData_slope)[colnames(allData_slope) == "slope"] <- "rt_slope"

# Add modality and domain category to long-format data
allData_acc <- add_dom_mod_func(allData_acc)
allData_rt <- add_dom_mod_func(allData_rt)
allData_slope <- add_dom_mod_func(allData_slope)
```

## SL against chance for TD and ASD
```{r}
t_test_against_chance <- 
  function(x){
  test <- t.test(x, mu=0.5, alternative= "greater")
  data.frame(p_value = test$p.value,
             df = test$parameter,
             t_stat = test$statistic)
  }

#TD
sapply(colnames(allData_td)[c(7:10)], 
       function(x) t_test_against_chance(allData_td[,x]))

#ASD
sapply(colnames(allData_asd)[c(7:10)], 
       function(x) t_test_against_chance(allData_asd[,x]))

t_test_against_zero <- 
  function(x){
  test <- t.test(x, mu=0, alternative= "less")
  data.frame(p_value = test$p.value,
             df = test$parameter,
             t_stat = test$statistic)
  }

#TD
sapply(colnames(allData_td)[c(16:19)], 
       function(x) t_test_against_zero(allData_td[,x]))

#ASD
sapply(colnames(allData_asd)[c(16:19)], 
       function(x) t_test_against_zero(allData_asd[,x]))
```

## SL Group Comparison Accuracy: By Trial Accuracy GLMER
```{r}
acc_trial <- read.csv("acc_trial.csv")

acc_trial$task <- as.factor(acc_trial$task)
acc_trial$subj <- as.factor(acc_trial$subj)
acc_trial$age_at_web_year <- as.numeric(as.character(acc_trial$age_at_web_year))

acc_trial$group <- 
  factor(acc_trial$group,
         levels = c("ASD", 
                    "TD"))
acc_trial <- acc_trial[order(acc_trial$group),]

acc_trial$domain <- 
  factor(acc_trial$domain,
         levels = c("nonling", 
                    "ling"))
acc_trial <- acc_trial[order(acc_trial$domain),]

acc_trial$modality <- 
  factor(acc_trial$modality,
         levels = c("auditory", 
                    "visual"))
acc_trial <- acc_trial[order(acc_trial$modality),]

head(acc_trial)
```

```{r}
logacc_dom <-
  glmer(corr~group*domain*modality + (1+domain+modality|subj), data = acc_trial,
    family = binomial,
    contrasts = list(domain = c(-0.5, 0.5), modality = c(-0.5, 0.5), group = c(-0.5,0.5)),
    control=glmerControl(optimizer = "bobyqa"))

summary(logacc_dom)

accModel <- summary(logacc_dom)
accModel <- round(accModel$coefficients, 2)
write.csv(as.data.frame(accModel), "accModel.csv")
```

## SL Group Comparison Accuracy: Post-hoc T-test TD vs. ASD
```{r}
t_test_multi_pair <- 
  function(x,y){
  test <- t.test(x, y, alternative = "greater")

  data.frame(p_value = test$p.value,
             df = test$parameter,
             t_stat = test$statistic)
  }

# Accuracy
sapply(intersect(colnames(allData_td),colnames(allData_asd))[c(7:10)], 
                 function(x) t_test_multi_pair(allData_td[,x], allData_asd[,x]))
```



# Section 4: SL Group Comparison Composite Scores 

## Preprocess and calculate composite scores
```{r}
compositeAge <- allData
# Scale RT slopes across participants for each task
compositeAge[, c("lsl_slopeScaled", "ssl_slopeScaled","vsl_slopeScaled", "tsl_slopeScaled")] <-
  lapply(compositeAge[, c("lsl_slope", "ssl_slope","vsl_slope", "tsl_slope")], 
         function(x) {
           scale(0 - x, center = T)
           })
# Scale percentage correct across participants for each task
compositeAge[, c("lsl_accScaled", "ssl_accScaled","vsl_accScaled", "tsl_accScaled")] <-
  lapply(compositeAge[, c("lsl_acc", "ssl_acc","vsl_acc", "tsl_acc")], 
         function(x) {
           scale(x, center = T)
           })
# Calculate composite scores
sumComposite <- function(taskCol, nCol, column_list) {
  # Step 1: Sum the relevant scaled RT slopes and scaled percentage correct columns
  compositeAge[, taskCol] <-
    rowSums(compositeAge[, column_list], na.rm = T)
  # Step 2: Count the number of non-NA values out of the relevant scaled RT slopes and scaled percentage correct columns
  compositeAge[, nCol] <-
    apply(compositeAge[column_list], 1, function(x) {
      sum(!is.na(x))
    })
  # Calcualte the mean composite scores (Step 1 / Step 2)
  compositeAge[, taskCol] <-
    compositeAge[, taskCol] / compositeAge[, nCol]
  
  return(compositeAge)
}
# Linguistic SL composite score
compositeAge <-
  sumComposite("composite_ling", "completeN_ling", 
               c("lsl_accScaled", "ssl_accScaled", 
                 "lsl_slopeScaled", "ssl_slopeScaled"))
# Nonlinguistic SL composite score
compositeAge <-
  sumComposite("composite_nonling", "completeN_nonling", 
               c("vsl_accScaled", "tsl_accScaled", 
                 "vsl_slopeScaled", "tsl_slopeScaled"))
# Letter SL composite score
compositeAge <-
  sumComposite("composite_lsl", "completeN_lsl", 
               c("lsl_accScaled", "lsl_slopeScaled"))
# Syllable SL composite score
compositeAge <-
  sumComposite("composite_ssl", "completeN_ssl", 
               c("ssl_accScaled", "ssl_slopeScaled"))
# Image SL composite score
compositeAge <-
  sumComposite("composite_vsl", "completeN_vsl", 
               c("vsl_accScaled", "vsl_slopeScaled"))
# Tone SL composite score
compositeAge <-
  sumComposite("composite_tsl", "completeN_tsl", 
               c("tsl_accScaled", "tsl_slopeScaled"))

```

## Descriptive stats of accuracy and RT slopes (in all participants, or Younger and Older age groups)
```{r}
compositeAge <- compositeAge

getDescripStat <- function(group, col) {
  compositeAge %>%
      group_by(!!as.symbol(group)) %>%
      dplyr::summarise(mean = mean((!!as.symbol(col)), na.rm = TRUE),
                sd = sd((!!as.symbol(col)), na.rm = TRUE),
                n = n()) %>%
      mutate(se = sd / sqrt(n),
             lower_ci = mean - qt(1 - (0.05 / 2), n - 1) * se,
             upper_ci = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
      select(!!as.symbol(group), mean, lower_ci, upper_ci) %>%
    slice(match(c("TD", "ASD"), group))
}

getDescripStat("group", "lsl_acc")
getDescripStat("group", "ssl_acc")
getDescripStat("group", "vsl_acc")
getDescripStat("group", "tsl_acc")

getDescripStat("group", "lsl_slope")
getDescripStat("group", "ssl_slope")
getDescripStat("group", "vsl_slope")
getDescripStat("group", "tsl_slope")

getDescripStat("group", "composite_lsl")
getDescripStat("group", "composite_ssl")
getDescripStat("group", "composite_vsl")
getDescripStat("group", "composite_tsl")

# getDescripStat("age_group", "composite_ling")
# getDescripStat("age_group", "composite_nonling")
```

## SL Group Comparison Composite: SL Composite Scores LMER
```{r}
compositeGroup <-
  compositeAge[, c(
    "part_id",
    "group",
    "gender",
    "age_at_web_month",
    "age_at_web_year",
    "composite_lsl",
    "composite_ssl",
    "composite_vsl",
    "composite_tsl")]

compositeGroupL <-
  melt(
    compositeGroup,
    id.vars = c(
      "part_id",
      "group",
      "gender",
      "age_at_web_month",
      "age_at_web_year"))

colnames(compositeGroupL)[colnames(compositeGroupL) %in% c("variable", "value")] <- c("task", "composite_score")
compositeGroupL <- add_dom_mod_func(compositeGroupL)
compositeGroupL$task <- as.factor(compositeGroupL$task)
compositeGroupL$part_id <- as.factor(compositeGroupL$part_id)
compositeGroupL$age_at_web_month <- as.numeric(as.character(compositeGroupL$age_at_web_month))
compositeGroupL$composite_score <- as.numeric(as.character(compositeGroupL$composite_score))

compositeGroupL$group <-
  factor(compositeGroupL$group,
         levels = c("ASD",
                    "TD"))
compositeGroupL <- compositeGroupL[order(compositeGroupL$group),]

compositeGroupL$domain <-
  factor(compositeGroupL$domain,
         levels = c("nonling",
                    "ling"))
compositeGroupL <- compositeGroupL[order(compositeGroupL$domain),]

compositeGroupL$modality <-
  factor(compositeGroupL$modality,
         levels = c("auditory",
                    "visual"))
compositeGroupL <- compositeGroupL[order(compositeGroupL$modality),]

head(compositeGroupL)
```

```{r}
composite_m1 <-
  lmer(composite_score ~ group*domain*modality + (1+domain+modality|part_id),
       data = compositeGroupL,
       contrasts = list(domain = c(-0.5, 0.5), modality = c(-0.5, 0.5), group = c(-0.5, 0.5)))
summary(composite_m1)

compositeModel <- summary(composite_m1)
compositeModel <- round(compositeModel$coefficients, 2)
write.csv(as.data.frame(compositeModel), "compositeModel.csv")
``` 

## SL Group Comparison Composite: Post-hoc T-test TD vs. ASD
```{r}
compositeGroupTD <- compositeGroup[which(compositeGroup$group == "TD"),]
compositeGroupASD <- compositeGroup[which(compositeGroup$group == "ASD"),]

# one-tailed t-test TD > ASD
sapply(intersect(colnames(compositeGroupTD),colnames(compositeGroupASD))[6:9], 
                 function(x) t_test_multi_pair(compositeGroupTD[,x], compositeGroupASD[,x]))
```



# Section 5: SL Cross-sectional Development Analyses

## Preprocess: scale age and re-scale SL composite scores
```{r}
# IMPORTANT: Scale age so that age is on the same scale as composite scores
compositeAge$age_scaled <- scale(compositeAge$age_at_web_year, center = T)
# Regenerate a long data frame with GJT and composite scores across domains
compositeAgeL <-
  melt(
    compositeAge[, c(
      "part_id",
      "group",
      "age_at_web_month",
      "age_at_web_year",
      "age_scaled",
      "a_prime",
      "scq_web",
      "rbs_r",
      "composite_nonling",
      "composite_ling"
    )],
    id.vars = c(
      "part_id",
      "group",
      "age_at_web_month",
      "age_at_web_year",
      "age_scaled",
      "a_prime",
      "scq_web",
      "rbs_r"
    )
  )

colnames(compositeAgeL)[which(colnames(compositeAgeL) == "variable")] <- "domain"
colnames(compositeAgeL)[which(colnames(compositeAgeL) == "value")] <- "composite_score"
```

## SL Cross-sectional Development Analyses: Continous Age and Composite Scores LMER
```{r}
compositeAgeL$domain <- as.factor(compositeAgeL$domain)
compositeAgeL$group <- as.factor(compositeAgeL$group)
compositeAgeL$age_scaled <- as.numeric(as.character((compositeAgeL$age_scaled)))

nCount <-
compositeAgeL %>%
  group_by(part_id) %>%
  dplyr::summarise(n = n())

which(nCount$n == 1)
# Every participant has a linguistic and a nonlinguistic composite score

compositeAgeL$domain <-
  factor(compositeAgeL$domain,
         levels = c("composite_nonling", "composite_ling"))
compositeAgeL <- compositeAgeL[order(compositeAgeL$domain), ]

compositeAgeL$group <-
  factor(compositeAgeL$group, levels = c("ASD", "TD"))
compositeAgeL <- compositeAgeL[order(compositeAgeL$group), ]

# Save non-scaled composite scores for other analyses
compositeAgeLNscaled <- compositeAgeL
hist(compositeAgeLNscaled$composite_score)

# Rescaling the composite score so that age and compsite scores are on the same scale; no scaling of composite scores yields similar model results with different estimates
compositeAgeL$composite_score <- scale(compositeAgeL$composite_score)
hist(compositeAgeL$composite_score)

age_composite_m1 <- 
  lmer(composite_score ~ group*domain*age_scaled + (1|part_id),  
       data = compositeAgeL,
      contrasts = list(domain = c(-0.5, 0.5),
                       group = c(-0.5, 0.5))
     )
summary(age_composite_m1)

ageCompositeModel <- summary(age_composite_m1)
ageCompositeModel <- round(ageCompositeModel$coefficients, 2)
write.csv(ageCompositeModel, "ageCompositeModel.csv")
```

## Assign age groups
```{r}
compositeAge <- compositeAge[order(compositeAge$age_at_web_month),]
# hist(compositeAge$age_at_web_year)

# Median split of age across all the participants
compositeAge[1:round(length(compositeAge$age_at_web_month)/2),"age_group"] <- "Younger"
compositeAge[which(compositeAge$group == "TD" & compositeAge$age_group == "Younger"), "age_group"] <- "Younger TD"
compositeAge[which(compositeAge$group == "ASD" & compositeAge$age_group == "Younger"), "age_group"] <- "Younger ASD"

median <- round((length(compositeAge$age_at_web_month)/2))+1
compositeAge[median:length(compositeAge$age_at_web_month),"age_group"] <- "Older"
compositeAge[which(compositeAge$group == "TD" & compositeAge$age_group == "Older"), "age_group"] <- "Older TD"
compositeAge[which(compositeAge$group == "ASD" & compositeAge$age_group == "Older"), "age_group"] <- "Older ASD"

compositeAge$ageSplit <- str_extract(compositeAge$age_group, "Young|Old")

# Mean split of age in each diagnostic group

# compositeAgeTD[which(compositeAgeTD$age_at_web_month < mean(compositeAgeTD$age_at_web_month)),"age_group"] <- "Younger TD"
# compositeAgeTD[which(compositeAgeTD$age_at_web_month > mean(compositeAgeTD$age_at_web_month)),"age_group"] <- "Older TD"
# compositeAgeASD[which(compositeAgeASD$age_at_web_month < mean(compositeAgeASD$age_at_web_month)),"age_group"] <- "Younger ASD"
# compositeAgeASD[which(compositeAgeASD$age_at_web_month > mean(compositeAgeASD$age_at_web_month)),"age_group"] <- "Older ASD"

# Check children younger than 6.5's accuracy (compared to Arnon's results)
# compositeAge[which(compositeAge$age_at_web_year < 6.5 & compositeAge$group == "TD"), "ssl_acc"]
```

## Age stats in Younger and Older age groups
```{r}
library(reshape2)
age_wide <- dcast(compositeAge, group~ageSplit, length)
print(age_wide)
# print(chisq.test(age_wide))

compositeAge %>%
    group_by(ageSplit) %>%
    dplyr::summarise(mean_age_month = mean(age_at_web_month), mean_age_year = round(mean(age_at_web_year),2), sd = sd(age_at_web_year), n = n())


oldYoungAge <- 
  compositeAge %>%
    group_by(group, ageSplit) %>%
    dplyr::summarise(mean_age_month = mean(age_at_web_month), mean_age_year = mean(age_at_web_year), sd = sd(age_at_web_year), n = n())

oldYoungAge[, -c(1:2)] <- round(oldYoungAge[, -c(1:2)], 2)

print(oldYoungAge)

compositeAgeTD <- compositeAge[which(compositeAge$group == "TD"),]
compositeAgeASD <- compositeAge[which(compositeAge$group == "ASD"),]

compositeAgeTDY <- compositeAgeTD[which(compositeAgeTD$ageSplit == "Young"),]
compositeAgeTDO <- compositeAgeTD[which(compositeAgeTD$ageSplit == "Old"),]

compositeAgeASDY <- compositeAgeASD[which(compositeAgeASD$ageSplit == "Young"),]
compositeAgeASDO <- compositeAgeASD[which(compositeAgeASD$ageSplit == "Old"),]

t.test(compositeAgeTDY$age_at_web_year, compositeAgeASDY$age_at_web_year)
t.test(compositeAgeTDO$age_at_web_year, compositeAgeASDO$age_at_web_year)
```

## SL Cross-sectional Development Analyses: Follow-up in Younger and Older age groups
```{r}
compositeAgeLNscaled <- merge(compositeAgeLNscaled, compositeAge[,c("part_id", "age_group", "ageSplit")], by.x = "part_id", by.y = "part_id", all.x = T)
compositeYoungL <- compositeAgeLNscaled[which(compositeAgeLNscaled$ageSplit == "Young"),]
compositeOldL <- compositeAgeLNscaled[which(compositeAgeLNscaled$ageSplit == "Old"),]

compositeAgeLNscaled$ageSplit <- as.factor(compositeAgeLNscaled$ageSplit)

compositeAgeLNscaled$ageSplit <-
  factor(compositeAgeLNscaled$ageSplit, levels = c("Young", "Old"))
compositeAgeLNscaled <- compositeAgeLNscaled[order(compositeAgeLNscaled$ageSplit),]

compositeAgeLNscaled$domain <-
  factor(compositeAgeLNscaled$domain,
         levels = c("composite_nonling", "composite_ling"))
compositeAgeLNscaled <- compositeAgeLNscaled[order(compositeAgeLNscaled$domain),]

compositeAgeLNscaled$group <-
  factor(compositeAgeLNscaled$group,
         levels = c("ASD", "TD"))
compositeAgeLNscaled <- compositeAgeLNscaled[order(compositeAgeLNscaled$group),]

head(compositeAgeLNscaled)
```
## SL Cross-sectional Development Analyses:
```{r}
# Rescaling in each age group:
compositeOldL <- compositeAgeLNscaled[which(compositeAgeLNscaled$ageSplit == "Old"),]
compositeOldL$composite_score <- scale(compositeOldL$composite_score)

# Rescaling in each age group:
compositeYoungL <- compositeAgeLNscaled[which(compositeAgeLNscaled$ageSplit == "Young"),]
compositeYoungL$composite_score <- scale(compositeYoungL$composite_score)

# Younger group
age_composite_m3 <- 
  lmer(composite_score ~ group*domain + (1|part_id),  
       data = compositeYoungL,
     contrasts = list(domain = c(-0.5, 0.5),
                      group = c(-0.5, 0.5))
     )

summary(age_composite_m3)

# all_fit(age_composite_m3)

ageCompositeYoungModel <- summary(age_composite_m3)
ageCompositeYoungModel <- round(ageCompositeYoungModel$coefficients, 2)
write.csv(ageCompositeYoungModel, "ageCompositeYoungModel.csv")


age_composite_m2 <- 
  lmer(composite_score ~ group*domain + (1|part_id),  
       data = compositeOldL,
     contrasts = list(domain = c(-0.5, 0.5),
                  group = c(-0.5, 0.5))
     )

summary(age_composite_m2)

ageCompositeOldModel <- summary(age_composite_m2)
ageCompositeOldModel <- round(ageCompositeOldModel$coefficients, 2)
write.csv(ageCompositeOldModel, "ageCompositeOldModel.csv")
```


## SL Cross-sectional Development Analyses: Post-hoc t-test of Linguistic and Nonlinguistic SL Composite Scores in older children
```{r}
# Older group linguistic:
t.test(compositeAgeTDO$composite_ling, compositeAgeASDO$composite_ling)
# Older group nonlinguistic
t.test(compositeAgeTDO$composite_nonling, compositeAgeASDO$composite_nonling)
```



# Section 6: Task Correlation analyses

## Preprocess: re-scale SL composite scores in each task
```{r}
mulregScaled <- compositeAge[,c("part_id", "group", "age_at_web_month", "age_at_web_year", "age_scaled", "a_prime",
                               "scq_web", "rbs_r", "composite_ling", "composite_nonling", "ageSplit",
                              "composite_lsl", "composite_ssl","composite_tsl", "composite_vsl")]

# Scale the data 
mulregScaled[, c("composite_lsl", "composite_ssl","composite_tsl", "composite_vsl")] <-
  lapply(mulregScaled[, c("composite_lsl", "composite_ssl","composite_tsl", "composite_vsl")], 
         function(x) {
           scale(x, center = T)
           })
```

## Planned Letter and Syllable SL analyses: Compare composite LSL and composite SSL relationship based on Age
```{r}
mulregScaled$ageSplit <- 
  factor(mulregScaled$ageSplit,levels = c("Young", "Old"))
mulregScaled <- mulregScaled[order(mulregScaled$ageSplit),]

mulregScaled$group <- 
  factor(mulregScaled$group,levels = c("ASD", "TD"))
mulregScaled <- mulregScaled[order(mulregScaled$group),]

head(mulregScaled)
```

```{r}
compositeCorr_m1 <- lm(composite_lsl ~ group*ageSplit*composite_ssl, data = mulregScaled,
                      contrasts = list( 
                      group = c(-0.5, 0.5),
                      ageSplit = c(-0.5, 0.5)))

summary(compositeCorr_m1)

compositeCorrModel <- summary(compositeCorr_m1)
compositeCorrModel <- compositeCorrModel$coefficients
compositeCorrModel <- round(compositeCorrModel, 2)
write.csv(compositeCorrModel, "compositeCorrModel.csv")

# When age was fit as a continous variable:
compositeCorr_m2 <- lm(composite_lsl ~ group*age_scaled*composite_ssl, data = mulregScaled,
                      contrasts = list( 
                      group = c(-0.5, 0.5)
                      ))

summary(compositeCorr_m2)
```


## Follow-up on Letter and Syllable Letter and Syllable SL analyses: composite LSL and composite SSL relationship in each age group
```{r}
mulregScaledY <- mulregScaled[which(mulregScaled$ageSplit == "Young"),]
mulregScaledO <- mulregScaled[which(mulregScaled$ageSplit == "Old"),]

# Fitting the not re-scaled composite SL scores also did not change the results:
compositeCorr_m3 <- lm(composite_lsl ~ group*composite_ssl, data = mulregScaledY,
                      contrasts = list( 
                      group = c(-0.5, 0.5)))

summary(compositeCorr_m3)

compositeCorrYoungModel <- summary(compositeCorr_m3)
compositeCorrYoungModel <- compositeCorrYoungModel$coefficients
compositeCorrYoungModel <- round(compositeCorrYoungModel, 2)
write.csv(compositeCorrYoungModel, "compositeCorrYoungModel.csv")

compositeCorr_m4 <- lm(composite_lsl ~ group*composite_ssl, data = mulregScaledO,
                      contrasts = list( 
                      group = c(-0.5, 0.5)))

summary(compositeCorr_m4)

compositeCorrOldModel <- summary(compositeCorr_m4)
compositeCorrOldModel <- compositeCorrOldModel$coefficients
compositeCorrOldModel <- round(compositeCorrOldModel, 2)
write.csv(compositeCorrOldModel, "compositeOldCorrModel.csv")
```

## Follow-up on Letter and Syllable SL analyses: Extract Pearson's R between composite LSL and composite SSL in each age group 
```{r} 
getCorrCI <- 
  function(df, group, age, col1, col2) {
      corTestDF <- cor.test(df[,c(col1)], df[,c(col2)])
      pearsonr <- corTestDF$estimate
      ci_upper <- corTestDF$conf.int[1]
      ci_lower <- corTestDF$conf.int[2]
      p_value <- corTestDF$p.value
      n <- corTestDF$parameter + 2
      
      tempDF <- data.frame(cbind(pearsonr, ci_upper, ci_lower, p_value, n))
      
      tempDF$Group <- group
      tempDF$Age <- age
      
      return(tempDF)
  }

lingCorrTDY <- getCorrCI(compositeAgeTDY, "TD", "Young", "composite_lsl", "composite_ssl")
lingCorrTDO <- getCorrCI(compositeAgeTDO, "TD", "Old", "composite_lsl", "composite_ssl")
lingCorrASDY <- getCorrCI(compositeAgeASDY, "ASD", "Young", "composite_lsl", "composite_ssl")
lingCorrASDO <- getCorrCI(compositeAgeASDO, "ASD", "Old", "composite_lsl", "composite_ssl")

lingCorr <- rbind(lingCorrTDY, lingCorrTDO, lingCorrASDY, lingCorrASDO)
# two-tailed p values
print(lingCorr)
```

## Follow-up on Letter and Syllable SL analyses: Simple correlation comparison on composite LSL and SSL relationship in TD vs. ASD
```{r}
library(cocor)

# Compare Linguistic SL composite scores between young TD and young ASD
cocor.indep.groups(r1.jk=lingCorr[which(lingCorr$Group == "TD" & lingCorr$Age == "Young"), "pearsonr"], 
                   r2.hm=lingCorr[which(lingCorr$Group == "ASD" & lingCorr$Age == "Young"), "pearsonr"], 
                   n1=lingCorr[which(lingCorr$Group == "TD" & lingCorr$Age == "Young"), "n"], 
                   n2=lingCorr[which(lingCorr$Group == "ASD" & lingCorr$Age == "Young"), "n"], 
                   alternative="two.sided", alpha=0.05, conf.level=0.95, null.value=0)
# Compare Linguistic SL composite scores between old TD and old ASD
cocor.indep.groups(r1.jk=lingCorr[which(lingCorr$Group == "TD" & lingCorr$Age == "Old"), "pearsonr"], 
                   r2.hm=lingCorr[which(lingCorr$Group == "ASD" & lingCorr$Age == "Old"), "pearsonr"], 
                   n1=lingCorr[which(lingCorr$Group == "TD" & lingCorr$Age == "Old"), "n"], 
                   n2=lingCorr[which(lingCorr$Group == "ASD" & lingCorr$Age == "Old"), "n"], 
                   alternative="two.sided", alpha=0.05, conf.level=0.95, null.value=0)
```

## Planned Letter and Image SL analyses: Compare composite LSL and composite VSL relationship based on Age
```{r}
compositeCorr_m3 <- lm(composite_lsl ~ group*ageSplit*composite_vsl, data = mulregScaled,
                      contrasts = list( 
                      group = c(-0.5, 0.5),
                      ageSplit = c(-0.5, 0.5)))

summary(compositeCorr_m3)

# When age was fit as a continous variable:
compositeCorr_m4 <- lm(composite_lsl ~ group*age_scaled*composite_vsl, data = mulregScaled,
                      contrasts = list( 
                      group = c(-0.5, 0.5)
                      ))

summary(compositeCorr_m4)
```

## Planned Analyses: Extract task correlations across all age
```{r}
getCorrComposite <-
function(df, group, age, task, col1, col2) {
      corTestDF <- cor.test(df[,c(col1)], df[,c(col2)])
      pearsonr <- corTestDF$estimate
      ci_upper <- corTestDF$conf.int[1]
      ci_lower <- corTestDF$conf.int[2]
      p_value <- corTestDF$p.value
      n <- corTestDF$parameter + 2
      
      tempDF <- data.frame(cbind(pearsonr, ci_upper, ci_lower, p_value, n))
      
      tempDF$Group <- group
      tempDF$Age <- age
      tempDF$Task <- task
      
      return(tempDF)
  }

lingCorrTDlsl_ssl <- getCorrComposite(compositeAgeTD, "TD", "all_age", "lsl_ssl", "composite_lsl", "composite_ssl")
lingCorrASDlsl_ssl <- getCorrComposite(compositeAgeASD, "ASD", "all_age", "lsl_ssl", "composite_lsl", "composite_ssl")
lingCorrTDlsl_vsl <- getCorrComposite(compositeAgeTD, "TD", "all_age", "lsl_vsl", "composite_lsl", "composite_vsl")
lingCorrASDlsl_vsl <- getCorrComposite(compositeAgeASD, "ASD", "all_age", "lsl_vsl", "composite_lsl", "composite_vsl")

lingCorrLSL <- rbind(lingCorrTDlsl_ssl, lingCorrASDlsl_ssl, lingCorrTDlsl_vsl, lingCorrASDlsl_vsl)

print(lingCorrLSL)

cor.test(compositeAgeTD$composite_lsl, compositeAgeTD$composite_vsl)
cor.test(compositeAgeTD$composite_lsl, compositeAgeTD$composite_ssl)
```


## Follow-up on Letter and Syllable SL analyses: Simple correlation comparison on composite LSL and SSL relationship in TD vs. ASD
```{r}
# Compare composite LSL/ SSL correlations between TD and ASD
cocor.indep.groups(r1.jk=lingCorrLSL[which(lingCorrLSL$Group == "TD" & lingCorrLSL$Task == "lsl_ssl"), "pearsonr"], 
                   r2.hm=lingCorrLSL[which(lingCorrLSL$Group == "ASD" & lingCorrLSL$Task == "lsl_ssl"), "pearsonr"], 
                   n1=lingCorrLSL[which(lingCorrLSL$Group == "TD" & lingCorrLSL$Task == "lsl_ssl"), "n"], 
                   n2=lingCorrLSL[which(lingCorrLSL$Group == "ASD" & lingCorrLSL$Task == "lsl_ssl"), "n"], 
                   alternative="two.sided", alpha=0.05, conf.level=0.95, null.value=0)
```

## Follow-up on Letter and Image SL analyses: Simple correlation comparison on composite LSL and VSL relationship in TD vs. ASD
```{r}
# Compare composite LSL/ SSL correlations between TD and ASD
cocor.indep.groups(r1.jk=lingCorrLSL[which(lingCorrLSL$Group == "TD" & lingCorrLSL$Task == "lsl_vsl"), "pearsonr"], 
                   r2.hm=lingCorrLSL[which(lingCorrLSL$Group == "ASD" & lingCorrLSL$Task == "lsl_vsl"), "pearsonr"], 
                   n1=lingCorrLSL[which(lingCorrLSL$Group == "TD" & lingCorrLSL$Task == "lsl_vsl"), "n"], 
                   n2=lingCorrLSL[which(lingCorrLSL$Group == "ASD" & lingCorrLSL$Task == "lsl_vsl"), "n"], 
                   alternative="two.sided", alpha=0.05, conf.level=0.95, null.value=0)
```


# Section 8: Prep Plotting

## Letter and Syllable SL analyses: Plot Letter and Syllable SL Composite Scores Correlation in each age group
```{r}
library("dplyr")
library("TeachingDemos")
library("ggpattern")
library("ggplot2")

cbPalette <- c('#a6cee3','#1f78b4','#b2df8a', '#66c2a5','#fc8d62','#8da0cb', '#1b9e77','#d95f02','#7570b3')
cbPaletteGrey <- col2grey(cbPalette)

labs <- c("Younger Children", "Older Children")
names(labs) <- c("Young", "Old")

lingCorr %>%
  ggplot(aes(
    x = Group,
    y = pearsonr,
    ymin = ci_lower,
    ymax = ci_upper,
    fill = Group
  )) +
  geom_bar(stat = "identity",
           position = position_dodge(),
           width = 0.9) +
  facet_wrap("Age", labeller = (labeller(Age = labs))) +
  geom_col_pattern(color = "black",
                   pattern = "null") +
  scale_fill_manual(values = c(cbPalette[1], cbPalette[8])) +
  geom_errorbar(width = .1, position = position_dodge(width = 0.9)) +
  labs(title = "Relationship between Letter and Syllable SL Composite Scores",
       x = "Group",  # Change x-axis label
       y = "Pearson's Correlation Estimate") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
    plot.title = element_text(size = 29, face = "bold"),
    axis.title.x = element_text(size = 26, face = "bold"),
    axis.title.y = element_text(size = 22, face = "bold"),
    axis.text = element_text(size = 24, face = "bold"),
    legend.text = element_text(size = 22, face = "bold"),
    legend.title = element_text(size = 22, face = "bold")
  ) +
  theme(
    panel.background = element_rect(fill = "white"),
    # Set plot background to white
    legend.key  = element_rect(fill = "white"),
    # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),
    # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1),
    # Add line to y axis
    strip.text = element_text(size = 24, face = "bold"),
    # Change facet text
    strip.background = element_rect(fill = "white", size = 1),
    # Change facet color
    panel.spacing = unit(.05, "lines"),
    # Add panel border
    panel.border = element_rect(color = "black", fill = NA, size = 0.5),
    # Change panel border color and size
    legend.position = c(0.064, 0.88),
    legend.background = element_rect(fill = "#ffffff00")
    # strip.text = element_blank()
  ) +
  geom_text(
    size = 14,
    color = "black",
    data = data.frame(
      Group = "TD",
      pearsonr = 0.55,
      Age = "Old",
      ci_upper = 0,
      ci_lower = 0,
      Domain = 0
    ),
    aes(x = 1.5, y = 0.85, label = paste0("*"))
  ) +
  geom_segment(
    aes(
      x = 1,
      xend = 2,
      y = 0.85,
      yend = 0.85
    ),
    data = data.frame(
      Group = "TD",
      pearsonr = 0.55,
      Age = "Old",
      ci_upper = 0,
      ci_lower = 0,
      Domain = 0
    )
  ) +
  geom_segment(
    aes(
      x = 1,
      xend = 2,
      y = 0.85,
      yend = 0.85
    ),
    data = data.frame(
      Group = "TD",
      pearsonr = 0.55,
      Age = "Old",
      ci_upper = 0,
      ci_lower = 0,
      Domain = 0
    )
  )

# ggsave("composite_lsl_ssl.png",
#         bg="transparent", width = 26, height = 15, units = "cm")
```


## Accuracy Line Plot (no outliers)
## Preprocess: set up within subject standard error function
```{r}
summarySEwithin <- function(data=NULL, measurevar, betweenvars=NULL, withinvars=NULL,
                            idvar=NULL, na.rm=FALSE, conf.interval=.95, .drop=TRUE) {

  # Ensure that the betweenvars and withinvars are factors
  factorvars <- vapply(data[, c(betweenvars, withinvars), drop=FALSE],
    FUN=is.factor, FUN.VALUE=logical(1))

  if (!all(factorvars)) {
    nonfactorvars <- names(factorvars)[!factorvars]
    message("Automatically converting the following non-factors to factors: ",
            paste(nonfactorvars, collapse = ", "))
    data[nonfactorvars] <- lapply(data[nonfactorvars], factor)
  }

  # Get the means from the un-normed data
  datac <- summarySE(data, measurevar, groupvars=c(betweenvars, withinvars),
                     na.rm=na.rm, conf.interval=conf.interval, .drop=.drop)

  # Drop all the unused columns (these will be calculated with normed data)
  datac$sd <- NULL
  datac$se <- NULL
  datac$ci <- NULL

  # Norm each subject's data
  ndata <- normDataWithin(data, idvar, measurevar, betweenvars, na.rm, .drop=.drop)

  # This is the name of the new column
  measurevar_n <- paste(measurevar, "_norm", sep="")

  # Collapse the normed data - now we can treat between and within vars the same
  ndatac <- summarySE(ndata, measurevar_n, groupvars=c(betweenvars, withinvars),
                      na.rm=na.rm, conf.interval=conf.interval, .drop=.drop)

  # Apply correction from Morey (2008) to the standard error and confidence interval
  #  Get the product of the number of conditions of within-S variables
  nWithinGroups    <- prod(vapply(ndatac[,withinvars, drop=FALSE], FUN=nlevels,
                           FUN.VALUE=numeric(1)))
  correctionFactor <- sqrt( nWithinGroups / (nWithinGroups-1) )

  # Apply the correction factor
  ndatac$sd <- ndatac$sd * correctionFactor
  ndatac$se <- ndatac$se * correctionFactor
  ndatac$ci <- ndatac$ci * correctionFactor

  # Combine the un-normed means with the normed results
  merge(datac, ndatac)
}

summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
    library(plyr)

    # New version of length which can handle NA's: if na.rm==T, don't count them
    length2 <- function (x, na.rm=FALSE) {
        if (na.rm) sum(!is.na(x))
        else       length(x)
    }

    # This does the summary. For each group's data frame, return a vector with
    # N, mean, and sd
    datac <- ddply(data, groupvars, .drop=.drop,
      .fun = function(xx, col) {
        c(N    = length2(xx[[col]], na.rm=na.rm),
          mean = mean   (xx[[col]], na.rm=na.rm),
          sd   = sd     (xx[[col]], na.rm=na.rm)
        )
      },
      measurevar
    )

    # Rename the "mean" column    
    datac <- rename(datac, c("mean" = measurevar))

    datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean

    # Confidence interval multiplier for standard error
    # Calculate t-statistic for confidence interval: 
    # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
    ciMult <- qt(conf.interval/2 + .5, datac$N-1)
    datac$ci <- datac$se * ciMult

    return(datac)
}

normDataWithin <- function(data=NULL, idvar, measurevar, betweenvars=NULL,
                           na.rm=FALSE, .drop=TRUE) {
    library(plyr)

    # Measure var on left, idvar + between vars on right of formula.
    data.subjMean <- ddply(data, c(idvar, betweenvars), .drop=.drop,
     .fun = function(xx, col, na.rm) {
        c(subjMean = mean(xx[,col], na.rm=na.rm))
      },
      measurevar,
      na.rm
    )

    # Put the subject means with original data
    data <- merge(data, data.subjMean)

    # Get the normalized data in a new column
    measureNormedVar <- paste(measurevar, "_norm", sep="")
    data[,measureNormedVar] <- data[,measurevar] - data[,"subjMean"] +
                               mean(data[,measurevar], na.rm=na.rm)

    # Remove this subject mean column
    data$subjMean <- NULL

    return(data)
}
```

## Preprocess: calculate within subject standard error for accuracy
```{r}
library(plyr)
library(dplyr)
library(ggplot2)
library(data.table)
library("pastecs")

bar_all <-  allData[,c(which(str_detect(colnames(allData), 
                                          "part_id|group|ssl|lsl|vsl|tsl")))]
stat_desc <- 
function(df,group,task) {
  stat.desc(df[which(df$group == group & df$variable == task),])
}

bar_all_long <- melt(bar_all, id.vars=c("part_id", "group"))

bar_acc <-
  bar_all_long[which(str_detect(
    bar_all_long$variable, "\\S{1}(?=sl_acc)")),]

library("data.table")

bar_acc$variable <-
revalue(bar_acc$variable, c("lsl_acc"="Letter",
                                     "vsl_acc"="Image",
                                   "tsl_acc"="Tone",
                                     "ssl_acc"="Syllable"))

bar_acc$variable <- 
  factor(bar_acc$variable,levels = c("Image", 
                                              "Letter", 
                                              "Tone", 
                                              "Syllable"))
bar_acc <-
  bar_acc[order(bar_acc$variable), ]

bar_acc$value <- 
  as.numeric(as.character(bar_acc$value))

detach(package:plyr)

acc_within_stat <- summarySEwithin(bar_acc, measurevar="value", betweenvars = "group",
                                   withinvars="variable", idvar="part_id", na.rm=T, conf.interval=.95)

colnames(acc_within_stat)[colnames(acc_within_stat) == "group"] <- "Group"

acc_within_stat$variable <-
  factor(acc_within_stat$variable,
         levels = c("Letter",
                    "Syllable",
                    "Image",
                    "Tone"))
```

## Plot Accuracy Line Plot
```{r}
pd <- position_dodge(width = 0.2)

acc_within_stat %>%
  ggplot(aes(x = variable, y = value, group = Group)) +
  geom_line(aes(linetype = Group, color = Group),
            position = pd,
            size = 1.8) +
  geom_errorbar(aes(ymin = value - se, ymax = value + se),
                width = .1,
                position = pd) +
  geom_point(
    aes(color = Group),
    size = 4,
    position = pd,
    show.legend = FALSE
  ) +
  geom_point(size = 3,
             color = "white",
             position = pd) +
  labs(title = "2AFC Accuracy",
       x = "SL Task",  # Change x-axis label
       y = "Mean Accuracy (%)") +
  scale_color_manual(values = c(cbPalette[1], cbPalette[8])) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
    plot.title = element_text(size = 26, face = "bold"),
    axis.title.x = element_text(size = 21, face = "bold"),
    axis.title.y = element_text(size = 16, face = "bold"),
    axis.text = element_text(size = 16, face = "bold")
  ) +
  theme(
    legend.text = element_text(size = 22, face = "bold"),
    legend.title = element_text(size = 22, face = "bold")
  ) +
  theme(
    panel.background = element_rect(fill = "white"),
    # Set plot background to white
    legend.key  = element_rect(fill = "white"),
    # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),
    # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) +
  geom_hline(yintercept = 0.5, color = "grey") +
  geom_text(aes(
    x = 1.1,
    y = 0.505,
    label = paste0("chance", "-level")
  ), size = 5) +
  geom_text(aes(
    x = 0.95,
    y = 0.7,
    label = paste0("***")
  ),
  size = 10,
  color = cbPalette[1]) +
  geom_text(aes(x = 1.95, y = 0.7, label = paste0("**")),
            size = 10,
            color = cbPalette[1]) +
  geom_text(aes(
    x = 2.95,
    y = 0.7,
    label = paste0("***")
  ),
  size = 10,
  color = cbPalette[1]) +
  geom_text(aes(x = 3.95, y = 0.7, label = paste0("**")),
            size = 10,
            color = cbPalette[1]) +
  # geom_text(aes(x= 4.05, y = 0.7, label = paste0("")), size=7, color="#00BFC4") +
  geom_text(aes(x = 3.05, y = 0.51, label = paste0("*")),
            size = 10,
            color = cbPalette[8]) +
  # geom_text(aes(x= 1.95, y = 0.51, label = paste0("")), size=7, color="#F8766d") +
  geom_text(aes(x = 4.05, y = 0.51, label = paste0("**")),
            size = 10,
            color = cbPalette[8]) +
  geom_text(aes(x = 2.05, y = 0.494, label = paste0("*")),
            size = 10,
            color = cbPalette[8])

# ggsave("behavioral_acc_across_group.png",
#        bg="transparent",width = 15, height = 15, units = "cm")
```

## Preprocess: calculate within subject standard error for RT slope
```{r}
library(dplyr)
library(ggplot2)

bar_all_long <- melt(bar_all, id.vars=c("part_id", "group"))

bar_slope <-
  bar_all_long[which(
    str_detect(bar_all_long$variable, "\\S{3}(?=_slope)")),]


bar_slope$variable <-
revalue(bar_slope$variable, c("lsl_slope"="Letter",
                                     "vsl_slope"="Image",
                                     "tsl_slope"="Tone",
                                     "ssl_slope"="Syllable"))

bar_slope$variable <- 
  factor(bar_slope$variable,levels = c("Image", 
                                                  "Letter", 
                                                  "Tone", 
                                                  "Syllable"))

bar_slope <-
  bar_slope[order(bar_slope$variable), ]

bar_slope$value <- 
  as.numeric(as.character(bar_slope$value))

detach(package:plyr)
slope_within_stat <- summarySEwithin(bar_slope, measurevar="value", betweenvars = "group", withinvars="variable",
                        idvar="part_id", na.rm=T, conf.interval=.95)

colnames(slope_within_stat)[colnames(slope_within_stat) == "group"] <- "Group"
colnames(slope_within_stat)[colnames(slope_within_stat) == "value"] <- "mean"
colnames(slope_within_stat)[colnames(slope_within_stat) == "se"] <- "std_error"
colnames(slope_within_stat)[colnames(slope_within_stat) == "variable"] <- "task"

slope_within_stat$task <-
  factor(slope_within_stat$task,
         levels = c("Letter",
                    "Syllable",
                    "Image",
                    "Tone"))

slope_within_stat$Group <-
  factor(slope_within_stat$Group, levels = c("TD",
                                             "ASD"))
```

## Plot RT Slope Line Plot (outliers removed)
```{r}
pd <- position_dodge(width = 0.2)

slope_within_stat %>%
  ggplot(aes(x = task, y = mean, group = Group)) +
  geom_line(aes(linetype = Group, color = Group),
            position = pd,
            size = 1.8) +
  geom_errorbar(
    aes(ymin = mean - std_error, ymax = mean + std_error),
    width = .1,
    position = pd
  ) +
  geom_point(
    aes(color = Group),
    size = 4,
    position = pd,
    show.legend = FALSE
  ) +
  geom_point(size = 3,
             color = "white",
             position = pd) +
  labs(title = "SL Reaction Time Slope",
       x = "SL Task",  # Change x-axis label
       y = "Mean Reaction Time Slope (arbitrary unit/trial)") +
  scale_color_manual(values = c(cbPalette[1], cbPalette[8])) +
  # scale_y_reverse() +
  theme(plot.title = element_text(hjust = 0.35)) +
  theme(
    plot.title = element_text(size = 26, face = "bold"),
    axis.title.x = element_text(size = 21, face = "bold"),
    axis.title.y = element_text(size = 16, face = "bold"),
    axis.text = element_text(size = 16, face = "bold")
  ) +
  theme(
    legend.text = element_text(size = 22, face = "bold"),
    legend.title = element_text(size = 22, face = "bold")
  ) +
  theme(
    panel.background = element_rect(fill = "white"),
    # Set plot background to white
    legend.key  = element_rect(fill = "white"),
    # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),
    # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  )  +
  geom_hline(yintercept = 0, color = "grey") +
  geom_text(aes(
    x = 1.95,
    y = -0.033,
    label = paste0("***")
  ),
  size = 10,
  color = cbPalette[1]) +
  geom_text(aes(
    x = 0.95,
    y = -0.033,
    label = paste0("**")
  ),
  size = 10,
  color = cbPalette[1]) +
  geom_text(aes(
    x = 3.05,
    y = -0.033,
    label = paste0("*")
  ),
  size = 10,
  color = cbPalette[8])

 
# ggsave(
#     "behavioral_slope_across_group.png",
#      width = 15, height = 15, units = "cm"
#  )
```

## Preprocess: calculate within subject standard error for composite scores
```{r}
composite_within_stat <-
  summarySEwithin(
    compositeGroupL,
    measurevar = "composite_score",
    betweenvars = "group",
    withinvars = "task",
    idvar = "part_id",
    na.rm = T,
    conf.interval = .95
  )
colnames(composite_within_stat)[colnames(composite_within_stat) == "group"] <-
  "Group"
composite_within_stat$task <-
  revalue(
    composite_within_stat$task,
    c(
      "composite_lsl" = "Letter",
      "composite_tsl" = "Tone",
      "composite_ssl" = "Syllable",
      "composite_vsl" = "Image"
    )
  )
composite_within_stat$task <-
  factor(composite_within_stat$task,
         levels = c("Letter",
                    "Syllable",
                    "Image",
                    "Tone"))
composite_within_stat$Group <-
  factor(composite_within_stat$Group, levels = c("TD", "ASD"))
```

## Plot Composite Score Line Plot
```{r}
composite_within_stat %>%
  ggplot(aes(x = task, y = composite_score, group = Group)) +
  geom_line(aes(linetype = Group, color = Group),
            position = pd,
            size = 1.8) +
  geom_errorbar(
    aes(ymin = composite_score - se, ymax = composite_score + se),
    width = .1,
    position = pd
  ) +
  geom_point(
    aes(color = Group),
    size = 4,
    position = pd,
    show.legend = FALSE
  ) +
  geom_point(size = 3,
             color = "white",
             position = pd) +
  labs(title = "SL Composite Scores",
       x = "SL Task",  # Change x-axis label
       y = "Composite Score") +
  scale_color_manual(values = c(cbPalette[1], cbPalette[8])) +
  theme(plot.title = element_text(hjust = 0.4)) +
  theme(
    plot.title = element_text(size = 26, face = "bold"),
    axis.title.x = element_text(size = 21, face = "bold"),
    axis.title.y = element_text(size = 16, face = "bold"),
    axis.text = element_text(size = 16, face = "bold")
  ) +
  theme(
    legend.text = element_text(size = 22, face = "bold"),
    legend.title = element_text(size = 22, face = "bold")
  ) +
  theme(
    panel.background = element_rect(fill = "white"),
    # Set plot background to white
    legend.key  = element_rect(fill = "white"),
    # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),
    # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  )

# ggsave(
#   "behavioral_composite_across_group.png",
#   bg = "transparent",
#   width = 15,
#   height = 15,
#   units = "cm"
# )
```


## Preprocess: calculate within subject standard error for composite scores in each age group
```{r}
compositeYoungPlot <- summarySEwithin(compositeYoungL, measurevar = "composite_score", betweenvars = "group", 
                                    withinvars = "domain", idvar="part_id", na.rm=T, conf.interval=.95)

compositeYoungPlot$Age <- "Younger"

compositeOldPlot <- summarySEwithin(compositeOldL, measurevar = "composite_score", betweenvars = "group", 
                                    withinvars = "domain", idvar="part_id", na.rm=T, conf.interval=.95)

compositeOldPlot$Age <- "Older"

compositeAgePlot <- rbind(compositeYoungPlot, compositeOldPlot)

compositeAgePlot$domain <- 
  factor(compositeAgePlot$domain,levels = c("composite_ling", 
                                              "composite_nonling"))

colnames(compositeAgePlot)[colnames(compositeAgePlot) == "group"] <- "Group"
compositeAgePlot[which(compositeAgePlot$domain == "composite_nonling"), "Domain"] <- "Nonlinguistic"
compositeAgePlot[which(compositeAgePlot$domain == "composite_ling"), "Domain"] <- "Linguistic"

compositeAgePlot$Domain <- as.factor(compositeAgePlot$Domain)

compositeAgePlot$Age <- 
  factor(compositeAgePlot$Age,
         levels = c("Younger", 
                    "Older"))
compositeAgePlot <- compositeAgePlot[order(compositeAgePlot$Age), ]
```

## Plot Composite Score in Each Age Group
```{r}
library(ggplot2)
library(ggpattern)

labs <- c("Younger Children", "Older Children")
names(labs) <- c("Younger", "Older")

compositeAgePlot %>%
  ggplot(
    aes(
      x = Domain,
      y = composite_score,
      ymin = composite_score - se,
      ymax = composite_score + se,
      group = Group
    )
  ) +
  scale_fill_manual(values = c(cbPalette[1], cbPalette[8])) +
  geom_bar(stat = "identity",
           position = position_dodge(),
           width = 0.9) +
  facet_wrap("Age", labeller = (labeller(Age = labs))) +
  geom_col_pattern(
    aes(
      x = Domain,
      y = composite_score,
      pattern = Domain,
      fill = Group
    ),
    # color = Group
    # pattern = 'stripe',
    position = position_dodge(),
    pattern_density = 0.1,
    pattern_spacing = 0.025,
    pattern_key_scale_factor = 0.6,
    color = "#000000",
    pattern_colour = "black",
    pattern_fill = "black"
  ) +
  scale_pattern_manual(values = c(Linguistic = "stripe", Nonlinguistic = "none")) +
  # scale_fill_grey(start = 0.6, end = 1)+
  guides(pattern = guide_legend(override.aes = list(fill = "white")),
         fill = guide_legend(override.aes = list(pattern = "none"))) +
  geom_errorbar(width = .1, position = position_dodge(width = 0.9)) +
  labs(title = "SL Composite Scores in Younger and Older Children",
       x = "Group",  # Change x-axis label
       y = "SL Composite Score") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
    plot.title = element_text(size = 30, face = "bold"),
    axis.title.x = element_text(size = 26, face = "bold"),
    axis.title.y = element_text(size = 22, face = "bold"),
    axis.text = element_text(size = 24, face = "bold"),
    legend.text = element_text(size = 22, face = "bold"),
    legend.title = element_text(size = 22, face = "bold"),
    legend.key = element_rect(color = "black"),
    panel.background = element_rect(fill = "white"),
    # Set plot background to whit
    axis.line.x = element_line(colour = "black", size = 1),
    # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1),
    # Add line to y axis
    strip.text = element_text(size = 24, face = "bold"),
    # Change facet text
    strip.background = element_rect(fill = "white", size = 1),
    # Change facet color
    panel.spacing = unit(.05, "lines"),
    # Add panel border
    panel.border = element_rect(color = "black", fill = NA, size = 0.5),
    # Change panel border color and size
    legend.position = c(0.06, 0.88),
    legend.background = element_rect(fill = "#ffffff00")
    # strip.text = element_blank()
  ) +
  guides(pattern = FALSE) +
  # geom_text(
  #   size = 14,
  #   color = "black",
  #   data = data.frame(
  #     Group = 0,
  #     composite_score = 0.55,
  #     Age = "Older",
  #     se = 0,
  #     Domain = 0
  #   ),
  #   aes(x = 1.5, y = 0.53, label = paste0("*"))
  # ) +
    geom_text( 
    size = 10,
    color = "black",
    data = data.frame(
      Group = 0,
      composite_score = 0.55,
      Age = "Older",
      se = 0,
      Domain = 0
    ),
    aes(x = 1.5, y = 0.68, label = paste0(""))
  ) +
  geom_segment(
    aes(
      x = 1,
      xend = 2,
      y = 0.58,
      yend = 0.58
    ),
    data = data.frame(
      Group = 0,
      composite_score = 0.55,
      Age = "Older",
      se = 0,
      Domain = 0
    )
  ) +
  # geom_text(
  #   size = 14,
  #   color = "black",
  #   data = data.frame(
  #     Group = 0,
  #     composite_score = 0.55,
  #     Age = "Older",
  #     se = 0,
  #     Domain = 0
  #   ),
  #   aes(x = 1, y = 0.42, label = paste0("*"))
  # ) +
  geom_text(
    size = 14,
    color = "black",
    data = data.frame(
      Group = 0,
      composite_score = 0.6,
      Age = "Older",
      se = 0,
      Domain = 0
    ),
    aes(x = 1, y = 0.45, label = paste0("**"))
  ) +
  geom_segment(
    aes(
      x = 0.8,
      xend = 1.2,
      y = 0.46,
      yend = 0.46
    ),
    data = data.frame(
      Group = 0,
      composite_score = 0.55,
      Age = "Older",
      se = 0,
      Domain = 0
    )
  ) + 
  geom_segment(
    aes(
      x = 1.8,
      xend = 2.2,
      y = 0.46,
      yend = 0.46
    ),
    data = data.frame(
      Group = 0,
      composite_score = 0.55,
      Age = "Older",
      se = 0,
      Domain = 0
    )
  ) + 
  geom_segment(
    aes(
      x = 1,
      xend = 1,
      y = 0.53,
      yend = 0.58
    ),
    data = data.frame(
      Group = 0,
      composite_score = 0.55,
      Age = "Older",
      se = 0,
      Domain = 0
    )
  ) +
  geom_segment(
    aes(
      x = 2,
      xend = 2,
      y = 0.53,
      yend = 0.58
    ),
    data = data.frame(
      Group = 0,
      composite_score = 0.55,
      Age = "Older",
      se = 0,
      Domain = 0
    )
  ) 
# ggsave("composite_age_median.png",
#         bg="transparent",width = 30, height = 15, units = "cm")
```



# Section 7: Individual difference: Correlations between tasks, age, language

## Caculate correlations between all measures
```{r}
# Correlation matrix between ASD Lingusitic rt slope, composite and SCQ, RBS-R, Age
library("RcmdrMisc")


compositeCorr <- function(df, group) {
  rcorr.adjust(as.matrix(df[which(df$group == group), c(
    "age_at_web_year",
    "a_prime",
    "rbs_r",
    "scq_web",
    "lsl_slope",
    "ssl_slope",
    "vsl_slope",
    "tsl_slope",
    "lsl_acc",
    "ssl_acc",
    "vsl_acc",
    "tsl_acc",
    "composite_lsl",
    "composite_ssl",
    "composite_vsl",
    "composite_tsl",
    "composite_ling",
    "composite_nonling"
  )]),
  use = c("pairwise.complete.obs"))
}

# Extract correlation matrix:
td_corr_posthoc <- compositeCorr(compositeAge, "TD")
write.csv(as.data.frame(td_corr_posthoc$R[1]), "compositeCorrTD.csv")
write.csv(as.data.frame(td_corr_posthoc$R[3]), "compositeCorrPTD.csv")

asd_corr_posthoc <- compositeCorr(compositeAge, "ASD")
write.csv(as.data.frame(asd_corr_posthoc$R[1]), "compositeCorrASD.csv")
write.csv(as.data.frame(asd_corr_posthoc$R[3]), "compositeCorrPASD.csv")

asdOLD_corr_posthoc <- compositeCorr(compositeAgeASDO, "ASD")
tdOLD_corr_posthoc <-  compositeCorr(compositeAgeTDO, "TD")
asdYOUNG_corr_posthoc <- compositeCorr(compositeAgeASDY, "ASD")
tdYOUNG_corr_posthoc <-  compositeCorr(compositeAgeTDY, "TD")

# Flatten correlation matrix for plotting:
flattenCorrMatrix <- function(cormat, pmat, nmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  = (cormat)[ut],
    p = pmat[ut],
    n = nmat[ut]
  )
}

# Correlations wihtin all TD
td_corr_posthoc <-
  flattenCorrMatrix(data.frame(td_corr_posthoc$R[1]),
                  data.frame(td_corr_posthoc$R[3]),
                  data.frame(td_corr_posthoc$R[2]))
# Correlations wihtin all ASD
asd_corr_posthoc <-
  flattenCorrMatrix(data.frame(asd_corr_posthoc$R[1]),
                  data.frame(asd_corr_posthoc$R[3]),
                  data.frame(asd_corr_posthoc$R[2]))
# Correlations wihtin older TD
tdOLD_corr_posthoc <-
  flattenCorrMatrix(data.frame(tdOLD_corr_posthoc$R[1]),
                  data.frame(tdOLD_corr_posthoc$R[3]),
                  data.frame(tdOLD_corr_posthoc$R[2]))
# Correlations wihtin older ASD
asdOLD_corr_posthoc <-
  flattenCorrMatrix(data.frame(asdOLD_corr_posthoc$R[1]),
                  data.frame(asdOLD_corr_posthoc$R[3]),
                  data.frame(asdOLD_corr_posthoc$R[2]))
# Correlations wihtin younger TD
tdYOUNG_corr_posthoc <-
  flattenCorrMatrix(data.frame(tdYOUNG_corr_posthoc$R[1]),
                  data.frame(tdYOUNG_corr_posthoc$R[3]),
                  data.frame(tdYOUNG_corr_posthoc$R[2]))
# Correlations wihtin younger ASD
asdYOUNG_corr_posthoc <-
  flattenCorrMatrix(data.frame(asdYOUNG_corr_posthoc$R[1]),
                  data.frame(asdYOUNG_corr_posthoc$R[3]),
                  data.frame(asdYOUNG_corr_posthoc$R[2]))
```

