---
title: "BLAST Child versus Adult ERP Data Analysis"
author: "JM Schneider"
date: "4/6/2020"
output: html_document
---

## This code analyzes the BLAST projects' adult versus child EEG data.

### Import libraries
```{r loadlib, echo=T, results='hide', message=F, warning=F}
library(psych)
library(readr)
library(optimx)
library(corrplot)
library(reshape)
library(reshape2)
library(lmerTest)
library(ggplot2)
library(scales)
library(ggbeeswarm)
library(Hmisc)
library(arm)
library(ez)
library(dplyr)
```

### Import data
```{r}
setwd("/Users/julieschneider/Julie_Personal/Projects/BLAST/R/")
df_adult=read.csv('blast_adult_factor_analysis_n45.csv')
df_child=read.csv('blast_td_N22.csv')

#df_adult <- subset(df_adult, select = -c(Early))
df_overall <- rbind(df_adult,df_child)
```

### GLMER of Early ERP Data
```{r, echo=TRUE}
model<- lmer(Early~ 1 + Group*Domain*Global*Local + (1+(Global*Local)|subject),data = df_overall)
summary(model)
```
### GLMER of Late ERP Data
```{r, echo=TRUE}
model<- lmer(Late~ 1 + Group*Domain*Global*Local + (1+(Global*Local)|subject),data = df_overall)
summary(model)
```
### ANOVA of Early ERP Data
```{r, echo=TRUE}
early_blastANOVA <- ezANOVA(df_overall, Early, subject, between = Group, within = .(Domain,Local,Global), type = 3, detailed = TRUE)
early_blastANOVA
```
### ANOVA of Late ERP Data
```{r, echo=TRUE}
late_blastANOVA <- ezANOVA(df_overall, Late, subject, between = Group, within = .(Domain,Local,Global), type = 3, detailed = TRUE)
late_blastANOVA
```

## Plotting
### Plotting Early Effects
### Plotting Domain x Local Interaction
```{r}
d <- df_overall %>%
       select(Early,Local,Domain) %>%  # select relevant variables
       mutate(Local = factor(Local),
              Global = factor(Domain))

head(d)
d %>% 
  group_by(Local, Domain) %>%
  summarise(Late_mean = mean(Early))
sum_d <- d %>% 
          group_by(Local, Domain) %>%
          summarise(Early_mean = mean(Early),
                    se   = sd(Early)/sqrt(n()))
sum_d
```

```{r}
pd <- position_dodge(width = 0)
sum_d %>%
  ggplot(aes(x = Domain, y = Early_mean, group = Local)) +
    geom_line(aes(linetype = Local), position = pd) +
    geom_errorbar(aes(ymin = Early_mean - se, ymax = Early_mean + se),
                  width = .1, position = pd) +
    geom_point(size = 4, position = pd) +
    geom_point(size = 3, color = "white", position = pd) + 
    guides(linetype = guide_legend("Local")) +
    labs(x = "Domain",
         y = "Average ERP Amplitude -- Early") +
  theme(
    text=element_text(size=20),
    panel.background = element_rect(fill = "white"),         # Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  )
```
### Plotting Group x Global Interaction
```{r}
d <- df_overall %>%
       select(Early,Group,Global) %>%  # select relevant variables
       mutate(Group = factor(Group),
              Global = factor(Global))

head(d)
d %>% 
  group_by(Group, Global) %>%
  summarise(Early_mean = mean(Early))
sum_d <- d %>% 
          group_by(Group, Global) %>%
          summarise(Early_mean = mean(Early),
                    se   = sd(Early)/sqrt(n()))
sum_d
```

```{r}
pd <- position_dodge(width = 0)
sum_d %>%
  ggplot(aes(x = Global, y = Early_mean, group = Group)) +
    geom_line(aes(linetype = Group), position = pd) +
    geom_errorbar(aes(ymin = Early_mean - se, ymax = Early_mean + se),
                  width = .1, position = pd) +
    geom_point(size = 4, position = pd) +
    geom_point(size = 3, color = "white", position = pd) + 
    guides(linetype = guide_legend("Group")) +
    labs(x = "Global",
         y = "Average ERP Amplitude") +
  theme(
    text=element_text(size=20),
    panel.background = element_rect(fill = "white"),         # Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  )
```
### Main Effect of Global
```{r}
df_early = cast(df_overall,subject~Global,mean, value="Early")
df_early_melt = melt(df_early,id=c("Low","High"))

p <- ggplot(df_early_melt, aes(x=Global, y=value)) + 
  geom_violin(trim=FALSE) + theme_classic()+ 
  labs(title="Main Effect of Global (p)", y = "Mean ERP Amplitude") +
  stat_summary(fun.data=mean_sdl,geom="pointrange", color="red") +
    theme(plot.title = element_text(hjust = 0.5))
p
```

### Main Effect of Group
```{r}
df_early = cast(df_overall,subject~Group,mean, value="Early")
df_early_melt = melt(df_early,id=c("Child","Adult"))

p <- ggplot(df_early_melt, aes(x=Group, y=value)) + 
  geom_violin(trim=FALSE) + theme_classic()+ 
  labs(title="Main Effect of Group", y = "Mean ERP Amplitude") +
  stat_summary(fun.data=mean_sdl,geom="pointrange", color="red") +
    theme(plot.title = element_text(hjust = 0.5))
p
```

### Plotting Later Effects
### Plotting Group x GLobal x Local Interaction
### Decided to plot the Global x Local Interaction Within Each Age Group
```{r}
d <- df_adult %>%
       select(Late,Local,Global) %>%  # select relevant variables
       mutate(Local = factor(Local),
              Global = factor(Global))

head(d)
d %>% 
  group_by(Local, Global) %>%
  summarise(Late_mean = mean(Late))
sum_d <- d %>% 
          group_by(Local, Global) %>%
          summarise(Late_mean = mean(Late),
                    se   = sd(Late)/sqrt(n()))
sum_d
```

```{r}
pd <- position_dodge(width = 0)
adult_plot <- sum_d %>%
  ggplot(aes(x = Global, y = Late_mean, group = Local)) +
    geom_line(aes(linetype = Local), position = pd) +
    geom_errorbar(aes(ymin = Late_mean - se, ymax = Late_mean + se),
                  width = .1, position = pd) +
    geom_point(size = 4, position = pd) +
    geom_point(size = 3, color = "white", position = pd) + 
    guides(linetype = guide_legend("Local")) +
    labs(x = "Global",
         y = "Average Adult ERP Amplitude") +
  theme(
    text=element_text(size=20),
    panel.background = element_rect(fill = "white"),         # Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  )
```
```{r}
d <- df_child %>%
       select(Late,Local,Global) %>%  # select relevant variables
       mutate(Local = factor(Local),
              Global = factor(Global))

head(d)
d %>% 
  group_by(Local, Global) %>%
  summarise(Late_mean = mean(Late))
sum_d <- d %>% 
          group_by(Local, Global) %>%
          summarise(Late_mean = mean(Late),
                    se   = sd(Late)/sqrt(n()))
sum_d
```
```{r}
pd <- position_dodge(width = 0)
child_plot <- sum_d %>%
  ggplot(aes(x = Global, y = Late_mean, group = Local)) +
    geom_line(aes(linetype = Local), position = pd) +
    geom_errorbar(aes(ymin = Late_mean - se, ymax = Late_mean + se),
                  width = .1, position = pd) +
    geom_point(size = 4, position = pd) +
    geom_point(size = 3, color = "white", position = pd) + 
    guides(linetype = guide_legend("Local")) +
    labs(x = "Global",
         y = "Average Child ERP Amplitude") +
  theme(
    text=element_text(size=20),
    panel.background = element_rect(fill = "white"),         # Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  )
```
```{r}
layout(matrix(c(1),2))
plot(adult_plot, main="Adult Global x Local")
plot(child_plot, main="Child Global x Local")
```
### Main Effect of Global
```{r}
df_late = cast(df_overall,subject~Global,mean, value="Late")
df_late_melt = melt(df_late,id=c("Low","High"))

p <- ggplot(df_late_melt, aes(x=Global, y=value)) + 
  geom_violin(trim=FALSE) + theme_classic()+ 
  labs(title="Main Effect of Global (p)", y = "Mean ERP Amplitude") +
  stat_summary(fun.data=mean_sdl,geom="pointrange", color="red") +
    theme(plot.title = element_text(hjust = 0.5))
p
```

### Main Effect of Group
```{r}
df_late = cast(df_overall,subject~Group,mean, value="Late")
df_late_melt = melt(df_late,id=c("Child","Adult"))

p <- ggplot(df_late_melt, aes(x=Group, y=value)) + 
  geom_violin(trim=FALSE) + theme_classic()+ 
  labs(title="Main Effect of Group", y = "Mean ERP Amplitude") +
  stat_summary(fun.data=mean_sdl,geom="pointrange", color="red") +
    theme(plot.title = element_text(hjust = 0.5))
p
```