---
title: "Blast Adult ERP Analysis"
author: "JM Schneider"
date: "10/22/2019"
output: html_document
---

## This code analyzes the BLAST projects' adult EEG data.

### Import libraries
```{r, eval=TRUE}
library(ez); library(ggplot2); library(multcomp); library(nlme); library(pastecs); library(reshape)
library(Hmisc); library (WRS2); library(lme4); library(lmerTest); library(plyr); library(splitstackshape) 
library(naniar); library(tidyr); library(dplyr); library(memisc); library(psychReport);library(Hmisc); library(ggplot2); library(scales); library(ggbeeswarm)

```
### Import data as dataframe
```{r, eval=TRUE}
setwd("/Volumes/data/projects/blast/adult_erp_manuscript/")
df_corr=read.csv('blast_online_erp_adult_corr_data.csv')
df_factor=read.csv('blast_adult_factor_analysis_n45.csv')
```
### Compare Correlation matrix and Factor matrix subjects
```{r, eval=TRUE}
df_factor_subset <- df_factor[1:45,]
df_factor_subset$subject[!(df_factor_subset$subject %in% df_corr$subject)]
df_corr$subject[!(df_corr$subject %in% df_factor_subset$subject)]
```
### Remove subjects that do not have SSL online data or do not have ERP data
```{r, eval=TRUE}
df_factor<- df_factor[!grepl("blast_a_012", df_factor$subject),]
df_factor<- df_factor[!grepl("blast_a_020", df_factor$subject),]
df_factor<- df_factor[!grepl("blast_a_027", df_factor$subject),]
df_factor<- df_factor[!grepl("blast_a_029", df_factor$subject),]
df_factor<- df_factor[!grepl("blast_a_031", df_factor$subject),]
df_factor<- df_factor[!grepl("blast_a_036", df_factor$subject),]

df_corr<- df_corr[!grepl("blast_a_017", df_corr$subject),]
df_corr<- df_corr[!grepl("blast_a_032", df_corr$subject),]
df_corr<- df_corr[!grepl("blast_a_035", df_corr$subject),]
df_corr<- df_corr[!grepl("blast_a_040", df_corr$subject),]
df_corr<- df_corr[!grepl("blast_a_052", df_corr$subject),]
```
### GLMER of Early ERP Data
```{r, echo=TRUE}
model<- lmer(Early~ 1 + Domain*Global*Local + (1|subject), family = gaussian(), control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)),data = df_factor)
summary(model)
```
### GLMER of Late ERP Data
```{r, echo=TRUE}
model<- lmer(Late~ 1 + Domain*Global*Local + (1|subject), family = gaussian(), control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)),data = df_factor)
summary(model)
```
### ANOVA of Early ERP Data
```{r, echo=TRUE}
early_blastANOVA <- ezANOVA(df_factor, Early, subject, within = .(Domain,Local,Global), type = 3, detailed = TRUE)
early_blastANOVA
```
### ANOVA of Late ERP Data
```{r, echo=TRUE}
early_blastANOVA <- ezANOVA(df_factor, Late, subject, within = .(Domain,Local,Global), type = 3, detailed = TRUE)
early_blastANOVA
```
### Table of Means for Early ERP
```{r, echo=TRUE}
tapply(X = df_factor$Early, INDEX = list(df_factor$Global), FUN = mean)
tapply(X = df_factor$Early, INDEX = list(df_factor$Local), FUN = mean)
tapply(X = df_factor$Early, INDEX = list(df_factor$Domain), FUN = mean)
```
### Table of Means for Late ERP
```{r, echo=TRUE}
tapply(X = df_factor$Late, INDEX = list(df_factor$Global), FUN = mean)
tapply(X = df_factor$Late, INDEX = list(df_factor$Local), FUN = mean)
tapply(X = df_factor$Late, INDEX = list(df_factor$Domain), FUN = mean)
```
### Pairwise t-tests
```{r, echo=TRUE}
pairwise.t.test(df_factor$Early, df_factor$Domain, p.adj = 'bonferroni')
pairwise.t.test(df_factor$Early, df_factor$Global, p.adj = 'bonferroni')
pairwise.t.test(df_factor$Early, df_factor$Local, p.adj = 'bonferroni')
pairwise.t.test(df_factor$Late, df_factor$Domain, p.adj = 'bonferroni')
pairwise.t.test(df_factor$Late, df_factor$Global, p.adj = 'bonferroni')
pairwise.t.test(df_factor$Late, df_factor$Local, p.adj = 'bonferroni')
```

## Correlation Analysis

This section is used to analyze the correlation between SSL and BLAST ERP amplitudes.

### Organizing correlation data
```{r, eval=TRUE}
df_factor$Early = as.numeric(df_factor$Early)
df_factor$Late = as.numeric(df_factor$Late)

global_early<-cast(df_factor,subject~Global, mean, value = "Early")
df_corr$global_early <- rowMeans(global_early[c('High', 'Low')], na.rm=TRUE)

global_late<-cast(df_factor,subject~Global, mean, value = "Late")
df_corr$global_late <- rowMeans(global_late[c('High', 'Low')], na.rm=TRUE)

local_early<-cast(df_factor,subject~Local, mean, value = "Early")
df_corr$local_early <- rowMeans(local_early[c('Long', 'Short')], na.rm=TRUE)

local_late<-cast(df_factor,subject~Local, mean, value = "Late")
df_corr$local_late <- rowMeans(local_late[c('Long', 'Short')], na.rm=TRUE)

domain_early<-cast(df_factor,subject~Domain, mean, value = "Early")
df_corr$domain_early <- rowMeans(domain_early[c('Syllable', 'Voice')], na.rm=TRUE)

domain_late<-cast(df_factor,subject~Domain, mean, value = "Late")
df_corr$domain_late <- rowMeans(domain_late[c('Syllable', 'Voice')], na.rm=TRUE)
```

```{r, eval=TRUE}
df_corr$subject = as.numeric(df_corr$subject)
df_corr$accuracy = as.numeric(df_corr$accuracy)
df_corr$mean_rt = as.numeric(df_corr$mean_rt)
df_corr$scaled_rt_slope = as.numeric(df_corr$scaled_rt_slope)
df_corr$entropy = as.numeric(df_corr$entropy)
df_corr$vocab = as.numeric(df_corr$vocab)
df_corr$global_early = as.numeric(df_corr$global_early)
df_corr$global_late = as.numeric(df_corr$global_late)
df_corr$local_early = as.numeric(df_corr$local_early)
df_corr$local_late = as.numeric(df_corr$local_late)
df_corr$domain_early = as.numeric(df_corr$domain_early)
df_corr$domain_late = as.numeric(df_corr$domain_late)
```

### Run correlation matrix
```{r, echo=TRUE}
#df_corr<- na.omit(df_corr)
mycor <- rcorr(as.matrix(df_corr),type = "spearman")
mycor$r #Pearsons R
mycor$P #P values
mycor_p <- mycor$P
mycor_r <- mycor$r
```
## Now let's do some plotting!!

### Local and Global Interaction in Early Time Window
```{r, echo=FALSE}
ggplot() +
  theme_classic(base_size = 20.0) +
  ggtitle("Interaction in Early Time Window") + theme(plot.title = element_text(hjust = 0.5)) +
  ylab(label = 'ERP Amplitude') +
  scale_y_continuous(breaks = pretty_breaks()) +
  geom_bar(aes(y = Early, x = Global,fill =    as.factor(Global)),data=df_factor,colour="black",fun.data = mean_sdl,stat = 'summary') +
  geom_beeswarm(aes(x = Global,y = Early),data=df_factor,dodge.width=0.9,cex=2.5) +
  geom_errorbar(aes(y = Early, x = Global),data=df_factor,size = 0.3,width = 0.2,fun.y = function(x) mean(x),fun.ymin = function(x) mean(x) - sd(x)/sqrt(length(x)),fun.ymax = function(x) mean(x) + sd(x)/sqrt(length(x)) ,stat = 'summary')+
  facet_wrap(facets = .~Local) +
  scale_x_discrete(name = 'Global Probability',labels = c("High","Low"))+   
  scale_fill_brewer(palette = 'Set2') +
  theme(legend.position = "none")
```
### Local and Global Interaction in Late Time Window
```{r, echo=FALSE}
ggplot() +
  theme_classic(base_size = 20.0) +
  ggtitle("Interaction in Late Time Window") + theme(plot.title = element_text(hjust = 0.5)) +
  ylab(label = 'ERP Amplitude') +
  scale_y_continuous(breaks = pretty_breaks()) +
  geom_bar(aes(y = Late, x = Global,fill =    as.factor(Global)),data=df_factor,colour="black",fun.data = mean_sdl,stat = 'summary') +
  geom_beeswarm(aes(x = Global,y = Late),data=df_factor,dodge.width=0.9,cex=2.5) +
  geom_errorbar(aes(y = Late, x = Global),data=df_factor,size = 0.3,width = 0.2,fun.y = function(x) mean(x),fun.ymin = function(x) mean(x) - sd(x)/sqrt(length(x)),fun.ymax = function(x) mean(x) + sd(x)/sqrt(length(x)) ,stat = 'summary')+
  facet_wrap(facets = .~Local) +
  scale_x_discrete(name = 'Global Probability',labels = c("High","Low"))+   
  scale_fill_brewer(palette = 'Set2') +
  theme(legend.position = "none")
```

