---
title: "Blast Adult ERP Analysis"
author: "JM Schneider"
date: "10/22/2019"
output: html_document
---

## This code analyzes the BLAST projects' adult EEG data.

### Import libraries
```{r}
library(psych)
library(readr)
library(optimx)
library(corrplot)
library(reshape)
library(reshape2)
library(lmerTest)
library(ggplot2)
library(scales)
library(ggbeeswarm)
library(Hmisc)
library(arm)
library(ez)
library(dplyr)
```
### Import data as dataframe
```{r}
setwd("/Volumes/data/projects/blast/adult_erp_manuscript/")
df_corr=read.csv('blast_online_erp_adult_corr_data.csv')
df_factor=read.csv('blast_adult_factor_analysis_n45.csv')
```

### GLMER of Early ERP Data
```{r, echo=TRUE}
model<- lmer(Early~ 1 + Domain*Global*Local + (1+(Global*Local)|subject),data = df_factor)
summary(model)
```
### GLMER of Late ERP Data
```{r, echo=TRUE}
model<- lmer(Late~ 1 + Domain*Global*Local + (1+(Global*Local)|subject),data = df_factor)
summary(model)
```
### ANOVA of Early ERP Data
```{r, echo=TRUE}
early_blastANOVA <- ezANOVA(df_factor, Early, subject, within = .(Domain,Local,Global), type = 3, detailed = TRUE)
early_blastANOVA
```
### ANOVA of Late ERP Data
```{r, echo=TRUE}
early_blastANOVA <- ezANOVA(df_factor, Late, subject, within = .(Domain,Local,Global), type = 3, detailed = TRUE)
early_blastANOVA
```
### Table of Means for Early ERP
```{r, echo=TRUE}
tapply(X = df_factor$Early, INDEX = list(df_factor$Global), FUN = mean)
tapply(X = df_factor$Early, INDEX = list(df_factor$Local), FUN = mean)
tapply(X = df_factor$Early, INDEX = list(df_factor$Domain), FUN = mean)
```
### Table of Means for Late ERP
```{r, echo=TRUE}
tapply(X = df_factor$Late, INDEX = list(df_factor$Global), FUN = mean)
tapply(X = df_factor$Late, INDEX = list(df_factor$Local), FUN = mean)
tapply(X = df_factor$Late, INDEX = list(df_factor$Domain), FUN = mean)
```
### Pairwise t-tests
```{r, echo=TRUE}
pairwise.t.test(df_factor$Early, df_factor$Domain, p.adj = 'bonferroni')
pairwise.t.test(df_factor$Early, df_factor$Global, p.adj = 'bonferroni')
pairwise.t.test(df_factor$Early, df_factor$Local, p.adj = 'bonferroni')
pairwise.t.test(df_factor$Late, df_factor$Domain, p.adj = 'bonferroni')
pairwise.t.test(df_factor$Late, df_factor$Global, p.adj = 'bonferroni')
pairwise.t.test(df_factor$Late, df_factor$Local, p.adj = 'bonferroni')
```

## ttests
```{r}
df_ttest = cast(df_factor,subject~Domain+Global+Local,value="Early")

df_ttest$Short = (df_ttest$Syllable_High_Short+df_ttest$Syllable_Low_Short+df_ttest$Voice_High_Short+df_ttest$Voice_Low_Short)/4
df_ttest$Long = (df_ttest$Syllable_High_Long+df_ttest$Syllable_Low_Long+df_ttest$Voice_High_Long+df_ttest$Voice_Low_Long)/4

df_ttest$High = (df_ttest$Syllable_High_Short+df_ttest$Syllable_High_Long+df_ttest$Voice_High_Short+df_ttest$Voice_High_Long)/4
df_ttest$Low = (df_ttest$Syllable_Low_Short+df_ttest$Syllable_Low_Long+df_ttest$Voice_Low_Short+df_ttest$Voice_Low_Long)/4

df_ttest$Syll_High = (df_ttest$Syllable_High_Short+df_ttest$Syllable_High_Long)/2
df_ttest$Syll_Low = (df_ttest$Syllable_Low_Short+df_ttest$Syllable_Low_Long)/2
df_ttest$Voice_High = (df_ttest$Voice_High_Short+df_ttest$Voice_High_Long)/2
df_ttest$Voice_Low = (df_ttest$Voice_Low_Short+df_ttest$Voice_Low_Long)/2

df_ttest$Syll_Short = (df_ttest$Syllable_High_Short+df_ttest$Syllable_Low_Short)/2
df_ttest$Syll_Long = (df_ttest$Syllable_High_Long+df_ttest$Syllable_Low_Long)/2
df_ttest$Voice_Short = (df_ttest$Voice_High_Short+df_ttest$Voice_Low_Short)/2
df_ttest$Voice_Long = (df_ttest$Voice_High_Long+df_ttest$Voice_Low_Long)/2

t.test(df_ttest$Short,df_ttest$Long,paired=TRUE)
t.test(df_ttest$High, df_ttest$Low,paired=TRUE)
t.test(df_ttest$Syll_Short, df_ttest$Syll_Long,paired=TRUE)
t.test(df_ttest$Syll_High, df_ttest$Syll_Low,paired=TRUE)
t.test(df_ttest$Voice_Short, df_ttest$Voice_Long,paired=TRUE)
t.test(df_ttest$Voice_High, df_ttest$Voice_Low,paired=TRUE)
```

## Correlation Analysis

This section is used to analyze the correlation between SSL and BLAST ERP amplitudes.

### Compare Correlation matrix and Factor matrix subjects
```{r, eval=TRUE}
df_factor_subset <- df_factor[1:45,]
df_factor_subset$subject[!(df_factor_subset$subject %in% df_corr$subject)]
df_corr$subject[!(df_corr$subject %in% df_factor_subset$subject)]
```

### Remove subjects that do not have SSL online data or do not have ERP data
```{r, eval=TRUE}
df_factor<- df_factor[!grepl("blast_a_012", df_factor$subject),]
df_factor<- df_factor[!grepl("blast_a_020", df_factor$subject),]
df_factor<- df_factor[!grepl("blast_a_027", df_factor$subject),]
df_factor<- df_factor[!grepl("blast_a_029", df_factor$subject),]
df_factor<- df_factor[!grepl("blast_a_031", df_factor$subject),]
df_factor<- df_factor[!grepl("blast_a_036", df_factor$subject),]

df_corr<- df_corr[!grepl("blast_a_017", df_corr$subject),]
df_corr<- df_corr[!grepl("blast_a_032", df_corr$subject),]
df_corr<- df_corr[!grepl("blast_a_035", df_corr$subject),]
df_corr<- df_corr[!grepl("blast_a_040", df_corr$subject),]
df_corr<- df_corr[!grepl("blast_a_052", df_corr$subject),]
```

### Organizing correlation data for Early time window
```{r, eval=TRUE}
df_factor$Early = as.numeric(df_factor$Early)

df_early = cast(df_factor,subject~Domain+Global+Local,value="Early")

df_corr$Short = (df_early$Syllable_High_Short+df_early$Syllable_Low_Short+df_early$Voice_High_Short+df_early$Voice_Low_Short)/4
df_corr$Long = (df_early$Syllable_High_Long+df_early$Syllable_Low_Long+df_early$Voice_High_Long+df_early$Voice_Low_Long)/4
df_corr$Short_Long_MMN = df_corr$Short - df_corr$Long

df_corr$High = (df_early$Syllable_High_Short+df_early$Syllable_High_Long+df_early$Voice_High_Short+df_early$Voice_High_Long)/4
df_corr$Low = (df_early$Syllable_Low_Short+df_early$Syllable_Low_Long+df_early$Voice_Low_Short+df_early$Voice_Low_Long)/4
df_corr$High_Low_MMN = df_corr$High - df_corr$Low

df_corr$Syllable = (df_early$Syllable_High_Short+df_early$Syllable_High_Long+df_early$Syllable_Low_Short+df_early$Syllable_Low_Long)/4
df_corr$Voice = (df_early$Voice_High_Short+df_early$Voice_High_Long+df_early$Voice_Low_Short+df_early$Voice_Low_Long)/4
df_corr$Voice_Syllable_MMN = df_corr$Voice - df_corr$Syllable

Syll_High = (df_early$Syllable_High_Short+df_early$Syllable_High_Long)/2
Syll_Low = (df_early$Syllable_Low_Short+df_early$Syllable_Low_Long)/2
Voice_High = (df_early$Voice_High_Short+df_early$Voice_High_Long)/2
Voice_Low = (df_early$Voice_Low_Short+df_early$Voice_Low_Long)/2

Syll_Short = (df_early$Syllable_High_Short+df_early$Syllable_Low_Short)/2
Syll_Long = (df_early$Syllable_High_Long+df_early$Syllable_Low_Long)/2
Voice_Short = (df_early$Voice_High_Short+df_early$Voice_Low_Short)/2
Voice_Long = (df_early$Voice_High_Long+df_early$Voice_Low_Long)/2

df_corr$Syll_Local = (Syll_Short-Syll_Long)
df_corr$Syll_Global = (Syll_High-Syll_Low)
df_corr$Voice_Local = (Voice_Short-Voice_Long)
df_corr$Voice_Global = (Voice_High-Voice_Low)

df_corr$Global_long = ((df_early$Syllable_High_Long+df_early$Voice_High_Long)/2) - ((df_early$Syllable_Low_Long+df_early$Voice_Low_Long)/2)
df_corr$Global_short = ((df_early$Syllable_High_Short+df_early$Voice_High_Short)/2) - ((df_early$Syllable_Low_Short+df_early$Voice_Low_Short)/2)
df_corr$Local_high = ((df_early$Syllable_High_Short+df_early$Voice_High_Short)/2) - ((df_early$Syllable_High_Long+df_early$Voice_High_Long)/2)
df_corr$Local_low = ((df_early$Syllable_Low_Short+df_early$Voice_Low_Short)/2) - ((df_early$Syllable_Low_Long+df_early$Voice_Low_Long)/2)
```

```{r, eval=TRUE}
df_corr$subject = as.numeric(df_corr$subject)
df_corr$accuracy = as.numeric(df_corr$accuracy)
df_corr$mean_rt = as.numeric(df_corr$mean_rt)
df_corr$scaled_rt_slope = as.numeric(df_corr$scaled_rt_slope)
df_corr$entropy = as.numeric(df_corr$entropy)
df_corr$vocab = as.numeric(df_corr$vocab)
df_corr$Short = as.numeric(df_corr$Short)
df_corr$Long = as.numeric(df_corr$Long)
df_corr$Short_Long_MMN = as.numeric(df_corr$Short_Long_MMN)
df_corr$High = as.numeric(df_corr$High)
df_corr$Low = as.numeric(df_corr$Low)
df_corr$High_Low_MMN = as.numeric(df_corr$High_Low_MMN)
df_corr$Syllable = as.numeric(df_corr$Syllable)
df_corr$Voice = as.numeric(df_corr$Voice)
df_corr$Voice_Syllable_MMN = as.numeric(df_corr$Voice_Syllable_MMN)
df_corr$Syll_Local = as.numeric(df_corr$Syll_Local)
df_corr$Syll_Global = as.numeric(df_corr$Syll_Global)
df_corr$Voice_Local = as.numeric(df_corr$Voice_Local)
df_corr$Voice_Global = as.numeric(df_corr$Voice_Global)
df_corr$Global_long = as.numeric(df_corr$Global_long)
df_corr$Global_short = as.numeric(df_corr$Global_short)
df_corr$Local_high = as.numeric(df_corr$Local_high)
df_corr$Local_low = as.numeric(df_corr$Local_low)
```

## Early Correlation 
### Run correlation matrix
```{r, echo=TRUE}
df_corr_early<- df_corr
mycor_early <- rcorr(as.matrix(df_corr_early),type = "spearman")
mycor_early$r #Pearsons R
mycor_early$P #P values
my_early_cor_p <- mycor_early$P
my_early_cor_r <- mycor_early$r
```

### Organizing correlation data for Late Time Window
```{r}
df_factor$Late = as.numeric(df_factor$Late)
df_late = cast(df_factor,subject~Domain+Global+Local,value="Late")

df_corr$Short = (df_late$Syllable_High_Short+df_late$Syllable_Low_Short+df_late$Voice_High_Short+df_late$Voice_Low_Short)/4
df_corr$Long = (df_late$Syllable_High_Long+df_late$Syllable_Low_Long+df_late$Voice_High_Long+df_late$Voice_Low_Long)/4
df_corr$Short_Long_MMN = df_corr$Short - df_corr$Long

df_corr$High = (df_late$Syllable_High_Short+df_late$Syllable_High_Long+df_late$Voice_High_Short+df_late$Voice_High_Long)/4
df_corr$Low = (df_late$Syllable_Low_Short+df_late$Syllable_Low_Long+df_late$Voice_Low_Short+df_late$Voice_Low_Long)/4
df_corr$High_Low_MMN = df_corr$High - df_corr$Low

df_corr$Syllable = (df_late$Syllable_High_Short+df_late$Syllable_High_Long+df_late$Syllable_Low_Short+df_late$Syllable_Low_Long)/4
df_corr$Voice = (df_late$Voice_High_Short+df_late$Voice_High_Long+df_late$Voice_Low_Short+df_late$Voice_Low_Long)/4
df_corr$Voice_Syllable_MMN = df_corr$Voice - df_corr$Syllable

Syll_High = (df_late$Syllable_High_Short+df_late$Syllable_High_Long)/2
Syll_Low = (df_late$Syllable_Low_Short+df_late$Syllable_Low_Long)/2
Voice_High = (df_late$Voice_High_Short+df_late$Voice_High_Long)/2
Voice_Low = (df_late$Voice_Low_Short+df_late$Voice_Low_Long)/2

Syll_Short = (df_late$Syllable_High_Short+df_late$Syllable_Low_Short)/2
Syll_Long = (df_late$Syllable_High_Long+df_late$Syllable_Low_Long)/2
Voice_Short = (df_late$Voice_High_Short+df_late$Voice_Low_Short)/2
Voice_Long = (df_late$Voice_High_Long+df_late$Voice_Low_Long)/2

df_corr$Syll_Local = (Syll_Short-Syll_Long)
df_corr$Syll_Global = (Syll_High-Syll_Low)
df_corr$Voice_Local = (Voice_Short-Voice_Long)
df_corr$Voice_Global = (Voice_High-Voice_Low)

df_corr$Global_long = ((df_late$Syllable_High_Long+df_late$Voice_High_Long)/2) - ((df_late$Syllable_Low_Long+df_late$Voice_Low_Long)/2)
df_corr$Global_short = ((df_late$Syllable_High_Short+df_late$Voice_High_Short)/2) - ((df_late$Syllable_Low_Short+df_late$Voice_Low_Short)/2)
df_corr$Local_high = ((df_late$Syllable_High_Short+df_late$Voice_High_Short)/2) - ((df_late$Syllable_High_Long+df_late$Voice_High_Long)/2)
df_corr$Local_low = ((df_late$Syllable_Low_Short+df_late$Voice_Low_Short)/2) - ((df_late$Syllable_Low_Long+df_late$Voice_Low_Long)/2)
```

```{r, eval=TRUE}
df_corr$subject = as.numeric(df_corr$subject)
df_corr$accuracy = as.numeric(df_corr$accuracy)
df_corr$mean_rt = as.numeric(df_corr$mean_rt)
df_corr$scaled_rt_slope = as.numeric(df_corr$scaled_rt_slope)
df_corr$entropy = as.numeric(df_corr$entropy)
df_corr$vocab = as.numeric(df_corr$vocab)
df_corr$Short = as.numeric(df_corr$Short)
df_corr$Long = as.numeric(df_corr$Long)
df_corr$Short_Long_MMN = as.numeric(df_corr$Short_Long_MMN)
df_corr$High = as.numeric(df_corr$High)
df_corr$Low = as.numeric(df_corr$Low)
df_corr$High_Low_MMN = as.numeric(df_corr$High_Low_MMN)
df_corr$Syllable = as.numeric(df_corr$Syllable)
df_corr$Voice = as.numeric(df_corr$Voice)
df_corr$Voice_Syllable_MMN = as.numeric(df_corr$Voice_Syllable_MMN)
df_corr$Syll_Local = as.numeric(df_corr$Syll_Local)
df_corr$Syll_Global = as.numeric(df_corr$Syll_Global)
df_corr$Voice_Local = as.numeric(df_corr$Voice_Local)
df_corr$Voice_Global = as.numeric(df_corr$Voice_Global)
df_corr$Global_long = as.numeric(df_corr$Global_long)
df_corr$Global_short = as.numeric(df_corr$Global_short)
df_corr$Local_high = as.numeric(df_corr$Local_high)
df_corr$Local_low = as.numeric(df_corr$Local_low)
```

## Late Correlation 
### Run correlation matrix
```{r, echo=TRUE}
df_corr_late <- df_corr
mycor_late <- rcorr(as.matrix(df_corr_late),type = "spearman")
mycor_late$r #Pearsons R
mycor_late$P #P values
my_late_cor_p <- mycor_late$P
my_late_cor_r <- mycor_late$r
```

## Now let's do some plotting!!

### Violin plot of local main effect in early time window
```{r}
df_early_test = cast(df_factor,subject~Local,mean, value="Early")
df_early_melt = melt(df_early_test,id=c("Short","Long"))

p <- ggplot(df_early_melt, aes(x=Local, y=value)) + 
  geom_violin(trim=FALSE) + theme_classic()+ 
  labs(title="Main Effect of Local (p)", y = "Mean ERP Amplitude") +
  theme(plot.title = element_text(hjust = 0.5)) +
  stat_summary(fun.data=mean_sdl, 
                 geom="pointrange", color="red")
p
```

```{r}
d <- df_early_melt

d %>% 
  group_by(Local) %>%
  summarise(Early_mean = mean(value))
sum_d <- d %>% 
          group_by(Local) %>%
          summarise(Early_mean = mean(value),
                    se   = sd(value)/sqrt(n()))
sum_d

pd <- position_dodge(width = 0)
sum_d %>%
  ggplot(aes(x = Local, y = Early_mean)) +
    geom_errorbar(aes(ymin = Early_mean - se, ymax = Early_mean + se),
                  width = .1, position = pd) +
    geom_point(size = 4, position = pd) +
    geom_point(size = 3, color = "white", position = pd) + 
    labs(x = "Local",
         y = "Average ERP Amplitude") +
  theme(
    text=element_text(size=20),
    panel.background = element_rect(fill = "white"),         # Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  )
```

### plot the line graphs to illustrate interaction between Local and Global Interaction in Late Time Window
```{r}
d <- df_factor %>%
       select(Late,Local,Global) %>%  # select relevant variables
       mutate(Local = factor(Local, labels = c("Short", "Long")),
              Global = factor(Global))

head(d)
d %>% 
  group_by(Local, Global) %>%
  summarise(Late_mean = mean(Late))
sum_d <- d %>% 
          group_by(Local, Global) %>%
          summarise(Late_mean = mean(Late),
                    se   = sd(Late)/sqrt(n()))
sum_d
```

```{r}
pd <- position_dodge(width = 0)
sum_d %>%
  ggplot(aes(x = Local, y = Late_mean, group = Global)) +
    geom_line(aes(linetype = Global), position = pd) +
    geom_errorbar(aes(ymin = Late_mean - se, ymax = Late_mean + se),
                  width = .1, position = pd) +
    geom_point(size = 4, position = pd) +
    geom_point(size = 3, color = "white", position = pd) + 
    guides(linetype = guide_legend("Global")) +
    labs(x = "Local",
         y = "Average ERP Amplitude") +
  theme(
    text=element_text(size=20),
    panel.background = element_rect(fill = "white"),         # Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  )
```

### Plot the same interaction (Local and Global Interaction in Late Time Window) as a bar graph
```{r, echo=FALSE}
ggplot() +
  theme_classic(base_size = 20.0) +
  ggtitle("Interaction in Late Time Window") + theme(plot.title = element_text(hjust = 0.5)) +
  ylab(label = 'ERP Amplitude') +
  scale_y_continuous(breaks = pretty_breaks()) +
  geom_bar(aes(y = Late, x = Global,fill =    as.factor(Global)),data=df_factor,colour="black",fun.data = mean_sdl,stat = 'summary') +
  geom_beeswarm(aes(x = Global,y = Late),data=df_factor,dodge.width=0.9,cex=2.5) +
  geom_errorbar(aes(y = Late, x = Global),data=df_factor,size = 0.3,width = 0.2,fun.y = function(x) mean(x),fun.ymin = function(x) mean(x) - sd(x)/sqrt(length(x)),fun.ymax = function(x) mean(x) + sd(x)/sqrt(length(x)) ,stat = 'summary')+
  facet_wrap(facets = .~Local) +
  scale_x_discrete(name = 'Global Probability',labels = c("High","Low"))+   
  scale_fill_brewer(palette = 'Set2') +
  theme(legend.position = "none")
```

### Plotting the early correlations
```{r}
ggplot(df_corr_early, aes(x=High_Low_MMN, y=accuracy)) + geom_point(size=3, color="navy blue", shape=19) + labs(title="Distributional SL Accuracy & Global (p) MMN", x="Global (p) MMN", y = "SL Accuracy") + theme(plot.title = element_text(hjust = 0.5)) + geom_smooth(method=lm)
```
```{r}
ggplot(df_corr_early, aes(x=Syll_Global, y=accuracy)) + geom_point(size=3, color="navy blue", shape=19) + labs(title="Distributional SL Accuracy & Global (p) MMN for Syllables", x="Syllable Only Global (p) MMN", y = "SL Accuracy") + theme(plot.title = element_text(hjust = 0.5)) + geom_smooth(method=lm)
```
```{r}
ggplot(df_corr_early, aes(x=Syll_Global, y=mean_rt)) + geom_point(size=3, color="navy blue", shape=19) + labs(title="Distributional SL Mean RT & Global (p) MMN for Syllables", x="Syllable Only Global (p) MMN", y = "Mean Reaction Time") + theme(plot.title = element_text(hjust = 0.5)) + geom_smooth(method=lm)
```
```{r}
ggplot(df_corr_early, aes(x=Local_low, y=scaled_rt_slope)) + geom_point(size=3, color="navy blue", shape=19) + labs(title="Distributional SL RT & Local (p) within Low Condition", x="Low Only Local (p) MMN", y = "RT SLope") + theme(plot.title = element_text(hjust = 0.5)) + geom_smooth(method=lm)
```

### Plotting the late correlations
```{r}
ggplot(df_corr_late, aes(x=Short, y=scaled_rt_slope)) + geom_point(size=3, color="navy blue", shape=19) + labs(title="Distributional SL RT & Local (p)", x="Local (p) Short Only", y = "RT Slope") + theme(plot.title = element_text(hjust = 0.5)) + geom_smooth(method=lm)
```

```{r}
ggplot(df_corr_late, aes(x=Short_Long_MMN, y=scaled_rt_slope)) + geom_point(size=3, color="navy blue", shape=19) + labs(title="Distributional SL RT & Local (p) MMN", x="Local (p) MMN", y = "RT Slope") + theme(plot.title = element_text(hjust = 0.5)) + geom_smooth(method=lm)
```
```{r}
ggplot(df_corr_late, aes(x=Voice_Global, y=entropy)) + geom_point(size=3, color="navy blue", shape=19) + labs(title="Distributional SL Entropy & Global (p) MMN for Voice", x="Voice Only Global (p) MMN", y = "Entropy") + theme(plot.title = element_text(hjust = 0.5)) + geom_smooth(method=lm)
```
```{r}
ggplot(df_corr_late, aes(x=Local_low, y=scaled_rt_slope)) + geom_point(size=3, color="navy blue", shape=19) + labs(title="Distributional SL RT & Local (p) within Low Condition", x="Low Only Local (p) MMN", y = "RT SLope") + theme(plot.title = element_text(hjust = 0.5)) + geom_smooth(method=lm)
```

