---
title: "Blast Adult ERP Analysis"
author: "JM Schneider"
date: "10/22/2019"
output: html_document
---

## This code analyzes the BLAST projects' adult EEG data.

### Import libraries
```{r, echo=FALSE}
library(psych);
library(readr);
library(optimx);
library(corrplot);
library(reshape);
library(reshape2);
library(lmerTest);
library(ggplot2);
library(scales);
library(ggbeeswarm);
library(Hmisc);
library(arm);
library(ez);
library(dplyr);
library(lmerTest)
library(simr);
library(dplyr)
```
### Import data as dataframe
```{r}
#setwd("/Volumes/data/projects/blast/adult_erp_manuscript/")
df_corr=read.csv('blast_online_erp_adult_corr_data.csv')
df_rt_slope=read.csv('blast_online_adult_ssl_indiv_rts.csv')
df_factor=read.csv('blast_adult_factor_analysis_n45.csv')
df_corr$mean_rt <- NULL
df_corr$scaled_rt_slope <- NULL
```

```{r}
df_rt_slope <- df_rt_slope %>% 
  dplyr::rename(
    subject = par_id
  )
df_rt_slope = subset(df_rt_slope, select = c(subject,mean_rt,scaled_rt_slope) )
df_corr <- merge(df_corr,df_rt_slope, by = "subject")
```

### LMER of Early ERP Data
```{r, echo=TRUE}
df_factor$Local = relevel(df_factor$Local,"Short")
model<- lmer(Early~ Domain*Global*Local + (1+(Global*Local)|subject),data = df_factor,control = lmerControl(calc.derivs = FALSE))
summary(model)
#lme.dscore(model, df_factor, "lme4")
```
### GLMER of Late ERP Data
```{r, echo=TRUE}
model<- lmer(Late~ Domain*Global*Local + (1+(Global*Local)|subject),data = df_factor,control = lmerControl(calc.derivs = FALSE))
summary(model)
```

### Table of Means for Early ERP
```{r, echo=TRUE}
tapply(X = df_factor$Early, INDEX = list(df_factor$Global), FUN = mean)
tapply(X = df_factor$Early, INDEX = list(df_factor$Local), FUN = mean)
tapply(X = df_factor$Early, INDEX = list(df_factor$Domain), FUN = mean)
```
### Table of Means for Late ERP
```{r, echo=TRUE}
tapply(X = df_factor$Late, INDEX = list(df_factor$Global), FUN = mean)
tapply(X = df_factor$Late, INDEX = list(df_factor$Local), FUN = mean)
tapply(X = df_factor$Late, INDEX = list(df_factor$Domain), FUN = mean)
```
### Pairwise t-tests
```{r, echo=TRUE}
pairwise.t.test(df_factor$Early, df_factor$Domain, p.adj = 'bonferroni')
pairwise.t.test(df_factor$Early, df_factor$Global, p.adj = 'bonferroni')
pairwise.t.test(df_factor$Early, df_factor$Local, p.adj = 'bonferroni')
pairwise.t.test(df_factor$Late, df_factor$Domain, p.adj = 'bonferroni')
pairwise.t.test(df_factor$Late, df_factor$Global, p.adj = 'bonferroni')
pairwise.t.test(df_factor$Late, df_factor$Local, p.adj = 'bonferroni')
```

#pairwise t-tests used to gauge interaction effect (breakdown of the interaction)
```{r}
blast_high<-df_factor[which(df_factor$Global=="High"),]
blast_low<-df_factor[which(df_factor$Global=="Low"),]

blast_short<-df_factor[which(df_factor$Local=="Short"),]
blast_long<-df_factor[which(df_factor$Local=="Long"),]

pairwise.t.test(blast_short$Late, blast_short$Global, p.adj = 'bonferroni') #significant
pairwise.t.test(blast_long$Late, blast_long$Global, p.adj = 'bonferroni')

pairwise.t.test(blast_high$Late, blast_high$Local, p.adj = 'bonferroni') #significant
pairwise.t.test(blast_low$Late, blast_low$Local, p.adj = 'bonferroni')
```

## ttests
```{r}
## Change Late and Early to run ttests on different time windows
df_ttest = cast(df_factor,subject~Domain+Global+Local,value="Late")

df_ttest$Short = (df_ttest$Syllable_High_Short+df_ttest$Syllable_Low_Short+df_ttest$Voice_High_Short+df_ttest$Voice_Low_Short)/4
df_ttest$Long = (df_ttest$Syllable_High_Long+df_ttest$Syllable_Low_Long+df_ttest$Voice_High_Long+df_ttest$Voice_Low_Long)/4

df_ttest$High = (df_ttest$Syllable_High_Short+df_ttest$Syllable_High_Long+df_ttest$Voice_High_Short+df_ttest$Voice_High_Long)/4
df_ttest$Low = (df_ttest$Syllable_Low_Short+df_ttest$Syllable_Low_Long+df_ttest$Voice_Low_Short+df_ttest$Voice_Low_Long)/4

df_ttest$Syll_High = (df_ttest$Syllable_High_Short+df_ttest$Syllable_High_Long)/2
df_ttest$Syll_Low = (df_ttest$Syllable_Low_Short+df_ttest$Syllable_Low_Long)/2
df_ttest$Voice_High = (df_ttest$Voice_High_Short+df_ttest$Voice_High_Long)/2
df_ttest$Voice_Low = (df_ttest$Voice_Low_Short+df_ttest$Voice_Low_Long)/2

df_ttest$Syll_Short = (df_ttest$Syllable_High_Short+df_ttest$Syllable_Low_Short)/2
df_ttest$Syll_Long = (df_ttest$Syllable_High_Long+df_ttest$Syllable_Low_Long)/2
df_ttest$Voice_Short = (df_ttest$Voice_High_Short+df_ttest$Voice_Low_Short)/2
df_ttest$Voice_Long = (df_ttest$Voice_High_Long+df_ttest$Voice_Low_Long)/2

df_ttest$High_Short = (df_ttest$Syllable_High_Short+df_ttest$Voice_High_Short)/2
df_ttest$Low_Short = (df_ttest$Syllable_Low_Short+df_ttest$Voice_Low_Short)/2
df_ttest$High_Long = (df_ttest$Syllable_High_Long+df_ttest$Voice_High_Long)/2
df_ttest$Low_Long = (df_ttest$Syllable_Low_Long+df_ttest$Voice_Low_Long)/2

t.test(df_ttest$Short,df_ttest$Long,paired=TRUE)
t.test(df_ttest$High, df_ttest$Low,paired=TRUE)
t.test(df_ttest$Syll_Short, df_ttest$Syll_Long,paired=TRUE)
t.test(df_ttest$Syll_High, df_ttest$Syll_Low,paired=TRUE)
t.test(df_ttest$Voice_Short, df_ttest$Voice_Long,paired=TRUE)
t.test(df_ttest$Voice_High, df_ttest$Voice_Low,paired=TRUE)

t.test(df_ttest$High_Short, df_ttest$Low_Short,paired=TRUE)
t.test(df_ttest$High_Short, df_ttest$High_Long,paired=TRUE)
t.test(df_ttest$Low_Long, df_ttest$Low_Short,paired=TRUE)
t.test(df_ttest$Low_Long, df_ttest$High_Long,paired=TRUE)

```

## Correlation Analysis

This section is used to analyze the correlation between web-based SSL and BLAST ERP amplitudes.

### Compare Correlation matrix and Factor matrix subjects
```{r, eval=TRUE}
df_factor_subset <- df_factor[1:45,]
df_factor_subset$subject[!(df_factor_subset$subject %in% df_corr$subject)]
df_corr$subject[!(df_corr$subject %in% df_factor_subset$subject)]
```

### Remove subjects that do not have SSL online data or do not have ERP data
```{r, eval=TRUE}
df_factor<- df_factor[!grepl("blast_a_012", df_factor$subject),]
df_factor<- df_factor[!grepl("blast_a_020", df_factor$subject),]
df_factor<- df_factor[!grepl("blast_a_027", df_factor$subject),]
df_factor<- df_factor[!grepl("blast_a_029", df_factor$subject),]
df_factor<- df_factor[!grepl("blast_a_031", df_factor$subject),]
df_factor<- df_factor[!grepl("blast_a_036", df_factor$subject),]
df_factor<- df_factor[!grepl("blast_a_025", df_factor$subject),]

df_corr<- df_corr[!grepl("blast_a_017", df_corr$subject),]
df_corr<- df_corr[!grepl("blast_a_032", df_corr$subject),]
df_corr<- df_corr[!grepl("blast_a_035", df_corr$subject),]
df_corr<- df_corr[!grepl("blast_a_040", df_corr$subject),]
df_corr<- df_corr[!grepl("blast_a_052", df_corr$subject),]
df_corr<- df_corr[!grepl("blast_a_025", df_corr$subject),]
```

### Organizing correlation data for Early time window
## all the global effects were defined as (Low - High); all the local effects were defined as (Long - Short)
```{r, eval=TRUE}
df_factor$Early = as.numeric(df_factor$Early)

df_early = cast(df_factor,subject~Domain+Global+Local,value="Early")
df_corr$Short = (df_early$Syllable_High_Short+df_early$Syllable_Low_Short+df_early$Voice_High_Short+df_early$Voice_Low_Short)/4
df_corr$Long = (df_early$Syllable_High_Long+df_early$Syllable_Low_Long+df_early$Voice_High_Long+df_early$Voice_Low_Long)/4
df_corr$Long_Short_MMN = df_corr$Long - df_corr$Short

df_corr$High = (df_early$Syllable_High_Short+df_early$Syllable_High_Long+df_early$Voice_High_Short+df_early$Voice_High_Long)/4
df_corr$Low = (df_early$Syllable_Low_Short+df_early$Syllable_Low_Long+df_early$Voice_Low_Short+df_early$Voice_Low_Long)/4
df_corr$Low_High_MMN = df_corr$Low - df_corr$High

df_corr$Syllable = (df_early$Syllable_High_Short+df_early$Syllable_High_Long+df_early$Syllable_Low_Short+df_early$Syllable_Low_Long)/4
df_corr$Voice = (df_early$Voice_High_Short+df_early$Voice_High_Long+df_early$Voice_Low_Short+df_early$Voice_Low_Long)/4
df_corr$Voice_Syllable_MMN = df_corr$Voice - df_corr$Syllable

Syll_High = (df_early$Syllable_High_Short+df_early$Syllable_High_Long)/2
Syll_Low = (df_early$Syllable_Low_Short+df_early$Syllable_Low_Long)/2
Voice_High = (df_early$Voice_High_Short+df_early$Voice_High_Long)/2
Voice_Low = (df_early$Voice_Low_Short+df_early$Voice_Low_Long)/2

Syll_Short = (df_early$Syllable_High_Short+df_early$Syllable_Low_Short)/2
Syll_Long = (df_early$Syllable_High_Long+df_early$Syllable_Low_Long)/2
Voice_Short = (df_early$Voice_High_Short+df_early$Voice_Low_Short)/2
Voice_Long = (df_early$Voice_High_Long+df_early$Voice_Low_Long)/2

df_corr$Syll_Local = (Syll_Long-Syll_Short)
df_corr$Syll_Global = (Syll_Low-Syll_High)
df_corr$Voice_Local = (Voice_Long-Voice_Short)
df_corr$Voice_Global = (Voice_Low-Voice_High)

df_corr$Global_long =  ((df_early$Syllable_Low_Long+df_early$Voice_Low_Long)/2) - ((df_early$Syllable_High_Long+df_early$Voice_High_Long)/2)
df_corr$Global_short = ((df_early$Syllable_Low_Short+df_early$Voice_Low_Short)/2) - ((df_early$Syllable_High_Short+df_early$Voice_High_Short)/2)
df_corr$Local_high = ((df_early$Syllable_High_Long+df_early$Voice_High_Long)/2)-((df_early$Syllable_High_Short+df_early$Voice_High_Short)/2)
df_corr$Local_low = ((df_early$Syllable_Low_Long+df_early$Voice_Low_Long)/2)-((df_early$Syllable_Low_Short+df_early$Voice_Low_Short)/2)
```

```{r, eval=TRUE}
df_corr$accuracy = as.numeric(df_corr$accuracy)
df_corr$mean_rt = as.numeric(df_corr$mean_rt)
df_corr$entropy = as.numeric(df_corr$entropy)
df_corr$vocab = as.numeric(df_corr$vocab)
df_corr$Short = as.numeric(df_corr$Short)
df_corr$Long = as.numeric(df_corr$Long)
df_corr$Long_Short_MMN = as.numeric(df_corr$Long_Short_MMN)
df_corr$High = as.numeric(df_corr$High)
df_corr$Low = as.numeric(df_corr$Low)
df_corr$Low_High_MMN = as.numeric(df_corr$Low_High_MMN)
df_corr$Syllable = as.numeric(df_corr$Syllable)
df_corr$Voice = as.numeric(df_corr$Voice)
df_corr$Voice_Syllable_MMN = as.numeric(df_corr$Voice_Syllable_MMN)
df_corr$Syll_Local = as.numeric(df_corr$Syll_Local)
df_corr$Syll_Global = as.numeric(df_corr$Syll_Global)
df_corr$Voice_Local = as.numeric(df_corr$Voice_Local)
df_corr$Voice_Global = as.numeric(df_corr$Voice_Global)
df_corr$Global_long = as.numeric(df_corr$Global_long)
df_corr$Global_short = as.numeric(df_corr$Global_short)
df_corr$Local_high = as.numeric(df_corr$Local_high)
df_corr$Local_low = as.numeric(df_corr$Local_low)
df_corr$scaled_rt_slope = as.numeric(as.character(df_corr$scaled_rt_slope))
#df_corr$subject = as.numeric(df_corr$subject)
```

## Early Correlation 
### Run correlation matrix
```{r, echo=TRUE}
df_corr_early<- df_corr
mycor_early <- rcorr(as.matrix(df_corr_early[,3:24]),type = "spearman")
mycor_early$r #Spearman Rho
mycor_early$P #P values
my_early_cor_p <- mycor_early$P
my_early_cor_r <- mycor_early$r
```

### Organizing correlation data for Late Time Window
## all the global effects were defined as (Low - High); all the local effects were defined as (Long - Short)
```{r}
df_factor$Late = as.numeric(df_factor$Late)
df_late = cast(df_factor,subject~Domain+Global+Local,value="Late")

df_corr$Short = (df_late$Syllable_High_Short+df_late$Syllable_Low_Short+df_late$Voice_High_Short+df_late$Voice_Low_Short)/4
df_corr$Long = (df_late$Syllable_High_Long+df_late$Syllable_Low_Long+df_late$Voice_High_Long+df_late$Voice_Low_Long)/4
df_corr$Long_Short_MMN = df_corr$Long-df_corr$Short

df_corr$High = (df_late$Syllable_High_Short+df_late$Syllable_High_Long+df_late$Voice_High_Short+df_late$Voice_High_Long)/4
df_corr$Low = (df_late$Syllable_Low_Short+df_late$Syllable_Low_Long+df_late$Voice_Low_Short+df_late$Voice_Low_Long)/4
df_corr$Low_High_MMN = df_corr$Low-df_corr$High

df_corr$Syllable = (df_late$Syllable_High_Short+df_late$Syllable_High_Long+df_late$Syllable_Low_Short+df_late$Syllable_Low_Long)/4
df_corr$Voice = (df_late$Voice_High_Short+df_late$Voice_High_Long+df_late$Voice_Low_Short+df_late$Voice_Low_Long)/4
df_corr$Voice_Syllable_MMN = df_corr$Voice - df_corr$Syllable

Syll_High = (df_late$Syllable_High_Short+df_late$Syllable_High_Long)/2
Syll_Low = (df_late$Syllable_Low_Short+df_late$Syllable_Low_Long)/2
Voice_High = (df_late$Voice_High_Short+df_late$Voice_High_Long)/2
Voice_Low = (df_late$Voice_Low_Short+df_late$Voice_Low_Long)/2

Syll_Short = (df_late$Syllable_High_Short+df_late$Syllable_Low_Short)/2
Syll_Long = (df_late$Syllable_High_Long+df_late$Syllable_Low_Long)/2
Voice_Short = (df_late$Voice_High_Short+df_late$Voice_Low_Short)/2
Voice_Long = (df_late$Voice_High_Long+df_late$Voice_Low_Long)/2

df_corr$Syll_Local = (Syll_Long-Syll_Short)
df_corr$Syll_Global = (Syll_Low-Syll_High)
df_corr$Voice_Local = (Voice_Long-Voice_Short)
df_corr$Voice_Global = (Voice_Low-Voice_High)

df_corr$Global_long =  ((df_late$Syllable_Low_Long+df_late$Voice_Low_Long)/2) - ((df_late$Syllable_High_Long+df_late$Voice_High_Long)/2)
df_corr$Global_short = ((df_late$Syllable_Low_Short+df_late$Voice_Low_Short)/2) - ((df_late$Syllable_High_Short+df_late$Voice_High_Short)/2)
df_corr$Local_high = ((df_late$Syllable_High_Long+df_late$Voice_High_Long)/2)- ((df_late$Syllable_High_Short+df_late$Voice_High_Short)/2)
df_corr$Local_low = ((df_late$Syllable_Low_Long+df_late$Voice_Low_Long)/2)-((df_late$Syllable_Low_Short+df_late$Voice_Low_Short)/2)
```

```{r, eval=TRUE}
df_corr$subject = as.numeric(df_corr$subject)
df_corr$accuracy = as.numeric(df_corr$accuracy)
df_corr$mean_rt = as.numeric(df_corr$mean_rt)
df_corr$scaled_rt_slope = as.numeric(as.character(df_corr$scaled_rt_slope))
df_corr$entropy = as.numeric(df_corr$entropy)
df_corr$vocab = as.numeric(df_corr$vocab)
df_corr$Short = as.numeric(df_corr$Short)
df_corr$Long = as.numeric(df_corr$Long)
df_corr$Short_Long_MMN = as.numeric(df_corr$Short_Long_MMN)
df_corr$High = as.numeric(df_corr$High)
df_corr$Low = as.numeric(df_corr$Low)
df_corr$Low_High_MMN = as.numeric(df_corr$Low_High_MMN)
df_corr$Syllable = as.numeric(df_corr$Syllable)
df_corr$Voice = as.numeric(df_corr$Voice)
df_corr$Voice_Syllable_MMN = as.numeric(df_corr$Voice_Syllable_MMN)
df_corr$Syll_Local = as.numeric(df_corr$Syll_Local)
df_corr$Syll_Global = as.numeric(df_corr$Syll_Global)
df_corr$Voice_Local = as.numeric(df_corr$Voice_Local)
df_corr$Voice_Global = as.numeric(df_corr$Voice_Global)
df_corr$Global_long = as.numeric(df_corr$Global_long)
df_corr$Global_short = as.numeric(df_corr$Global_short)
df_corr$Local_high = as.numeric(df_corr$Local_high)
df_corr$Local_low = as.numeric(df_corr$Local_low)
```

## Late Correlation 
### Run correlation matrix
```{r, echo=TRUE}
df_corr_late <- df_corr
mycor_late <- rcorr(as.matrix(df_corr_late),type = "spearman")
mycor_late$r #Spearman Rho
mycor_late$P #P values
my_late_cor_p <- mycor_late$P
my_late_cor_r <- mycor_late$r
```

## Random Analyses
### One Sample t-test of behavioral data
```{r}
t.test(df_corr$accuracy, mu = .50, alternative = "two.sided")
t.test(df_corr$scaled_rt_slope, mu = 0, alternative = "two.sided")
```

### Specific Pairwise correlations
```{r}
cor.test(df_corr$accuracy, df_corr$scaled_rt_slope,  method = "pearson")
# Be sure to run the corr matrix for the early time window
cor.test(df_corr$Short_Long_MMN, df_corr$scaled_rt_slope,  method = "spearman", exact = FALSE)

# Be sure to run the corr matrix for the late time window
cor.test(df_corr$Global_long, df_corr$scaled_rt_slope,  method = "spearman", exact = FALSE)
cor.test(df_corr$Global_short, df_corr$scaled_rt_slope,  method = "spearman", exact = FALSE)
cor.test(df_corr$Local_high, df_corr$scaled_rt_slope,  method = "spearman", exact = FALSE)
cor.test(df_corr$Local_low, df_corr$scaled_rt_slope,  method = "spearman", exact = FALSE)
```

### Good and Poor Learners as determined by RT Slope
```{r}
good_learn<-df_corr[which(df_corr$scaled_rt_slope < 0),]
poor_learn<-df_corr[which(df_corr$scaled_rt_slope > 0),]
```

## Now let's do some plotting!!


### plot the line graphs to illustrate interaction between Local and Global Interaction in Late Time Window
- Julie, I suggest plot the within-subject error bars for visualization (following Morey(2008):http://www.cookbook-r.com/Graphs/Plotting_means_and_error_bars_(ggplot2)/#understanding-within-subjects-error-bars) [I haven't done that yet]
```{r}
d <- df_factor %>%
       select(Late,Local,Global) %>%  # select relevant variables
       mutate(Local = factor(Local),
              Global = factor(Global))

head(d)
d %>% 
  group_by(Local, Global) %>%
  summarise(Late_mean = mean(Late))
sum_d <- d %>% 
          group_by(Local, Global) %>%
          summarise(Late_mean = mean(Late),
                    se   = sd(Late)/sqrt(n()))
sum_d
```

```{r}
pd <- position_dodge(width = 0)
sum_d %>%
  ggplot(aes(x = Global, y = Late_mean, group = Local)) +
    geom_line(aes(linetype = Local), position = pd) +
    geom_errorbar(aes(ymin = Late_mean - se, ymax = Late_mean + se),
                  width = .1, position = pd) +
    geom_point(size = 4, position = pd) +
    geom_point(size = 3, color = "white", position = pd) + 
    guides(linetype = guide_legend("Local")) +
    labs(x = "Global",
         y = "Average ERP Amplitude") +
  theme(
    text=element_text(size=20),
    panel.background = element_rect(fill = "white"),         # Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  )
```


### Plotting the early correlations (OLD)

```{r}
ggplot(df_corr_early, aes(x=Short_Long_MMN, y=scaled_rt_slope)) + geom_point(size=3, color="navy blue", shape=19) + labs(title="Relationship between MMN and Learning", x="MMN Amplitude (uV)\nLocal Probability", y = "Speech SL (RT Slope)") +   theme_classic() +
theme(plot.title = element_text(hjust = 0.5)) + geom_smooth(method=loess)
```


### Plotting the late correlations (OLD)
```{r}
ggplot(df_corr_late, aes(x=Short_Long_MMN, y=scaled_rt_slope)) + geom_point(size=3, color="navy blue", shape=19) + labs(title="RT Slope & Local (p) MMN", x="Local (p) MMN", y = "RT Slope") + theme_classic()+ theme(plot.title = element_text(hjust = 0.5)) 
```

```{r}
ggplot(df_corr_late, aes(x=Local_low, y=scaled_rt_slope)) + geom_point(size=3, color="navy blue", shape=19) + labs(x="P3 Amplitude (uV)\nLocal (Low vs. High), Low Frequency ", y = "Speech SL (RT Slope)") +  geom_smooth(method = "loess", se=FALSE) + theme_classic(base_size = 20.0) +
theme(plot.title = element_text(hjust = 0.5))

```


### Plot the same interaction (Local and Global Interaction in Late Time Window) based on learner ability as a line graph
```{r, echo=FALSE}
good_learn <- df_corr[which(df_corr$scaled_rt_slope < 0),]
poor_learn <- df_corr[which(df_corr$scaled_rt_slope > 0),]
df_factor$subject<-as.numeric(df_factor$subject)

df_factor_subset<-merge(poor_learn, df_factor, by = "subject", sort = TRUE)

d <- df_factor_subset %>%
       select(Late,Local,Global) %>%  # select relevant variables
       mutate(Local = factor(Local),
              Global = factor(Global))

head(d)
d %>% 
  group_by(Local, Global) %>%
  summarise(Late_mean = mean(Late))
sum_d <- d %>% 
          group_by(Local, Global) %>%
          summarise(Late_mean = mean(Late),
                    se   = sd(Late)/sqrt(n()))
sum_d

pd <- position_dodge(width = 0)
sum_d %>%
  ggplot(aes(x = Global, y = Late_mean, group = Local)) +
    geom_line(aes(linetype = Local), position = pd) +
    geom_errorbar(aes(ymin = Late_mean - se, ymax = Late_mean + se),
                  width = .1, position = pd) +
    geom_point(size = 4, position = pd) +
    geom_point(size = 3, color = "white", position = pd) + 
    guides(linetype = guide_legend("Local")) +
    labs(x = "Global",
         y = "Average ERP Amplitude") +
  theme(
    text=element_text(size=20),
    panel.background = element_rect(fill = "white"),         # Set plot background to white
    legend.key  = element_rect(fill = "white"),              # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),  # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  )
```

```{r, echo=FALSE}
df_corr$learner = "fast"
df_corr[which(df_corr$scaled_rt_slope > 0),]$learner="slow"
df_corr$learner2 = "P3"
df_corr[which(df_corr$Local_low < 0),]$learner2="LDN"
df_corr$learner2 = as.factor(df_corr$learner2)
summary(df_corr$learner)
t.test(scaled_rt_slope~learner,data = df_corr)
t.test(accuracy~learner,data = df_corr)

ggplot() +
  theme_classic(base_size = 20.0) +
  #ggtitle('P3 size:Local(low) - Local(high)' + theme(plot.title = element_text(hjust = 0.5))) +
  ylab(label = 'P3 Amplitude\nLocal(Low vs. High),\n Low Frequency') +
  scale_y_continuous(breaks = pretty_breaks()) +
  geom_bar(aes(y = Local_low, x = learner,fill =  as.factor(learner)),data=df_corr,colour="black",fun.data = mean_sdl,stat = 'summary') +
  #geom_beeswarm(aes(x = learner,y = Local_low),data=df_corr,dodge.width=0.9,cex=2.5) +
  geom_errorbar(aes(y = Local_low, x = learner),data=df_corr,size = 0.3,width = 0.2,fun.y = function(x) mean(x),fun.ymin = function(x) mean(x) - sd(x)/sqrt(length(x)),fun.ymax = function(x) mean(x) + sd(x)/sqrt(length(x)) ,stat = 'summary')+
  scale_x_discrete(name = 'Learner Group',labels = c("Fast","Slow"))+   
  scale_fill_brewer(palette = 'Set2')+
  theme(legend.position = "none")

ggplot() +
  theme_classic(base_size = 20.0) +
  #ggtitle('P3 size:Local(low) - Local(high)' + theme(plot.title = element_text(hjust = 0.5))) +
  ylab(label = 'Accuracy') +
  scale_y_continuous(breaks = pretty_breaks()) +
  geom_bar(aes(y = accuracy, x = learner,fill =  as.factor(learner)),data=df_corr,colour="black",fun.data = mean_sdl,stat = 'summary') +
  #geom_beeswarm(aes(x = learner,y = Local_low),data=df_corr,dodge.width=0.9,cex=2.5) +
  geom_errorbar(aes(y = accuracy, x = learner),data=df_corr,size = 0.3,width = 0.2,fun.y = function(x) mean(x),fun.ymin = function(x) mean(x) - sd(x)/sqrt(length(x)),fun.ymax = function(x) mean(x) + sd(x)/sqrt(length(x)) ,stat = 'summary')+
  scale_x_discrete(name = 'Learner Group',labels = c("Fast","Slow"))+   
  scale_fill_brewer(palette = 'Set2')+
  theme(legend.position = "none")

ggplot() +
  theme_classic(base_size = 20.0) +
  #ggtitle('P3 size:Local(low) - Local(high)' + theme(plot.title = element_text(hjust = 0.5))) +
  ylab(label = 'Scaled RT Slope') +
  scale_y_continuous(breaks = pretty_breaks()) +
  geom_bar(aes(y = scaled_rt_slope, x = learner2,fill =  as.factor(learner2)),data=df_corr,colour="black",fun.data = mean_sdl,stat = 'summary') +
  geom_beeswarm(aes(x = learner2,y = scaled_rt_slope),data=df_corr,dodge.width=0.9,cex=2.5) +
  geom_errorbar(aes(y = scaled_rt_slope, x = learner2),data=df_corr,size = 0.3,width = 0.2,fun.y = function(x) mean(x),fun.ymin = function(x) mean(x) - sd(x)/sqrt(length(x)),fun.ymax = function(x) mean(x) + sd(x)/sqrt(length(x)) ,stat = 'summary')+
  scale_x_discrete(name = 'Learner Group',labels = c("LDN","P3"))+   
  scale_fill_brewer(palette = 'Set2')+
  theme(legend.position = "none")

ggplot() +
  theme_classic(base_size = 20.0) +
  #ggtitle('P3 size:Local(low) - Local(high)' + theme(plot.title = element_text(hjust = 0.5))) +
  ylab(label = 'Accuracy') +
  scale_y_continuous(breaks = pretty_breaks()) +
  geom_bar(aes(y = accuracy, x = learner2,fill =  as.factor(learner2)),data=df_corr,colour="black",fun.data = mean_sdl,stat = 'summary') +
  geom_beeswarm(aes(x = learner2,y = accuracy),data=df_corr,dodge.width=0.9,cex=2.5) +
  geom_errorbar(aes(y = accuracy, x = learner2),data=df_corr,size = 0.3,width = 0.2,fun.y = function(x) mean(x),fun.ymin = function(x) mean(x) - sd(x)/sqrt(length(x)),fun.ymax = function(x) mean(x) + sd(x)/sqrt(length(x)) ,stat = 'summary')+
  scale_x_discrete(name = 'Learner Group',labels = c("LDN","P3"))+   
  scale_fill_brewer(palette = 'Set2')+
  theme(legend.position = "none")
```

```{r}
length(which(df_corr$scaled_rt_slope < 0))
length(which(df_corr$scaled_rt_slope > 0))
```

