---
title: "PTT"
author: "An Nguyen"
date: "May 14, 2018"
output: html_document
---

```{r,echo=FALSE}
library(ggplot2)
# ACCURACY DATA
test <- list()

path <- "C:/Users/Qlab/Documents/ptt/"  
files <- list.files(path=path, pattern="*test_session.csv") 

for(file in files)
{
   
    assign(
        gsub(" ","",file), 
        read.csv(paste(path,file,sep="")))
}
for(file in files){test <- append(test,list(eval(parse(text=file))))}


test <- do.call(rbind.data.frame, test)

tsl <- mean(test$tsl.corr,na.rm=TRUE)
vsl <- mean(test$vsl_question_key_resp.corr,na.rm=TRUE)
lsl <- mean(test$lsl_question_key_resp.corr,na.rm=TRUE)
ssl <- mean(test$ssl_question_key_resp.corr,na.rm=TRUE)

c1 <- round(c(tsl,vsl,lsl,ssl),2)
c2 <- round(c(t.test(test$tsl.corr,mu=0.5,alternative='greater', na.rm=TRUE)$p.value,t.test(test$vsl_question_key_resp.corr,mu=0.5,alternative='greater', na.rm=TRUE)$p.value,t.test(test$lsl_question_key_resp.corr,mu=0.5,alternative='greater', na.rm=TRUE)$p.value,t.test(test$ssl_question_key_resp.corr,mu=0.5,alternative='greater', na.rm=TRUE)$p.value),3)
test_result <- data.frame(c1,c2)
colnames(test_result) <- c("Mean Accuracy","p-value")
rownames(test_result) <- c("TSL","VSL","LSL","SSL")
print(test_result)
```

```{r,echo=FALSE,warning=FALSE}
# RT AUDITORY
aud <- list()

aud_path <- "C:/Users/Qlab/Documents/ptt/aud/"  
auditory_files <- list.files(path=aud_path, pattern="*.csv") 

for(file in auditory_files)
{
   
    assign(
        gsub(" ","",file), 
        read.csv(paste(aud_path,file,sep="")))
}
for(file in auditory_files){aud <- append(aud,list(eval(parse(text=file))))}


aud <- do.call(rbind.data.frame, aud)
aud$tone_block_key_resp.rt <- aud$tone_block_key_resp.rt*1000
aud$sound_block_key_resp.rt <- aud$sound_block_key_resp.rt*1000

aud$soundFile <- gsub(".wav","",aud$soundFile)
random_tone <- aud[which(aud$Run <=2 & aud$condition=="R"),]
random_syllable <- aud[which(aud$Run >2 & aud$condition=="R"),]

structured_tone <- aud[which(aud$Run >2 & aud$condition=="S"),]
structured_syllable <- aud[which(aud$Run <=2 & aud$condition=="S"),]


rt_col <- NULL
id <- NULL
trial <- NULL
target <- NULL
row_number <- which(random_tone$ttarget==random_tone$soundFile)

for (i in row_number){
    if (!is.na(random_tone[i,]$tone_block_key_resp.rt)){rt_col <- append(rt_col,random_tone[i,][,"tone_block_key_resp.rt"])} 
    trial <- append(trial,paste(random_tone[i,][,"trialnum"]))
    id <- append(id,paste(random_tone[i,]$PartID))
    if (!is.na(random_tone[i+1,][,"tone_block_key_resp.rt"])){
        rt_col[(match(i,row_number))] <- 480+random_tone[i+1,][,"tone_block_key_resp.rt"]}
    if (!is.na(random_tone[i-1,][,"tone_block_key_resp.rt"])){
        rt_col[(match(i,row_number))] <- 0-random_tone[i-1,][,"tone_block_key_resp.rt"]
        
    }}
fam_trial <- data.frame(trial,rt_col,id)
reindex <- c(rep(1:48,5))
reindex <- append(reindex,25:48)
reindex <- append(reindex,rep(1:48,9))
fam_trial$reindex <- reindex
mean_table <- fam_trial[which(!is.na(fam_trial$rt_col) & fam_trial$rt_col<960 & fam_trial$rt_col>-480), ]
mean_rt <- NULL
rt_slope <- NULL
list_id <- unique(mean_table$id)
for(id in list_id){
  mean_rt<-append(mean_rt,round(mean(mean_table$rt_col[mean_table$id==id]),digits=3))
 rt_slope <-append(rt_slope,round(summary(lm(mean_table$rt_col[mean_table$id==id]~mean_table$reindex[mean_table$id==id]))$coefficient[2,1],digits=3))
}
subj_table <- data.frame(list_id,mean_rt,rt_slope)
subj_table$condition <- "Random"
subj_table$Type <- "Tone"

########

rt_col <- NULL
id <- NULL
trial <- NULL
target <- NULL
row_number <- which(structured_tone$ttarget==structured_tone$soundFile)

for (i in row_number){
  if (!is.na(structured_tone[i,]$tone_block_key_resp.rt)){rt_col <- append(rt_col,structured_tone[i,][,"tone_block_key_resp.rt"])} 
  trial <- append(trial,paste(structured_tone[i,][,"trialnum"]))
  id <- append(id,paste(structured_tone[i,]$PartID))
  if (!is.na(structured_tone[i+1,][,"tone_block_key_resp.rt"])){
    rt_col[(match(i,row_number))] <- 480+structured_tone[i+1,][,"tone_block_key_resp.rt"]}
  if (!is.na(structured_tone[i-1,][,"tone_block_key_resp.rt"])){
    rt_col[(match(i,row_number))] <- 0-structured_tone[i-1,][,"tone_block_key_resp.rt"]
    
  }}
fam_trial <- data.frame(trial,rt_col,id)
reindex <- c(rep(1:48,15))
fam_trial$reindex <- reindex
mean_table <- fam_trial[which(!is.na(fam_trial$rt_col) & fam_trial$rt_col<960 & fam_trial$rt_col>-480), ]
mean_rt <- NULL
rt_slope <- NULL
list_id <- unique(mean_table$id)
for(id in list_id){
  mean_rt<-append(mean_rt,round(mean(mean_table$rt_col[mean_table$id==id]),digits=3))
  rt_slope <-append(rt_slope,round(summary(lm(mean_table$rt_col[mean_table$id==id]~mean_table$reindex[mean_table$id==id]))$coefficient[2,1],digits=3))
}
temp <- data.frame(list_id,mean_rt,rt_slope)
temp$Condition <- "Structured"
temp$Type <- "Tone"
names(temp) <- names(subj_table)

#######

rt_col <- NULL
id <- NULL
trial <- NULL
target <- NULL
row_number <- which(structured_syllable$starget==structured_syllable$soundFile)

for (i in row_number){
  if (!is.na(structured_syllable[i,]$sound_block_key_resp.rt)){rt_col <- append(rt_col,structured_syllable[i,][,"sound_block_key_resp.rt"])} 
  trial <- append(trial,paste(structured_syllable[i,][,"trialnum"]))
  id <- append(id,paste(structured_syllable[i,]$PartID))
  if (!is.na(structured_syllable[i+1,][,"sound_block_key_resp.rt"])){
    rt_col[(match(i,row_number))] <- 480+structured_syllable[i+1,][,"sound_block_key_resp.rt"]}
  if (!is.na(structured_syllable[i-1,][,"sound_block_key_resp.rt"])){
    rt_col[(match(i,row_number))] <- 0-structured_syllable[i-1,][,"sound_block_key_resp.rt"]
    
  }}
fam_trial <- data.frame(trial,rt_col,id)
reindex <- c(rep(1:48,5))
reindex <- append(reindex,25:48)
reindex <- append(reindex,rep(1:48,9))
fam_trial$reindex <- reindex
mean_table <- fam_trial[which(!is.na(fam_trial$rt_col) & fam_trial$rt_col<960 & fam_trial$rt_col>-480), ]
mean_rt <- NULL
rt_slope <- NULL
list_id <- unique(mean_table$id)
for(id in list_id){
  mean_rt<-append(mean_rt,round(mean(mean_table$rt_col[mean_table$id==id]),digits=3))
  rt_slope <-append(rt_slope,round(summary(lm(mean_table$rt_col[mean_table$id==id]~mean_table$reindex[mean_table$id==id]))$coefficient[2,1],digits=3))
}
temp2 <- data.frame(list_id,mean_rt,rt_slope)
temp2$Condition <- "Structured"
temp2$Type <- "Syllable"
names(temp2) <- names(subj_table)

########
rt_col <- NULL
id <- NULL
trial <- NULL
target <- NULL
row_number <- which(random_syllable$starget==random_syllable$soundFile)

for (i in row_number){
    if (!is.na(random_syllable[i,]$sound_block_key_resp.rt)){rt_col <- append(rt_col,random_syllable[i,][,"sound_block_key_resp.rt"])} 
    trial <- append(trial,paste(random_syllable[i,][,"trialnum"]))
    id <- append(id,paste(random_syllable[i,]$PartID))
    if (!is.na(random_syllable[i+1,][,"sound_block_key_resp.rt"])){
        rt_col[(match(i,row_number))] <- 480+random_syllable[i+1,][,"sound_block_key_resp.rt"]}
    if (!is.na(random_syllable[i-1,][,"sound_block_key_resp.rt"])){
        rt_col[(match(i,row_number))] <- 0-random_syllable[i-1,][,"sound_block_key_resp.rt"]
        
    }}
fam_trial <- data.frame(trial,rt_col,id)
reindex <- c(rep(1:48,15))
fam_trial$reindex <- reindex
mean_table <- fam_trial[which(!is.na(fam_trial$rt_col) & fam_trial$rt_col<960 & fam_trial$rt_col>-480), ]
mean_rt <- NULL
rt_slope <- NULL
list_id <- unique(mean_table$id)
for(id in list_id){
    mean_rt<-append(mean_rt,round(mean(mean_table$rt_col[mean_table$id==id]),digits=3))
    rt_slope <-append(rt_slope,round(summary(lm(mean_table$rt_col[mean_table$id==id]~mean_table$reindex[mean_table$id==id]))$coefficient[2,1],digits=3))
}
temp3 <- data.frame(list_id,mean_rt,rt_slope)
temp3$Condition <- "Random"
temp3$Type <- "Syllable"
names(temp3) <- names(subj_table)

subj_table <- rbind(subj_table,temp,temp2,temp3)

lowerbound <- mean(subj_table$rt_slope) - 2.5*sd(subj_table$rt_slope)
upperbound <- mean(subj_table$rt_slope) + 2.5*sd(subj_table$rt_slope)
subj_table <- subj_table[subj_table$rt_slope>=lowerbound,]
subj_table <- subj_table[subj_table$rt_slope<=upperbound,]

ggplot(subj_table,aes(x=Type,y=rt_slope,fill=condition)) + geom_bar(stat='summary', position=position_dodge()) 

t.test(subj_table$rt_slope[subj_table$condition=="Random"],subj_table$rt_slope[subj_table$condition=="Structured"],alternative="greater")

t.test(subj_table$rt_slope[subj_table$condition=="Random" & subj_table$Type=="Tone"],subj_table$rt_slope[subj_table$condition=="Structured" & subj_table$Type=="Tone"],alternative="greater")

t.test(subj_table$rt_slope[subj_table$condition=="Random" & subj_table$Type=="Syllable"],subj_table$rt_slope[subj_table$condition=="Structured" & subj_table$Type=="Syllable"],alternative="greater")

t.test(subj_table$rt_slope[subj_table$condition=="Random"],mu=0.5,alternative = 'less')

t.test(subj_table$rt_slope[subj_table$condition=="Structured"],mu=0.5,alternative = 'less')
#print(subj_table)
```

```{r,echo=FALSE,warning=FALSE}
#VISUAL
visual <- list()

visual_path <- "C:/Users/Qlab/Documents/ptt/visual/"  
visual_files <- list.files(path=visual_path, pattern="*.csv") 

for(file in visual_files)
{
  
  assign(
    gsub(" ","",file), 
    read.csv(paste(visual_path,file,sep="")))
}
for(file in visual_files){visual <- append(visual,list(eval(parse(text=file))))}


visual <- do.call(rbind.data.frame, visual)
visual$v_block_trial_key_resp.rt <- visual$v_block_trial_key_resp.rt*1000
visual$image <- gsub(".bmp","",visual$image)
visual$image <- gsub("Alien","",visual$image)

random_image <- visual[which(visual$Run <=2 & visual$condition=="R"),]
structured_image <- visual[which(visual$Run >2 & visual$condition=="S"),]


rt_col <- NULL
id <- NULL
trial <- NULL
target <- NULL
row_number <- which(random_image$vtarget==random_image$image)

for (i in row_number){
  if (!is.na(random_image[i,]$v_block_trial_key_resp.rt)){rt_col <- append(rt_col,random_image[i,][,"v_block_trial_key_resp.rt"])} 
  trial <- append(trial,paste(random_image[i,][,"trialnum"]))
  id <- append(id,paste(random_image[i,]$PartID))
  if (!is.na(random_image[i+1,][,"v_block_trial_key_resp.rt"])){
    rt_col[(match(i,row_number))] <- 1000+random_image[i+1,][,"v_block_trial_key_resp.rt"]}
  if (!is.na(random_image[i-1,][,"v_block_trial_key_resp.rt"])){
    rt_col[(match(i,row_number))] <- 0-random_image[i-1,][,"v_block_trial_key_resp.rt"]
    
  }}
fam_trial <- data.frame(trial,rt_col,id)
reindex <- NULL
le <- NULL
for (i in unique(fam_trial$id)){le <- append(le,(sum(fam_trial$id==i)))}
for (i in le){reindex <- append(reindex,c(1:i))}
fam_trial$reindex <- reindex
mean_table <- fam_trial[which(!is.na(fam_trial$rt_col) & fam_trial$rt_col<1000 & fam_trial$rt_col>-1000), ]
mean_rt <- NULL
rt_slope <- NULL
list_id <- unique(mean_table$id)
for(id in list_id){
  mean_rt<-append(mean_rt,round(mean(mean_table$rt_col[mean_table$id==id]),digits=3))
  rt_slope <-append(rt_slope,round(summary(lm(mean_table$rt_col[mean_table$id==id]~mean_table$reindex[mean_table$id==id]))$coefficient[2,1],digits=3))
}
subj_table <- data.frame(list_id,mean_rt,rt_slope)
subj_table$condition <- "Random"
subj_table$Type <- "Image"

#####


rt_col <- NULL
id <- NULL
trial <- NULL
target <- NULL
row_number <- which(structured_image$vtarget==structured_image$image)
for (i in row_number){
  if (!is.na(structured_image[i+1,][,"v_block_trial_key_resp.rt"])){
    rt_col[(match(i,row_number))] <- 1000+structured_image[i+1,][,"v_block_trial_key_resp.rt"]}
  if (!is.na(structured_image[i,]$v_block_trial_key_resp.rt)){rt_col <- append(rt_col,structured_image[i,][,"v_block_trial_key_resp.rt"])} 
  trial <- append(trial,paste(structured_image[i,][,"trialnum"]))
  id <- append(id,paste(structured_image[i,]$PartID))
  if (is.na(structured_image[i,]$v_block_trial_key_resp.rt)){rt_col[(match(i,row_number))] <- "NA"}  
  
  if (!is.na(structured_image[i-1,][,"v_block_trial_key_resp.rt"])){
    rt_col[(match(i,row_number))] <- 0-structured_image[i-1,][,"v_block_trial_key_resp.rt"]
    
  }}
fam_trial <- data.frame(trial,rt_col,id)
fam_trial$rt_col <- as.numeric(fam_trial$rt_col)
reindex <- c(rep(1:24,15))
fam_trial$reindex <- reindex
mean_table <- fam_trial[which(!is.na(fam_trial$rt_col) & fam_trial$rt_col<1000 & fam_trial$rt_col>-1000), ]
mean_rt <- NULL
rt_slope <- NULL
list_id <- unique(mean_table$id)
for(id in list_id){
  mean_rt<-append(mean_rt,round(mean(mean_table$rt_col[mean_table$id==id]),digits=3))
  rt_slope <-append(rt_slope,round(summary(lm(mean_table$rt_col[mean_table$id==id]~mean_table$reindex[mean_table$id==id]))$coefficient[2,1],digits=3))
}
subj_table2 <- data.frame(list_id,mean_rt,rt_slope)
subj_table2$condition <- "Structured"
subj_table2$Type <- "Image"

####
subj_table_v <- rbind(subj_table,subj_table2)
t.test(subj_table_v$rt_slope[subj_table_v$condition=="Random"],subj_table_v$rt_slope[subj_table_v$condition=="Structured"],alternative="greater")
ggplot(subj_table_v,aes(x=factor(condition),y=rt_slope, fll=condition)) + geom_bar(stat='summary')
#print(subj_table_v)
